---
title: "EXNAT_4_TMS_Stats_Reading"
author: "Sandra Martin"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    code-fold: true
editor_options:
  chunk_output_type: console
---

```{r file setup, echo = FALSE}
rm(list = ls()) # clear environment
knitr::opts_chunk$set() # set default options for all code blocks in this document
options(scipen = 999) # don't use scientific notation for very large or small numbers
n.cores <- max(1, parallel::detectCores() %/% 2, na.rm = T) # Use half of the available cores
```

# Load packages
```{r packages, echo = FALSE, message = FALSE, warning = TRUE}
# Create a list with needed libraries
pkgs <- c("here", # for working with relative paths
          "ggeffects",
          "marginaleffects",
          "emmeans",
          "ggplot2", # for plots
          "dplyr", # for replacing multiple values in vector with different values
          "tidyverse", # for aggregating
          "easystats", # includes performance, see, insight, modelbased
          #"lme4", # also for linear mixed emodels, but no p-values in the summary
          "lmerTest", # extension of lme4 - for tab_model() for showing lme4 model results
          "glmmTMB",
          "mgcv",
          "gratia",
          "itsadug",
          "ggside",
          "ggpubr",
          "car", # for basic Anova() function & aGSIFs (= basically weird adjusted VIFs)
          "sjPlot", # for running Anova & showing results in a HTML table in the Viewer
          "ggnewscale",
          "colorspace", # for beautiful and balanced color palettes
          "ggrepel", # for labels
          "scales",
          "egg") # creating patchwork plots

# Load each listed library, check if it's already installed
# and install if necessary
for (pkg in pkgs){
  if(!require(pkg, character.only = TRUE)){
    install.packages(pkg)
    library(pkg, character.only = TRUE)
  }
}

today <- Sys.Date()
today <- format(today, format="%y%m%d")

emm_options(rg.limit = 1000000) # for emm calculations
```

# Load R Data
```{r}
df_all_data_clean <- readRDS(here::here("RData/df_all_data_clean.rds")) # df with all trials and participants incl demographic information

# load LMM (which takes really long to compute) but not gamm, which is computed quite fast
lmm_reading <- readRDS(file = here("RData/models/lmm_reading.rds"))

# reading predictions and comparisons (take quite long to calculate due to long dfs)
pred_surprisal <- readRDS(file = here("RData/models/gamm_reading_pred_surprisal.rds"))
cmp_reading_surprisal <- readRDS(file = here("RData/models/gamm_reading_comp_reading_surprisal.rds"))

pred_time <- readRDS(file = here("RData/models/gamm_reading_pred_time.rds"))
cmp_reading_time <- readRDS(file = here("RData/models/gamm_reading_comp_reading_time.rds"))
cmp_reading_time_NoTask <- readRDS(file = here("RData/models/gamm_reading_comp_reading_time_NoTask.rds"))
```

# Settings for plots
```{r Theme for plots, echo = FALSE}
# Custom colour palettes for the plots:
palet_task_condition <- c("#D2BFE7",
                      "#977FB2") 
palet_task_condition_lines <- c("#ad8bd3",
                      "#7B5EC6") 

# for distinguishing between cognitive load conditions: 
 cols_reading <- c("#575A7B", # Reading Only
                 "#ED9201", # 1-back
                 "#982126") # 2-back
#cols_reading <- c("#F8A29E", "#9F4D48", "#4B201D", "#D2BFF5", "#9b84b7", "#56476D")
cols_reading <- c("#F8A29E", "#9F4D48", "#4B201D", "#E9B3FB", "#85409D", "#3B0270")
#cols_dual <- c("#D2BFE7", "#9b84b7", "#56476D")

cols_dualContrast <- c("#B29675", "#575A7B")

# creating a function for std.error
std.error <- function(x, na.rm = TRUE){sd(x, na.rm = TRUE)/sqrt(length(x[!is.na(x)]))}
```

# READING ANALYSIS: READING ONLY & DUAL TASK
## Df for reading tasks
```{r df for single n-back}
reading_df <- subset(df_all_data_clean, task != "1back_single_main_click" & task != "2back_single_main_click")
reading_df <- droplevels(reading_df)
```

## Prepare df, contrast coding
```{r prepare data for stats single n-back, echo = FALSE}
# add column with information whether there was a TMS burst in a certain trial or not
reading_df <- reading_df %>% 
  mutate(is_trigger = case_when(
    stim_type != "Offline" & !is.na(trigger_time) ~ "True",
    stim_type != "Offline" & is.na(trigger_time) ~ "False",
    stim_type == "Offline" ~ "False"
  ))

# if the n-back trial was in the dual task (adding level to cognitive load column)
reading_df <- reading_df %>% 
  mutate(cognitive_load = case_when(
    task == "2back_dual_main_click" ~ "dual task",
    TRUE ~ "single task"
  ))

# simple coding ----
# create a simple coding scheme for reaction (2 levels), is_trigger, cognitive_load
c <- contr.treatment(2) 
my.coding <- matrix(rep(1/2, 2), ncol = 1) 
my.simple <- c-my.coding

reading_df$reaction <- as.factor(reading_df$reaction)
contrasts(reading_df$reaction) <- my.simple

reading_df$is_trigger <- as.factor(reading_df$is_trigger)
contrasts(reading_df$is_trigger) <- my.simple

reading_df$cognitive_load <- as.factor(reading_df$cognitive_load)
contrasts(reading_df$cognitive_load) <- my.simple

reading_df$task <- factor(reading_df$task, levels = c("Reading_Baseline_main_click", "2back_dual_main_click"))
contrasts(reading_df$task) <- my.simple

# simple coding for stimulation type, session, block name, cognitive_load
c <- contr.treatment(3) 
my.coding <- matrix(rep(1/3, 6), ncol = 2) 
my.simple <- c-my.coding

reading_df$stim_type <- factor(reading_df$stim_type, levels = c("Sham", "Offline", "Offline + Online"))
contrasts(reading_df$stim_type) <- my.simple

reading_df$session <- as.factor(reading_df$session)
contrasts(reading_df$session) <- my.simple

# simple coding for punctuation (5 levels)
c <- contr.treatment(5) 
my.coding <- matrix(rep(1/5, 20), ncol = 4) 
my.simple <- c-my.coding
reading_df$punctuation <- as.factor(reading_df$punctuation)
contrasts(reading_df$punctuation) <- my.simple

# simple coding for stimulation order (6 levels)
c <- contr.treatment(6) 
my.coding <- matrix(rep(1/6, 30), ncol = 5) 
my.simple <- c-my.coding
reading_df$Stim_Order <- as.factor(reading_df$Stim_Order)
contrasts(reading_df$Stim_Order) <- my.simple

# create a column for time that sets first trial of each task to 0 and calculates time to next trial so we get a measure of time progress in s across one session
reading_df <- reading_df %>%
  arrange(participant, stim_type, trial_index_session) %>%
  group_by(participant, stim_type, date, task) %>%
  mutate(
    time_from_onset_task = as.numeric(global_onset_time - first(global_onset_time), units = "secs"),
    task_onset = first(time_from_onset_session),
    block_nr_task = cumsum(trial_nr == 1)
  ) %>%
  ungroup()

# add column whether the previous trial and second to last trials were an n-back target or not and whether the previous response was correct or incorrect
reading_df <- reading_df %>%
  group_by(participant, stim_type, block_nr_exp) %>%
  mutate(
    # Previous trial was target (lag 1)
    prev_target = lag(target, n = 1, default = NA),
    
    # Second-to-last trial was target (lag 2)
    prev2_target = lag(target, n = 2, default = NA),
    
    # Previous trial accuracy (for post-error effects)
    prev_correct = lag(nback_response, n = 1, default = NA),
    
    # RT of previous trial
    previous_duration = lag(RT, n = 1, default = NA)
  ) %>%
  ungroup()

# Create column that codes nback acc as correct/incorrect instead of four levels (avoids collinearity with reaction predictor in model)
reading_df <- reading_df %>% 
  mutate(nback_acc = case_when(
    nback_response == "correct rejection" ~ "correct",
    nback_response == "hit" ~ "correct",
    nback_response == "false alarm" ~ "incorrect",
    nback_response == "miss" ~ "incorrect",
  ))

# simple coding previous reaction, previous target, previous2 target, nback_acc
c <- contr.treatment(2) 
my.coding <- matrix(rep(1/2, 2), ncol = 1) 
my.simple <- c-my.coding

reading_df$previous_reaction[reading_df$previous_reaction == ""] <- NA
reading_df$previous_reaction <- as.factor(reading_df$previous_reaction)
reading_df$previous_reaction <- droplevels(reading_df$previous_reaction)
contrasts(reading_df$previous_reaction) <- my.simple

reading_df$nback_acc <- as.factor(reading_df$nback_acc)
contrasts(reading_df$nback_acc) <- my.simple

c <- contr.treatment(3) 
my.coding <- matrix(rep(1/3, 6), ncol = 2) 
my.simple <- c-my.coding

reading_df$prev_target <- as.factor(reading_df$prev_target)
contrasts(reading_df$prev_target) <- my.simple

reading_df$prev2_target <- as.factor(reading_df$prev2_target)
contrasts(reading_df$prev2_target) <- my.simple

reading_df$Age <- as.numeric(reading_df$Age)

# Add the information how many triggers there were per block 
# Ultimately doesn't perform well in models because there was no online trigger in the offline session leading to overall weird estimates
# CAVE: this is centred within the offline+online & sham session and NOT the offline session since there were no triggers per block in this session
# nback_df <- nback_df %>% 
#   group_by(participant, stim_type, block_names_numbered) %>% 
#   mutate(trigger_per_block = sum(is_trigger == "True")) %>% 
#   ungroup()
# nback_df <- nback_df %>%
#   mutate(
#     grand_mean_nonoffline = mean(trigger_per_block[stim_type != "Offline"], na.rm = TRUE),
#     trigger_per_block_centered = case_when(
#       stim_type == "Offline" ~ 0,
#       TRUE ~ trigger_per_block - grand_mean_nonoffline
#     )
#   ) %>%
#   select(-grand_mean_nonoffline, -trigger_per_block)  # Clean up temporary variable
# nback_df$trigger_per_block_centered <- as.numeric(nback_df$trigger_per_block_centered)

# save single n-back df ----
# saveRDS(nback_df, file = here::here("RData/nback_df.rds"))

# For statistical models, remove first trials w/o surprisal values on ts 2 ----
reading_df <- subset(reading_df, !is.na(surprisal_2) & !is.na(previous_surprisal_2))
reading_df <- subset(reading_df, surprisal_2 < 40)
#reading_df <- subset(reading_df, RT > 100)
reading_df <- reading_df %>% 
  mutate(task = dplyr::recode(task, "Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))
```

## ALL TRIALS: Reading time analysis
```{r}
# look at RT
hist(log(reading_df$RT))
hist(reading_df$RT)
fitdistrplus::descdist(reading_df$RT)
fitdistrplus::descdist(log(reading_df$RT))

# GAMM ----
reading_df <- reading_df %>% 
  mutate(across(where(is.character), as.factor))

gamm_reading <- bam(log(RT) ~ 
            # parametric main effects and interactions (factors)  
              #stim_type + 
              #task +
              session + 
              is_trigger + 
              reaction +
              punctuation +
              RS +
              executive_sum +
              education_years +
              Age +
              sideEffects_sum +
              #stim_type:task + 
            # non-parametric main effects (smooths)
              s(time_from_onset_task, k = 20) + 
              s(surprisal_2, k = 20) + 
              s(entropy_2, k = 30) +
              s(word_length_single, k = 20) + 
              s(zipf_frequency, k = 20) +
              s(log(previous_duration), k = 50) +
              s(previous_surprisal_2, k = 20) + 
            # interactions
              s(stim_type, time_from_onset_task, bs = "sz", k = 20) + 
              s(task, time_from_onset_task, bs = "sz", k = 20) + 
              s(stim_type, task, time_from_onset_task, bs = "sz", k = 20) + 
              #s(time_from_onset_task, by = stimType_task, k = 20) + # old way of writing the interaction term
              
              s(stim_type, surprisal_2, bs = "sz", k = 20) + 
              s(task, surprisal_2, bs = "sz", k = 20) + 
              s(stim_type, task, surprisal_2, bs = "sz", k = 20) + 
              #s(surprisal_2, by = stimType_task, k = 20) + # old way of writing the interaction term
            # random terms
              s(participant, bs = "re") +
              s(participant, stim_type, bs = "re") +
              s(participant, task, bs = "re") +  
              s(surprisal_2, participant, bs = "fs", k = 10) +
              s(time_from_onset_task, participant, bs = "fs") +
              s(text_nr, bs = "re"),
    data = reading_df,
    #family = Gamma(link = "log"),
    method = "fREML",
    discrete = TRUE,
    control = gam.control(nthreads = n.cores)
)

gam.check(gamm_reading, k.rep = 1000)

summary(gamm_reading)

# LMM ----
lmm_reading <- lmerTest::lmer(log(RT) ~
                         stim_type +
                         session +
                         task +
                         is_trigger +
                         reaction + 
                         punctuation +
                         scale(time_from_onset_task, scale = FALSE) +   
                         scale(RS, scale = FALSE) +
                         scale(executive_sum, scale = FALSE) +
                         scale(education_years, scale = FALSE) +
                         scale(Age, scale = FALSE) +
                         scale(sideEffects_sum, scale = FALSE) +
                         # lexical predictors
                         scale(surprisal_2, scale = FALSE) + # slope yes
                         scale(entropy_2, scale = FALSE) + # slope no
                         scale(zipf_frequency, scale = FALSE) + # slope no
                         scale(word_length_single, scale = FALSE) + # slope no
                         scale(log(previous_duration), scale = FALSE) +
                         scale(previous_surprisal_2, scale = FALSE) + # slope no
                         # interactions
                         stim_type:task +
                         stim_type:scale(time_from_onset_task, scale = FALSE) +   
                         stim_type:scale(surprisal_2, scale = FALSE) +   
                         task:scale(surprisal_2, scale = FALSE) +   
                         task:scale(time_from_onset_task, scale = FALSE) +   
                         stim_type:task:scale(surprisal_2, scale = FALSE) +   
                         stim_type:task:scale(time_from_onset_task, scale = FALSE) +   
                         (1 + stim_type + task | participant) +
                         (1 | text_nr),
                       data = reading_df,
                       REML = FALSE,
                       control = lmerControl(optimizer = "bobyqa")
)
saveRDS(lmm_reading, file = here("RData/models/lmm_reading.rds")) # save it because it takes forever too compute

check_model(lmm_reading)

summary(lmm_reading)
anova(lmm_reading)

tab_model(lmm_reading, 
          gamm_reading, 
          show.intercept = FALSE,
          show.icc = TRUE,   # ICC (Intraclass Correlation) is not always needed
          show.re.var = TRUE,  # Show variance of random effects
          show.df = FALSE,     # Don't display degrees of freedom
          show.obs = TRUE,    # Don't display number of observations
          show.ngroups = FALSE, # Don't display number of groups for random effects
          show.stat = TRUE,    # Show model statistics (e.g., p-values, F-values)
          collapse.ci = TRUE,  # Collapse confidence intervals into one line
          show.std = "std", # Show standardized beta,
          df.method = "satterthwaite",
          file = here("reading_models_new.doc"))

# contrast stim_types by task:
estimate_contrasts(lmm_reading, contrast = "stim_type", by = "task", transform = T, estimate = "average", backend = "emmeans", p_adjust = "holm")

emm <- emmeans(
  lmm_reading,
  ~ stim_type * task
)

contrast(
  emm,
  interaction = c("pairwise", "pairwise"),
  type = "response"
)

# full pairwise contrast matrix
emmeans(lmm_reading, pairwise ~ stim_type * task, adjust = "none")
```

### Plots reading time models
```{r}
# GAMM plots ----
#1) stim type x task x surprisal: three-way interaction from GAMM ----
# first build a grid for plotting and comparisons
sm_names <- smooths(gamm_reading)
rand_terms <- sm_names[grepl("participant|text_nr", sm_names)]
mf <- model.frame(gamm_reading)

tasks     <- unique(mf$task)
stimtypes <- unique(mf$stim_type)

# for plotting
reading_df$stim_task <- interaction(reading_df$stim_type, reading_df$task, drop = TRUE)

# build grid manually to make sure we only include surprisal values in predictions actually present in the different tasks and stimulation conditions (should be balanced)
reading_grid_surprisal <- do.call(
  rbind,
  lapply(tasks, function(tt) {
    lapply(stimtypes, function(ss) {
      mf_sub <- subset(mf, task == tt & stim_type == ss)

      datagrid(
        model = gamm_reading,
        surprisal_2 = seq(
          min(mf_sub$surprisal_2, na.rm = TRUE),
          max(mf_sub$surprisal_2, na.rm = TRUE),
          length.out = 100
        ),
        task       = tt,
        stim_type  = ss,
        session    = levels(mf$session),
        punctuation = levels(mf$punctuation),
        is_trigger  = levels(mf$is_trigger),
        reaction    = levels(mf$reaction)
      )
    })
  }) |> unlist(recursive = FALSE)
)

pred_surprisal <- predictions(
  gamm_reading,
  newdata = reading_grid_surprisal,
  by = c("surprisal_2", "stim_type", "task"),
  type = "link",
  transform = exp,
  exclude = rand_terms
)
saveRDS(pred_surprisal, file = here("RData/models/gamm_reading_pred_surprisal.rds"))

pred_surprisal$stim_task <- interaction(pred_surprisal$stim_type, pred_surprisal$task, drop = TRUE)

(RT_reading_stimtype_task_surprisal <- ggplot(pred_surprisal, aes(x = surprisal_2, y = estimate, colour = stim_task, fill = stim_task)) +
  #geom_jitter2(data = slice_sample(reading_df, prop = 0.1), mapping = aes(x = surprisal_2, y = RT), alpha = 0.02) +
  geom_rug(
  data = reading_df |> group_by(stim_task) |> distinct(surprisal_2),
  aes(x = surprisal_2, colour = stim_task),
  inherit.aes = FALSE,
  sides = "b",
  alpha = 0.12,
  linewidth = 0.2
) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
  geom_line(linewidth = 1.1) +
  facet_wrap(~ task, labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task")), scales = "free_x") +
  ylab("Reading time in ms") +
  xlab("Lexical surprisal") +
  coord_cartesian(ylim = c(250, 1290)) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 3)) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_color_manual(values = cols_reading) +
  scale_fill_manual(values = cols_reading) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 8.5))
)
ggsave(RT_reading_stimtype_task_surprisal, file = here(paste0("Plots/RT_reading_stimtype_task_surprisal_", today, ".png")), width = 90, height = 72, units = "mm")

##1b) Comparison of different smooths ----
cmp_reading_surprisal <- comparisons(
  gamm_reading,
  newdata = reading_grid_surprisal,
  variables = list(stim_type = "pairwise"),
  type = "link",
  transform = exp,
  exclude = rand_terms,
  comparison = "difference",
  #hypothesis = difference ~ reference
)
saveRDS(cmp_reading_surprisal, file = here("RData/models/gamm_reading_comp_reading_surprisal.rds"))
# with transform = exp we get ratio, otherwise we get log ms
# interpretation: 
# ratio of 0.9999152 means: for one unit of surprisal, RT is 0.0000848% lower relative to sham, multiply this e.g. by 1000 s to get a better picture: 0.0848 --> after 1000s about 8.5% lower than sham

cmp_df_reading_surprisal <- as.data.frame(cmp_reading_surprisal)
cmp_df_reading_surprisal$comp_task <- interaction(cmp_df_reading_surprisal$contrast, cmp_df_reading_surprisal$task)
cmp_df_reading_surprisal$percent_change_rt <- (cmp_df_reading_surprisal$estimate - 1)*100
cmp_df_reading_surprisal <- cmp_df_reading_surprisal %>% 
  mutate(significance = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"),
         significance_ribbon = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"),
         significance_line = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"))

cmp_df_reading_surprisal <- cmp_df_reading_surprisal |>
  arrange(task, comp_task, surprisal_2) |>
  group_by(task, comp_task) |>
  mutate(seg_id = cumsum(significance != dplyr::lag(significance, default = first(significance)))) |>
  ungroup()

# for adding vertical lines/geom_rect
sig_ranges <- cmp_df_reading_surprisal |>
  filter(significance == "significant") |>
  group_by(task, comp_task) |>
  summarise(
    x_start = min(surprisal_2),
    x_end   = max(surprisal_2),
    .groups = "drop")

(RT_comp_reading_stimtype_task_surprisal <- ggplot(subset(cmp_df_reading_surprisal, contrast != "Offline + Online - Offline"), aes(x = surprisal_2, y = percent_change_rt, colour = comp_task, fill = comp_task, group = interaction(comp_task, seg_id))) +
  #geom_rect(data = sig_ranges, aes(xmin = x_start, xmax = x_end, ymin = -Inf, ymax = Inf), inherit.aes = FALSE, fill  = "grey80", alpha = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "#3b4856", linewidth = 0.8, alpha = 0.7) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line)) + #aes(linetype = significance)
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_start), linetype = 2, colour = "black") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_end), linetype = 2, colour = "black") +
  facet_wrap(~ task, labeller = labeller(task = c("Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "Dual task")), scales = "free_x") +
  ylab("% change in RT") +
  xlab("Lexical surprisal") +
  scale_y_continuous(limits = c(-14, 13)) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_color_manual(values = cols_reading[c(2,3,5,6)]) +
  scale_fill_manual(values = cols_reading[c(2,3,5,6)]) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)
ggsave(RT_comp_reading_stimtype_task_surprisal, file = here(paste0("RT_comp_reading_stimtype_task_surprisal_", today, ".png")), width = 50, height = 50, units = "mm")

# also plot online+offline vs offline session
(RT_comp_reading_stimtype_task_surprisal_active <- ggplot(subset(cmp_df_reading_surprisal, contrast == "Offline + Online - Offline"), aes(x = surprisal_2, y = percent_change_rt, colour = comp_task, fill = comp_task, group = interaction(comp_task, seg_id))) +
  #geom_rect(data = sig_ranges, aes(xmin = x_start, xmax = x_end, ymin = -Inf, ymax = Inf), inherit.aes = FALSE, fill  = "grey80", alpha = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "#3b4856", linewidth = 0.8, alpha = 0.7) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line)) + #aes(linetype = significance)
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_start), linetype = 2, colour = "black") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_end), linetype = 2, colour = "black") +
  facet_wrap(~ task, labeller = labeller(task = c("Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "Dual task")), scales = "free_x") +
  ylab("% change in RT") +
  xlab("Lexical surprisal") +
  scale_y_continuous(limits = c(-14, 13)) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_color_manual(values = cols_reading[c(3,6)]) +
  scale_fill_manual(values = cols_reading[c(3,6)]) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)
ggsave(RT_comp_reading_stimtype_task_surprisal_active, file = here(paste0("RT_comp_reading_stimtype_task_surprisal_active_", today, ".png")), width = 50, height = 50, units = "mm")

##1c) Forest plot: stim type x task x surprisal ----
cmp_reading_surprisal_selected <- comparisons(
  gamm_reading,
  newdata = datagrid(
    surprisal_2 = c(10, 20, 30),
    stim_type = unique(mf$stim_type),
    task = unique(mf$task)
  ),
  variables = list(stim_type = "pairwise"),
  type = "link",
  transform = exp,
  exclude = rand_terms,
  comparison = "difference"
)

cmp_reading_surprisal_selected <- cmp_reading_surprisal_selected %>% 
  filter(contrast != "Offline + Online - Offline") %>% 
  filter(stim_type != "Sham") %>% 
  mutate(significance = case_when(p.value < 0.05 ~ "*", .default = ""),
         y_pos = surprisal_2 + case_when(
           contrast == "Offline - Sham"        ~  1,
           contrast == "Offline + Online - Sham" ~ -1,
           TRUE ~ 0),
         percent_change = (estimate-1)*100,
         CI_low_percent = (conf.low-1)*100,
         CI_high_percent = (conf.high-1)*100)
saveRDS(cmp_reading_surprisal_selected, file = here("RData/models/gamm_reading_comp_reading_surprisal_selected.rds"))

(RT_comp_reading_stimtype_surprisal_forest <- ggplot(cmp_reading_surprisal_selected, aes(x = percent_change, y = y_pos, color = interaction(contrast, task), group = contrast)) +
  geom_vline(xintercept = 0, color = "#3b4856", linetype = "dashed", linewidth = 0.8, alpha = 0.7) +
  geom_errorbar(aes(xmin = CI_low_percent, xmax = CI_high_percent), linewidth = .5, orientation = "y", width = 1) +
  geom_point(shape = 18, size = 4.5) +
  geom_text(aes(x = conf.high, label = significance), color = "#3b4856", nudge_x = 0.01, hjust = -0.1, vjust = 0.7, size = 5, show.legend = FALSE) +
  facet_wrap(~ task, labeller = labeller(task = c("Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "Dual task"))) +
  scale_color_manual(values = cols_reading[c(2,3,5,6)], labels = c("Offline", "Offline + Online"), name = "Condition") +
  scale_y_continuous(name = "Lexical surprisal", breaks = unique(cmp_reading_surprisal_selected$surprisal_2), labels = unique(cmp_reading_surprisal_selected$surprisal_2)) +
  scale_x_continuous(name = "% change in RT relative to Sham TMS", limits = c(-12, 12), breaks = c(-12, -6, 0, 6, 12)) +
  theme_bw(base_size = 9.5) +
  theme(panel.background  = element_blank(),
    panel.grid.major  = element_blank(),
    panel.grid.minor  = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(size = 10),
    text = element_text(family = "Helvetica"),
    axis.line = element_line(),
    axis.text = element_text(size = 8.5),
    #axis.title.x = element_text(size = 10),
    legend.position = "none")
)
ggsave(RT_comp_reading_stimtype_surprisal_forest, file = here(paste0("RT_comp_reading_stimtype_surprisal_forest_", today, ".png")), width = 50, height = 50, units = "mm")

##1d) Arrange plot ----
(figure_RT_reading_surprisal <- ggarrange(RT_reading_stimtype_task_surprisal,
                                   RT_comp_reading_stimtype_task_surprisal,
                                   nrow = 1))
ggsave(figure_RT_reading_surprisal, file = here(paste0("Plots/figure_RT_reading_surprisal_", today, ".pdf")), width = 120, height = 60, units = "mm")

#2) Two-way interaction stim_type x time from GAMM ----
# first build a grid for plotting and comparisons
sm_names <- smooths(gamm_reading)
rand_terms <- sm_names[grepl("participant|text_nr", sm_names)]
mf <- model.frame(gamm_reading)

stimtypes <- unique(mf$stim_type)

reading_grid_time <- do.call(
  rbind,
    lapply(stimtypes, function(ss) {
      mf_sub <- subset(mf, stim_type == ss)
      datagrid(
        model = gamm_reading,
        time_from_onset_task = seq(
          min(mf_sub$time_from_onset_task, na.rm = TRUE),
          max(mf_sub$time_from_onset_task, na.rm = TRUE),
          length.out = 100
        ),
        task       = levels(mf$task),
        stim_type  = ss,
        session    = levels(mf$session),
        punctuation = levels(mf$punctuation),
        is_trigger  = levels(mf$is_trigger),
        reaction    = levels(mf$reaction)
      )
  })
)

pred_time <- predictions(
  gamm_reading,
  newdata = reading_grid_time,
  by = c("time_from_onset_task", "stim_type"),
  type = "link",
  transform = exp,
  exclude = rand_terms
)
#pred_time$stim_task <- interaction(pred_time$stim_type, pred_time$task)
saveRDS(pred_time, file = here("RData/models/gamm_reading_pred_time.rds"))

# plot smooths for all stim types
(RT_reading_stimtype_time <- ggplot(pred_time, aes(x = time_from_onset_task, y = estimate, colour = stim_type, fill = stim_type)) +
    #geom_jitter2(data = slice_sample(reading_df, prop = .04), mapping = aes(x = time_from_onset_task, y = RT), alpha = 0.02) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
    geom_line(linewidth = 1.1) +
    #facet_wrap(~ task, labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task")), scales = "free_x") +
    ylab("Reaction time in ms") +
    xlab("Time since task onset in s") +
    scale_y_continuous(limits = c(300, 1200)) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 3), expand = expansion(mult = c(0.02, 0.15))) +
    #coord_cartesian(ylim = c(400, 1600)) +
    scale_color_manual(values = c("#b6b8dd", "#8a8cb0", "#575a7b")) +
  scale_fill_manual(values = c("#b6b8dd", "#8a8cb0", "#575a7b")) +
    theme_bw(base_size = 9.5)+
    theme(legend.position = "none",
          text = element_text(family = "Helvetica"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.background = element_blank(),
          strip.text = element_text(size = 10),
          axis.line = element_line(),
          axis.text.y = element_text(size = 8.5),
          #axis.title.x = element_blank(),
          axis.text.x.bottom = element_text(size = 8.5))
)

##2b) Comparison of different smooths ----
# calculate difference smooths
# takes quite a while to compute, better use pre-computed df
cmp_reading_time_NoTask <- marginaleffects::avg_comparisons(
  gamm_reading,
  newdata = reading_grid_time,
  variables = list(stim_type = "pairwise"),
  by = "time_from_onset_task",
  type = "link",
  transform = exp,
  comparison = "difference",
  exclude = rand_terms
)
saveRDS(cmp_reading_time_NoTask, file = here("RData/models/gamm_reading_comp_reading_time_NoTask.rds"))

cmp_df_reading_time <- as.data.frame(cmp_reading_time_NoTask) |>
  transmute(
    contrast,
    time_from_onset_task,
    estimate,
    conf.low,
    conf.high,
    p.value,
    percent_change_rt = (estimate - 1) * 100,
    significance = if_else(p.value < .05, "significant", "not significant")
  ) %>% 
  arrange(contrast, time_from_onset_task)

cmp_df_reading_time <- cmp_df_reading_time %>% 
  mutate(
    significance = case_when(
      p.value < 0.05 ~ "significant",
      TRUE ~ "not significant"
    ),
    significance_ribbon = significance,
    significance_line = significance
  ) %>% 
  arrange(contrast, time_from_onset_task) %>% 
  group_by(contrast) %>% 
  mutate(
    seg_id = cumsum(
      significance != lag(significance, default = first(significance))
      )) %>% 
  ungroup()

(RT_comp_reading_stimtype_time <- ggplot(subset(cmp_df_reading_time, contrast != "Offline + Online - Offline"), aes(x = time_from_onset_task, y = percent_change_rt, colour = contrast, fill = contrast)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon, group = interaction(contrast, seg_id)), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line, group = interaction(contrast, seg_id))) + #aes(linetype = significance)
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  ylab("% change in reaction time") +
  xlab("Time since task onset in s") +
  #scale_y_continuous(limits = c(300, 1200)) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 3), expand = expansion(mult = c(0.02, 0.15))) +
  scale_color_manual(values = c("#8a8cb0", "#575a7b")) +
  scale_fill_manual(values = c("#8a8cb0", "#575a7b")) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)

# also plot online+offline vs offline 
(RT_comp_reading_stimtype_time <- ggplot(subset(cmp_df_reading_time, contrast == "Offline + Online - Offline"), aes(x = time_from_onset_task, y = percent_change_rt, colour = contrast, fill = contrast)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon, group = interaction(contrast, seg_id)), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line, group = interaction(contrast, seg_id))) + #aes(linetype = significance)
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  ylab("% change in reaction time") +
  xlab("Time since task onset in s") +
  #scale_y_continuous(limits = c(300, 1200)) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 3), expand = expansion(mult = c(0.02, 0.15))) +
  scale_color_manual(values = c("#8a8cb0", "#575a7b")) +
  scale_fill_manual(values = c("#8a8cb0", "#575a7b")) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)

##2c) Arrange plots ----
(figure_RT_reading_time <- ggarrange(RT_reading_stimtype_time,
                                   RT_comp_reading_stimtype_time,
                                   nrow = 1))
ggsave(figure_RT_reading_time, file = here(paste0("Plots/figure_RT_reading_time_", today, ".pdf")), width = 100, height = 60, units = "mm")

#3) Main effects: time, surprisal, entropy, word length, frequency, previous duration, previous surprisal ----
## Surprisal ----
gamm_surprisal <- predict_response(gamm_reading, "surprisal_2", margin = "marginalmeans")

# Use the exact data/subset used to fit the model if possible
x_limits <- range(
  c(gamm_surprisal$x, reading_df$surprisal_2),
  na.rm = TRUE
)

surprisal_unique <- reading_df |>
  distinct(word, .keep_all = TRUE) |>
  filter(!is.na(surprisal_2))

(GAMM_surprisal <- ggplot(gamm_surprisal, aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.25, colour = NA, fill = "#272A50") +
  geom_line(linewidth = 1.5, colour = "#272A50") +
  ylab("Reading time in ms") +
  xlab("Lexical surprisal") +
  scale_x_continuous(limits = x_limits, breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  #scale_y_continuous(limits = c(300, 1200)) +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)

GAMM_surprisal_den <- ggplot(surprisal_unique, aes(x = surprisal_2)) +
  #geom_histogram(bins = 35, fill = "#272A50", colour = "white", linewidth = 0.15, alpha = 0.75) +
  geom_density(aes(y = after_stat(scaled)), fill = "#272A50", colour = "#272A50", alpha = 0.45, linewidth = 0.5, adjust = .8, trim = TRUE) +
  scale_x_continuous(limits = x_limits, breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  labs(x = "Lexical surprisal", y = "Density") +
  scale_y_continuous(limits = c(0,1), breaks = c(0,1)) +
  theme_bw(base_size = 9.5) +
  theme(
    legend.position = "none",
    text = element_text(family = "Helvetica"),
    panel.grid = element_blank(),
    axis.line = element_line(),
    #axis.title.y = element_blank(),
    #axis.ticks.y = element_blank(),
    #axis.text.y = element_blank(),
    axis.text = element_text(size = 8.5)
)

(plot_GAMM_surprisal <- GAMM_surprisal / GAMM_surprisal_den +
  plot_layout(heights = c(4, 1))
)

## Time ----
gamm_time <- predict_response(gamm_reading, "time_from_onset_task")

# Use the exact data/subset used to fit the model if possible
x_limits <- range(
  c(gamm_time$x, reading_df$time_from_onset_task),
  na.rm = TRUE
)

time_unique <- reading_df |>
  distinct(word, .keep_all = TRUE) |>
  filter(!is.na(time_from_onset_task))

(GAMM_time <- ggplot(gamm_time, aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.25, colour = NA, fill = "#272A50") +
  geom_line(linewidth = 1.5, colour = "#272A50") +
  ylab("Reading time in ms") +
  xlab("Time since task onset in s") +
  scale_x_continuous(limits = x_limits, breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  #scale_y_continuous(limits = c(300, 1200)) +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)

GAMM_time_den <- ggplot(time_unique, aes(x = time_from_onset_task)) +
  #geom_histogram(bins = 35, fill = "#272A50", colour = "white", linewidth = 0.15, alpha = 0.75) +
  geom_density(aes(y = after_stat(scaled)), fill = "#272A50", colour = "#272A50", alpha = 0.45, linewidth = 0.5, adjust = .8, trim = TRUE) +
  scale_x_continuous(limits = x_limits, breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  labs(x = "Time since task onset in s", y = "Density") +
  scale_y_continuous(limits = c(0,1), breaks = c(0,1)) +
  theme_bw(base_size = 9.5) +
  theme(
    legend.position = "none",
    text = element_text(family = "Helvetica"),
    panel.grid = element_blank(),
    axis.line = element_line(),
    #axis.title.y = element_blank(),
    #axis.ticks.y = element_blank(),
    #axis.text.y = element_blank(),
    axis.text = element_text(size = 8.5))

(plot_GAMM_time <- GAMM_time / GAMM_time_den +
  plot_layout(heights = c(4, 1))
)




## Entropy ----
gamm_entropy <- predict_response(gamm_reading, "entropy_2", margin = "marginalmeans")

# Use the exact data/subset used to fit the model if possible
x_limits <- range(
  c(gamm_entropy$x, reading_df$entropy_2),
  na.rm = TRUE
)

entropy_unique <- reading_df |>
  distinct(word, .keep_all = TRUE) |>
  filter(!is.na(entropy_2))

(GAMM_entropy <- ggplot(gamm_entropy, aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.25, colour = NA, fill = "#272A50") +
  geom_line(linewidth = 1.5, colour = "#272A50") +
  ylab("Reading time in ms") +
  xlab("Entropy") +
  scale_x_continuous(limits = x_limits, breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  #scale_y_continuous(limits = c(300, 1200)) +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)

GAMM_entropy_den <- ggplot(entropy_unique, aes(x = entropy_2)) +
  #geom_histogram(bins = 35, fill = "#272A50", colour = "white", linewidth = 0.15, alpha = 0.75) +
  geom_density(aes(y = after_stat(scaled)), fill = "#272A50", colour = "#272A50", alpha = 0.45, linewidth = 0.5, adjust = .8, trim = TRUE) +
  scale_x_continuous(limits = x_limits, breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  labs(x = "Entropy", y = "Density") +
  scale_y_continuous(limits = c(0,1), breaks = c(0,1)) +
  theme_bw(base_size = 9.5) +
  theme(
    legend.position = "none",
    text = element_text(family = "Helvetica"),
    panel.grid = element_blank(),
    axis.line = element_line(),
    #axis.title.y = element_blank(),
    #axis.ticks.y = element_blank(),
    #axis.text.y = element_blank(),
    axis.text = element_text(size = 8.5))

(plot_GAMM_entropy <- GAMM_entropy / GAMM_entropy_den +
  plot_layout(heights = c(4, 1))
)




## Frequency ----
gamm_frequency <- predict_response(gamm_reading, "zipf_frequency", margin = "marginalmeans")

# Use the exact data/subset used to fit the model if possible
x_limits <- range(
  c(gamm_frequency$x, reading_df$zipf_frequency),
  na.rm = TRUE
)

frequency_unique <- reading_df |>
  distinct(word, .keep_all = TRUE) |>
  filter(!is.na(zipf_frequency))

(GAMM_frequency <- ggplot(gamm_frequency, aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.25, colour = NA, fill = "#272A50") +
  geom_line(linewidth = 1.5, colour = "#272A50") +
  ylab("Reading time in ms") +
  xlab("Zipf frequency") +
  scale_x_continuous(limits = x_limits, breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  #scale_y_continuous(limits = c(300, 1200)) +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)

GAMM_frequency_den <- ggplot(frequency_unique, aes(x = zipf_frequency)) +
  #geom_histogram(bins = 35, fill = "#272A50", colour = "white", linewidth = 0.15, alpha = 0.75) +
  geom_density(aes(y = after_stat(scaled)), fill = "#272A50", colour = "#272A50", alpha = 0.45, linewidth = 0.5, adjust = .8, trim = TRUE) +
  scale_x_continuous(limits = x_limits, breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  labs(x = "Zipf frequency", y = "Density") +
  scale_y_continuous(limits = c(0,1), breaks = c(0,1)) +
  theme_bw(base_size = 9.5) +
  theme(
    legend.position = "none",
    text = element_text(family = "Helvetica"),
    panel.grid = element_blank(),
    axis.line = element_line(),
    #axis.title.y = element_blank(),
    #axis.ticks.y = element_blank(),
    #axis.text.y = element_blank(),
    axis.text = element_text(size = 8.5))

(plot_GAMM_frequency <- GAMM_frequency / GAMM_frequency_den +
  plot_layout(heights = c(4, 1))
)

## Word length ----
gamm_length <- predict_response(gamm_reading, "word_length_single", margin = "marginalmeans")

# Use the exact data/subset used to fit the model if possible
x_limits <- range(
  c(gamm_length$x, reading_df$word_length_single),
  na.rm = TRUE
)

length_unique <- reading_df |>
  distinct(word, .keep_all = TRUE) |>
  filter(!is.na(word_length_single))

(GAMM_length <- ggplot(gamm_length, aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.25, colour = NA, fill = "#272A50") +
  geom_line(linewidth = 1.5, colour = "#272A50") +
  ylab("Reading time in ms") +
  xlab("Word length in characters") +
  scale_x_continuous(limits = x_limits, breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  #scale_y_continuous(limits = c(300, 1200)) +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)

GAMM_length_den <- ggplot(length_unique, aes(x = word_length_single)) +
  #geom_histogram(bins = 35, fill = "#272A50", colour = "white", linewidth = 0.15, alpha = 0.75) +
  geom_density(aes(y = after_stat(scaled)), fill = "#272A50", colour = "#272A50", alpha = 0.45, linewidth = 0.5, adjust = .8, trim = TRUE) +
  scale_x_continuous(limits = x_limits, breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  labs(x = "Word length in characters", y = "Density") +
  scale_y_continuous(limits = c(0,1), breaks = c(0,1)) +
  theme_bw(base_size = 9.5) +
  theme(
    legend.position = "none",
    text = element_text(family = "Helvetica"),
    panel.grid = element_blank(),
    axis.line = element_line(),
    #axis.title.y = element_blank(),
    #axis.ticks.y = element_blank(),
    #axis.text.y = element_blank(),
    axis.text = element_text(size = 8.5))

(plot_GAMM_length <- GAMM_length / GAMM_length_den +
  plot_layout(heights = c(4, 1))
)


## Surprisal previous word ----
gamm_surprisal_prev <- predict_response(gamm_reading, "previous_surprisal_2", margin = "marginalmeans")

# Use the exact data/subset used to fit the model if possible
x_limits <- range(
  c(gamm_surprisal_prev$x, reading_df$previous_surprisal_2),
  na.rm = TRUE
)

surprisal_prev_unique <- reading_df |>
  distinct(word, .keep_all = TRUE) |>
  filter(!is.na(previous_surprisal_2))

(GAMM_surprisal_prev <- ggplot(gamm_surprisal_prev, aes(x = x, y = predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.25, colour = NA, fill = "#272A50") +
  geom_line(linewidth = 1.5, colour = "#272A50") +
  ylab("Reading time in ms") +
  xlab("Previous surprisal") +
  scale_x_continuous(limits = c(0.004880777,40), breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  coord_cartesian(ylim = c(650,900)) +
  #scale_y_continuous(limits = c(300, 1200)) +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)

GAMM_surprisal_prev_den <- ggplot(surprisal_prev_unique, aes(x = previous_surprisal_2)) +
  #geom_histogram(bins = 35, fill = "#272A50", colour = "white", linewidth = 0.15, alpha = 0.75) +
  geom_density(aes(y = after_stat(scaled)), fill = "#272A50", colour = "#272A50", alpha = 0.45, linewidth = 0.5, adjust = .8, trim = TRUE) +
  scale_x_continuous(limits = c(0.004880777,40), breaks = scales::pretty_breaks(n = 5), expand = expansion(mult = c(0.01, 0.01))) +
  labs(x = "Previous surprisal", y = "Density") +
  scale_y_continuous(limits = c(0,1), breaks = c(0,1)) +
  theme_bw(base_size = 9.5) +
  theme(
    legend.position = "none",
    text = element_text(family = "Helvetica"),
    panel.grid = element_blank(),
    axis.line = element_line(),
    #axis.title.y = element_blank(),
    #axis.ticks.y = element_blank(),
    #axis.text.y = element_blank(),
    axis.text = element_text(size = 8.5))

(plot_GAMM_surprisal_prev <- GAMM_surprisal_prev / GAMM_surprisal_prev_den +
  plot_layout(heights = c(4, 1))
)



# LMM plots ----
##1) stim type x task x surprisal ----

###1a) three-way interaction from LMM ----
mf <- model.frame(lmm_reading)
tasks     <- unique(mf$task)
stimtypes <- unique(mf$stim_type)

# build grid manually to make sure we only include surprisal values in predictions actually present in the different tasks and stimulation conditions (should be balanced)
reading_grid_surprisal <- do.call(
  rbind,
  lapply(tasks, function(tt) {
    lapply(stimtypes, function(ss) {
      mf_sub <- subset(mf, task == tt & stim_type == ss)

      datagrid(
        model = lmm_reading,
        surprisal_2 = seq(
          min(mf_sub$`scale(surprisal_2, scale = FALSE)`, na.rm = TRUE),
          max(mf_sub$`scale(surprisal_2, scale = FALSE)`, na.rm = TRUE),
          length.out = 100),
        task       = tt,
        stim_type  = ss,
        session    = levels(mf$session),
        punctuation = levels(mf$punctuation),
        is_trigger  = levels(mf$is_trigger),
        reaction    = levels(mf$reaction)
      )
    })
  }) |> unlist(recursive = FALSE)
)


pred_surprisal_lmm <- predictions(
  lmm_reading,
  newdata = reading_grid_surprisal,
  by = c("surprisal_2", "stim_type", "task"),
  type = "response",
  transform = exp,
  re.form = NA
)

# for plotting
reading_df$stim_task <- interaction(reading_df$stim_type, reading_df$task, drop = TRUE)
pred_surprisal_lmm$stim_task <- interaction(pred_surprisal_lmm$stim_type, pred_surprisal_lmm$task, drop = TRUE)

(RT_reading_stimtype_task_surprisal_lmm <- ggplot(pred_surprisal_lmm, aes(x = surprisal_2, y = estimate, colour = stim_task, fill = stim_task)) +
  geom_jitter2(data = slice_sample(reading_df, prop = 0.1), mapping = aes(x = surprisal_2, y = RT), alpha = 0.02) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
  geom_line(linewidth = 1.1) +
  facet_wrap(~ task, labeller = labeller(task = c("Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "Dual task"))) +
  ylab("Reading time in ms") +
  xlab("Lexical surprisal") +
  scale_y_continuous(limits = c(400, 1290)) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_color_manual(values = cols_reading) +
  scale_fill_manual(values = cols_reading) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 8.5))
)
ggsave(RT_reading_stimtype_task_surprisal, file = here(paste0("Plots/RT_reading_stimtype_task_surprisal_", today, ".png")), width = 90, height = 72, units = "mm")

###1b) Comparison of different smooths ----
cmp_reading_surprisal <- comparisons(
  lmm_reading,
  newdata = reading_grid_surprisal,
  variables = list(stim_type = "pairwise"),
  type = "response",
  transform = exp,
  re.form = NA,
  comparison = "difference",
  #hypothesis = difference ~ reference
)
# with transform = exp we get ratio, otherwise we get log ms
# interpretation: 
# ratio of 0.9999152 means: for one unit of surprisal, RT is 0.0000848% lower relative to sham, multiply this e.g. by 1000 s to get a better picture: 0.0848 --> after 1000s about 8.5% lower than sham

cmp_df_reading_surprisal <- as.data.frame(cmp_reading_surprisal)
cmp_df_reading_surprisal$comp_task <- interaction(cmp_df_reading_surprisal$contrast, cmp_df_reading_surprisal$task)
cmp_df_reading_surprisal$percent_change_rt <- (cmp_df_reading_surprisal$estimate - 1)*100
cmp_df_reading_surprisal <- cmp_df_reading_surprisal %>% 
  mutate(significance = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"),
         significance_ribbon = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"),
         significance_line = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"))

cmp_df_reading_surprisal <- cmp_df_reading_surprisal |>
  arrange(task, comp_task, surprisal_2) |>
  group_by(task, comp_task) |>
  mutate(seg_id = cumsum(significance != dplyr::lag(significance, default = first(significance)))) |>
  ungroup()

# for adding vertical lines/geom_rect
sig_ranges <- cmp_df_reading_surprisal |>
  filter(significance == "significant") |>
  group_by(task, comp_task) |>
  summarise(
    x_start = min(surprisal_2),
    x_end   = max(surprisal_2),
    .groups = "drop")

(RT_comp_reading_stimtype_task_surprisal <- ggplot(subset(cmp_df_reading_surprisal, contrast != "Offline + Online - Offline"), aes(x = surprisal_2, y = percent_change_rt, colour = comp_task, fill = comp_task, group = interaction(comp_task, seg_id))) +
  #geom_rect(data = sig_ranges, aes(xmin = x_start, xmax = x_end, ymin = -Inf, ymax = Inf), inherit.aes = FALSE, fill  = "grey80", alpha = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "#3b4856", linewidth = 0.8, alpha = 0.7) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line)) + #aes(linetype = significance)
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_start), linetype = 2, colour = "black") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_end), linetype = 2, colour = "black") +
  facet_wrap(~ task, labeller = labeller(task = c("Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "Dual task")), scales = "free_x") +
  ylab("% change in RT") +
  xlab("Lexical surprisal") +
  scale_y_continuous(limits = c(-14, 13)) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_color_manual(values = cols_reading[c(2,3,5,6)]) +
  scale_fill_manual(values = cols_reading[c(2,3,5,6)]) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "bottom",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)
ggsave(RT_comp_reading_stimtype_task_surprisal, file = here(paste0("RT_comp_reading_stimtype_task_surprisal_", today, ".png")), width = 50, height = 50, units = "mm")

# also plot online+offline vs offline session
(RT_comp_reading_stimtype_task_surprisal_active <- ggplot(subset(cmp_df_reading_surprisal, contrast == "Offline + Online - Offline"), aes(x = surprisal_2, y = percent_change_rt, colour = comp_task, fill = comp_task, group = interaction(comp_task, seg_id))) +
  #geom_rect(data = sig_ranges, aes(xmin = x_start, xmax = x_end, ymin = -Inf, ymax = Inf), inherit.aes = FALSE, fill  = "grey80", alpha = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "#3b4856", linewidth = 0.8, alpha = 0.7) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line)) + #aes(linetype = significance)
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_start), linetype = 2, colour = "black") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_end), linetype = 2, colour = "black") +
  facet_wrap(~ task, labeller = labeller(task = c("Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "Dual task")), scales = "free_x") +
  ylab("% change in RT") +
  xlab("Lexical surprisal") +
  scale_y_continuous(limits = c(-14, 13)) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_color_manual(values = cols_reading[c(3,6)]) +
  scale_fill_manual(values = cols_reading[c(3,6)]) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)
ggsave(RT_comp_reading_stimtype_task_surprisal_active, file = here(paste0("RT_comp_reading_stimtype_task_surprisal_active_", today, ".png")), width = 50, height = 50, units = "mm")

###1c) Forest plot: stim type x task x surprisal ----
cmp_reading_surprisal_selected <- comparisons(
  gamm_reading,
  newdata = datagrid(
    surprisal_2 = c(10, 20, 30),
    stim_type = unique(mf$stim_type),
    task = unique(mf$task)
  ),
  variables = list(stim_type = "pairwise"),
  type = "link",
  transform = exp,
  exclude = rand_terms,
  comparison = "difference"
)

cmp_reading_surprisal_selected <- cmp_reading_surprisal_selected %>% 
  filter(contrast != "Offline + Online - Offline") %>% 
  filter(stim_type != "Sham") %>% 
  mutate(significance = case_when(p.value < 0.05 ~ "*", .default = ""),
         y_pos = surprisal_2 + case_when(
           contrast == "Offline - Sham"        ~  1,
           contrast == "Offline + Online - Sham" ~ -1,
           TRUE ~ 0),
         percent_change = (estimate-1)*100,
         CI_low_percent = (conf.low-1)*100,
         CI_high_percent = (conf.high-1)*100)
saveRDS(cmp_reading_surprisal_selected, file = here("RData/models/gamm_reading_comp_reading_surprisal_selected.rds"))

(RT_comp_reading_stimtype_surprisal_forest <- ggplot(cmp_reading_surprisal_selected, aes(x = percent_change, y = y_pos, color = interaction(contrast, task), group = contrast)) +
  geom_vline(xintercept = 0, color = "#3b4856", linetype = "dashed", linewidth = 0.8, alpha = 0.7) +
  geom_errorbar(aes(xmin = CI_low_percent, xmax = CI_high_percent), linewidth = .5, orientation = "y", width = 1) +
  geom_point(shape = 18, size = 4.5) +
  geom_text(aes(x = conf.high, label = significance), color = "#3b4856", nudge_x = 0.01, hjust = -0.1, vjust = 0.7, size = 5, show.legend = FALSE) +
  facet_wrap(~ task, labeller = labeller(task = c("Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "Dual task"))) +
  scale_color_manual(values = cols_reading[c(2,3,5,6)], labels = c("Offline", "Offline + Online"), name = "Condition") +
  scale_y_continuous(name = "Lexical surprisal", breaks = unique(cmp_reading_surprisal_selected$surprisal_2), labels = unique(cmp_reading_surprisal_selected$surprisal_2)) +
  scale_x_continuous(name = "% change in RT relative to Sham TMS", limits = c(-12, 12), breaks = c(-12, -6, 0, 6, 12)) +
  theme_bw(base_size = 9.5) +
  theme(panel.background  = element_blank(),
    panel.grid.major  = element_blank(),
    panel.grid.minor  = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(size = 10),
    text = element_text(family = "Helvetica"),
    axis.line = element_line(),
    axis.text = element_text(size = 8.5),
    #axis.title.x = element_text(size = 10),
    legend.position = "none")
)
ggsave(RT_comp_reading_stimtype_surprisal_forest, file = here(paste0("RT_comp_reading_stimtype_surprisal_forest_", today, ".png")), width = 50, height = 50, units = "mm")

##2) Two-way interaction stim_type x time from LMM ----
# first build a grid for plotting and comparisons
mf <- model.frame(lmm_reading)
stimtypes <- unique(mf$stim_type)

reading_grid_time <- do.call(
  rbind,
    lapply(stimtypes, function(ss) {
      mf_sub <- subset(mf, stim_type == ss)
      datagrid(
        model = lmm_reading,
        time_from_onset_task = seq(
          min(mf_sub$`scale(time_from_onset_task, scale = FALSE)`, na.rm = TRUE),
          max(mf_sub$`scale(time_from_onset_task, scale = FALSE)`, na.rm = TRUE),
          length.out = 100
        ),
        task       = levels(mf$task),
        stim_type  = ss,
        session    = levels(mf$session),
        punctuation = levels(mf$punctuation),
        is_trigger  = levels(mf$is_trigger),
        reaction    = levels(mf$reaction)
      )
  })
)

pred_time_lmm <- predictions(
  lmm_reading,
  newdata = reading_grid_time,
  by = c("time_from_onset_task", "stim_type"),
  type = "response",
  transform = exp,
  re.form = NA
)

# plot smooths for all stim types
(RT_reading_stimtype_time <- ggplot(pred_time_lmm, aes(x = time_from_onset_task, y = estimate, colour = stim_type, fill = stim_type)) +
    geom_jitter2(data = slice_sample(reading_df, prop = .04), mapping = aes(x = time_from_onset_task, y = RT), alpha = 0.02) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
    geom_line(linewidth = 1.1) +
    #facet_wrap(~ task, labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task")), scales = "free_x") +
    ylab("Reaction time in ms") +
    xlab("Time since task onset in s") +
    scale_y_continuous(limits = c(300, 1200)) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 3), expand = expansion(mult = c(0.02, 0.15))) +
    #coord_cartesian(ylim = c(400, 1600)) +
    scale_color_manual(values = c("#b6b8dd", "#8a8cb0", "#575a7b")) +
  scale_fill_manual(values = c("#b6b8dd", "#8a8cb0", "#575a7b")) +
    theme_bw(base_size = 9.5)+
    theme(legend.position = "none",
          text = element_text(family = "Helvetica"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.background = element_blank(),
          strip.text = element_text(size = 10),
          axis.line = element_line(),
          axis.text.y = element_text(size = 8.5),
          #axis.title.x = element_blank(),
          axis.text.x.bottom = element_text(size = 8.5))
)

### Comparison of different smooths ----
cmp_reading_time_NoTask <- marginaleffects::avg_comparisons(
  lmm_reading,
  newdata = reading_grid_time,
  variables = list(stim_type = "pairwise"),
  by = "time_from_onset_task",
  type = "response",
  transform = exp,
  comparison = "difference",
  re.form = NA
)
saveRDS(cmp_reading_time_NoTask, file = here("RData/models/gamm_reading_comp_reading_time_NoTask.rds"))

cmp_df_reading_time <- as.data.frame(cmp_reading_time_NoTask) |>
  transmute(
    contrast,
    time_from_onset_task,
    estimate,
    conf.low,
    conf.high,
    p.value,
    percent_change_rt = (estimate - 1) * 100,
    significance = if_else(p.value < .05, "significant", "not significant")
  ) %>% 
  arrange(contrast, time_from_onset_task)

cmp_df_reading_time <- cmp_df_reading_time %>% 
  mutate(
    significance = case_when(
      p.value < 0.05 ~ "significant",
      TRUE ~ "not significant"
    ),
    significance_ribbon = significance,
    significance_line = significance
  ) %>% 
  arrange(contrast, time_from_onset_task) %>% 
  group_by(contrast) %>% 
  mutate(
    seg_id = cumsum(
      significance != lag(significance, default = first(significance))
      )) %>% 
  ungroup()

(RT_comp_reading_stimtype_time <- ggplot(subset(cmp_df_reading_time, contrast != "Offline + Online - Offline"), aes(x = time_from_onset_task, y = percent_change_rt, colour = contrast, fill = contrast)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon, group = interaction(contrast, seg_id)), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line, group = interaction(contrast, seg_id))) + #aes(linetype = significance)
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  ylab("% change in reaction time") +
  xlab("Time since task onset in s") +
  #scale_y_continuous(limits = c(300, 1200)) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 3), expand = expansion(mult = c(0.02, 0.15))) +
  scale_color_manual(values = c("#8a8cb0", "#575a7b")) +
  scale_fill_manual(values = c("#8a8cb0", "#575a7b")) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "bottom",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)

(RT_comp_reading_stimtype_time <- ggplot(subset(cmp_df_reading_time, contrast == "Offline + Online - Offline"), aes(x = time_from_onset_task, y = percent_change_rt, colour = contrast, fill = contrast)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon, group = interaction(contrast, seg_id)), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line, group = interaction(contrast, seg_id))) + #aes(linetype = significance)
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  ylab("% change in reaction time") +
  xlab("Time since task onset in s") +
  #scale_y_continuous(limits = c(300, 1200)) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 3), expand = expansion(mult = c(0.02, 0.15))) +
  scale_color_manual(values = c("#8a8cb0", "#575a7b")) +
  scale_fill_manual(values = c("#8a8cb0", "#575a7b")) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "bottom",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5))
)

##3) Parametric effects LMM ----
pred_lmm <- predictions(
  lmm_reading,
  by = c("stim_type", "task"),
  type = "response",
  transform = exp,
  re.form = NA
)
pred_lmm$stim_task <- interaction(pred_lmm$stim_type, pred_lmm$task, drop = TRUE)

stim_task_labels <- c(
  "Sham.Reading" = "Sham",
  "Offline.Reading" = "Offline",
  "Offline + Online.Reading" = "Offline+Online",
  "Sham.2-back dual" = "Sham",
  "Offline.2-back dual" = "Offline",
  "Offline + Online.2-back dual" = "Offline+Online"
)

(LMM_RT_reading_stim_type_task <- ggplot(pred_lmm, aes(x = stim_task, y = estimate, color = stim_task, group = stim_task, fill = stim_task)) +
  #geom_point(data = reading_df, mapping = aes(x = task, y = RT, color = stim_task), alpha = 1, position=position_jitterdodge()) +
  geom_point(position = position_dodge(width = 1), size = 3, shape = 23) +
  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high), width = 0.15, position = position_dodge(width = 1), linewidth = 1) +
  ylab("Reading time in ms") +
  xlab("Task") +
  #scale_y_continuous(limits = c(300, 950)) +
  #scale_x_discrete(labels = c("Reading", "Dual task")) +
  scale_x_discrete(labels = stim_task_labels) +
  coord_cartesian(ylim = c(380, 950)) +
  scale_color_manual(values = cols_reading) +
  scale_fill_manual(values = cols_reading) +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       #strip.text = element_blank(),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1))
)
ggsave(LMM_RT_reading_stim_type_task, file = here(paste0("Plots/LMM_RT_reading_stim_type_task_", today, ".pdf")), width = 50, height = 65, units = "mm")

##4) GAMM vs LMM ----
pred_surprisal_gamm <- pred_surprisal
pred_surprisal_lmm <- predictions(
  lmm_reading,
  newdata = reading_grid_surprisal,
  by = c("surprisal_2", "stim_type", "task"),
  type = "response",
  transform = exp,
  re.form = NA
)

pred_surprisal_gamm$stim_task <- interaction(pred_surprisal_gamm$stim_type, pred_surprisal_gamm$task, drop = TRUE)
pred_surprisal_gamm$model <- "GAMM"
pred_surprisal_lmm$stim_task <- interaction(pred_surprisal_lmm$stim_type, pred_surprisal_lmm$task, drop = TRUE)
pred_surprisal_lmm$model <- "LMM"

data_fig_models <- rbind(pred_surprisal_gamm, pred_surprisal_lmm)

(RT_reading_stimtype_task_surprisal_LMM_GAMM <- ggplot(data_fig_models, aes(x = surprisal_2, y = estimate, colour = stim_task, fill = stim_task)) +
  geom_jitter2(data = reading_df, mapping = aes(x = surprisal_2, y = RT), alpha = 0.1) +
  #geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
  geom_line(aes(linetype = model), linewidth = 1.5, color = "black") +
  facet_wrap(~ task + stim_type) +
  ylab("Reaction time in ms") +
  xlab("Lexical surprisal") +
  scale_y_continuous(limits = c(340, 1500)) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_color_manual(values = cols_reading) +
  #scale_fill_manual(values = cols_reading) +
  theme_bw(base_size = 10)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       #strip.text = element_blank(),
       axis.line = element_line(),
       axis.text.y = element_text(size = 9),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 9))
)




##4c) Main plots ----
(figure_RT_reading <- ggarrange(LMM_RT_reading_stim_type_task,
                                RT_reading_stimtype_task_surprisal +
                                  theme(axis.title.y = element_blank(),
                                  axis.text.y = element_blank(),
                                  axis.ticks.y = element_blank(),
                                  axis.line.y = element_blank()),
                                RT_reading_stimtype_task_time +
                                  theme(axis.title.y = element_blank(),
                                  axis.text.y = element_blank(),
                                  axis.ticks.y = element_blank(),
                                  axis.line.y = element_blank()),
                                nrow = 2, 
                                widths = c(0.35,1,1))
  
)
ggsave(figure_RT_reading, file = here(paste0("Plots/figure_RT_reading_", today, ".png")), width = 180, height = 65, units = "mm")

##4d) Difference smooths surprisal ----
(figure_RT_reading_surprisal <- ggarrange(RT_comp_reading_stimtype_task_surprisal,
                                RT_comp_reading_stimtype_surprisal_forest,
                                RT_comp_reading_stimtype_task_surprisal_active,
                                nrow = 1, 
                                widths = c(.85,1.05,.85))
  
)
ggsave(figure_RT_reading_surprisal, file = here(paste0("Plots/figure_RT_reading_surprisal_", today, ".pdf")), width = 180, height = 65, units = "mm")

##4e) Difference smooths time ----
(figure_RT_reading_time <- ggarrange(RT_comp_reading_stimtype_task_time,
                                RT_comp_reading_stimtype_time_forest,
                                RT_comp_reading_stimtype_task_time_active,
                                nrow = 1, 
                                widths = c(.85,1.05,.85))
  
)
ggsave(figure_RT_reading_time, file = here(paste0("Plots/figure_RT_reading_time_", today, ".pdf")), width = 180, height = 65, units = "mm")

##4f) Online TMS plot ----
(figure_RT_reading_online <- ggarrange(RT_reading_stimtype_task_time_online +
                                          theme(axis.title.x = element_blank()),
                                RT_comp_reading_stimtype_task_time_online +
                                  theme(axis.title.x = element_blank()),
                                nrow = 1)
  
)
ggsave(figure_RT_reading_online, file = here(paste0("Plots/figure_RT_reading_online_", today, ".pdf")), width = 120, height = 60, units = "mm")


# old stuff but maybe useful ----
pred_gamm_reading_RT_stimType_task_surprisal <- estimate_slopes(gamm_reading, by = c("stim_type", "task"), trend = "surprisal_2", transform = TRUE, backend = "marginalmeans", include_random = TRUE)

plot(pred_gamm_reading_RT_stimType_task_surprisal)

#pred_gamm_nback_RT_stimType_task2 <- avg_predictions(gamm_RT_only_nback, variables = c("task", "stim_type"), type = "response", transform = exp)
#plot_predictions(gamm_RT_only_nback, condition = c("stim_type", "task"), type = "response", transform = exp)

# plot the predicted values
(plot_gamm_nback_RT_stimType_task <- ggplot(pred_gamm_reading_RT_stimType_task_surprisal, aes(x = stim_type, y = Slope, color = task, fill = task)) +
   geom_point2(size = 3, position = position_dodge(width = 0.5)) +
   geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.2, position = position_dodge(width = 0.5)) +
   geom_line(aes(group = task), position = position_dodge(width = 0.5), alpha = 0.75, linetype = "dashed") +
   #geom_violinhalf(data = nback_only_nback_trials, aes(x = task, y = RT), position = position_dodge(width = 0.4), trim = T) +
   ylab("N-back reaction time in ms") +
   xlab("Stimulation condition") +
   #coord_cartesian(ylim=c(800, 1100)) +
   scale_color_manual(values = cols_nback) +  
   scale_fill_manual(values = cols_nback) +  
   theme_bw() +
   theme(legend.position = "bottom",
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         strip.background = element_blank(),
         axis.line = element_line(),
         #axis.title.y = element_text(size = 8),
         axis.text.y = element_text(size = 10),
         axis.text.x = element_text(size = 10))
         #axis.title = element_blank())
)

ggsave(plot_gamm_nback_RT_stimType_task, file = here::here("Plots/plot_gamm_nback_RT_stimType_task.rds"))

estimate_contrasts(gamm_reading, contrast = c("stim_type"), by = c("task"), transform = TRUE, p_adjust = "fdr", comparison = "reference", integer_as_continuous = TRUE, backend = "marginalmeans")

### Compare time slopes ----
slopes_gamm_nback_RT_stimType_time <- estimate_slopes(gamm_RT_only_nback, 
                                                      by = c("stim_type"), 
                                                      trend = "time_from_onset_session", 
                                                      transform = TRUE, # with transform = TRUE we get ratio, otherwise we get log ms
                                                      hypothesis = difference ~ reference, # gives us the difference in slope
                                                      multcomp = "holm") 
# interpretation: 
# ratio of 0.9999152 means: for one s RT is 0.0000848% lower relative to sham, multiply this e.g. by 1000 s to get a better picture: 0.0848 --> after 1000s about 8.5% lower than sham

# alternative that works equally well:
#estimate_contrasts(gamm_RT_only_nback, contrast = c("time_from_onset_session"), by = c("stim_type"), p_adjust = "fdr", comparison = "pairwise", integer_as_continuous = TRUE, backend = "emmeans", predict = "response", transform = T)

slopes_gamm_nback_RT_stimType_time
plot(slopes_gamm_nback_RT_stimType_time)

```

## ONLINE TMS: Reading time analysis ----
```{r}
reading_df_online <- subset(reading_df, is_trigger == "True")
reading_df_online <- droplevels(reading_df_online)

# new contrast coding for stim type since we're loosing one level
c <- contr.treatment(2) 
my.coding <- matrix(rep(1/2, 2), ncol = 1) 
my.simple <- c-my.coding

contrasts(reading_df_online$stim_type) <- my.simple

reading_df_online$reaction <- as.factor(reading_df_online$reaction)
contrasts(reading_df_online$reaction) <- my.simple

reading_df_online$task <- factor(reading_df_online$task, levels = c("Reading", "2-back dual"))
contrasts(reading_df_online$task) <- my.simple

# simple coding for session
c <- contr.treatment(3) 
my.coding <- matrix(rep(1/3, 6), ncol = 2) 
my.simple <- c-my.coding

reading_df_online$session <- as.factor(reading_df_online$session)
contrasts(reading_df_online$session) <- my.simple

# simple coding for punctuation (5 levels)
c <- contr.treatment(5) 
my.coding <- matrix(rep(1/5, 20), ncol = 4) 
my.simple <- c-my.coding

reading_df_online$punctuation <- as.factor(reading_df_online$punctuation)
contrasts(reading_df_online$punctuation) <- my.simple

## GAMM ----
reading_df_online <- reading_df_online %>% 
  ungroup() %>% 
  mutate(across(where(is.character), as.factor))

gamm_reading_online <- bam(log(RT) ~ 
            # parametric main effects and interactions (factors)  
              #stim_type + 
              #task +
              session + 
              reaction +
              punctuation +
              RS +
              executive_sum +
              education_years +
              Age +
              sideEffects_sum +
              #stim_type:task + 
            # non-parametric main effects (smooths)
              s(time_from_onset_task, k = 20) + 
              s(surprisal_2, k = 20) + 
              s(entropy_2, k = 30) +
              s(word_length_single, k = 20) + 
              s(zipf_frequency, k = 20) +
            # interactions
              s(stim_type, time_from_onset_task, bs = "sz", k = 20) + 
              s(task, time_from_onset_task, bs = "sz", k = 20) + 
              s(stim_type, task, time_from_onset_task, bs = "sz", k = 20) + 
              #s(time_from_onset_task, by = stimType_task, k = 20) +
              
              s(stim_type, surprisal_2, bs = "sz", k = 20) + 
              s(task, surprisal_2, bs = "sz", k = 20) + 
              s(stim_type, task, surprisal_2, bs = "sz", k = 20) + 
              #s(surprisal_2, by = stimType_task, k = 20) + 
            # random terms
              s(participant, bs = "re") +
              s(participant, stim_type, bs = "re") +
              s(participant, task, bs = "re") +  
              s(surprisal_2, participant, bs = "fs", k = 10) +
              s(time_from_onset_task, participant, bs = "fs") +
              s(text_nr, bs = "re"),
    data = reading_df_online,
    method = "fREML",
    discrete = TRUE,
    control = gam.control(nthreads = n.cores)
)

k.check(gamm_reading_online, n.rep = 1000)

summary(gamm_reading_online)

## LMM ----
lmm_reading_online <- lmerTest::lmer(log(RT) ~
                         stim_type +
                         session +
                         task +
                         reaction + 
                         punctuation +
                         scale(time_from_onset_task, scale = FALSE) +   
                         scale(RS, scale = FALSE) +
                         scale(executive_sum, scale = FALSE) +
                         scale(education_years, scale = FALSE) +
                         scale(Age, scale = FALSE) +
                         scale(sideEffects_sum, scale = FALSE) +
                         scale(surprisal_2, scale = FALSE) + # slope yes
                         scale(entropy_2, scale = FALSE) + # slope no
                         scale(zipf_frequency, scale = FALSE) + # slope no
                         scale(word_length_single, scale = FALSE) + # slope no
                         stim_type:task +
                         stim_type:scale(time_from_onset_task, scale = FALSE) +   
                         stim_type:scale(surprisal_2, scale = FALSE) +   
                         task:scale(surprisal_2, scale = FALSE) + 
                         task:scale(time_from_onset_task, scale = FALSE) + 
                         stim_type:task:scale(surprisal_2, scale = FALSE) +  
                         stim_type:task:scale(time_from_onset_task, scale = FALSE) +  
                         (1 + stim_type + task | participant),
                       data = reading_df_online,
                       REML = FALSE,
                       control = lmerControl(optimizer = "bobyqa")
)

summary(lmm_reading_online)
anova(lmm_reading_online)

# contrast stim_types by task:
estimate_contrasts(lmm_reading_online, contrast = "stim_type", by = "task", transform = T, estimate = "average", backend = "emmeans")

tab_model(lmm_reading_online, 
          gamm_reading_online, 
          show.intercept = FALSE,
          show.icc = TRUE,   # ICC (Intraclass Correlation) is not always needed
          show.re.var = TRUE,  # Show variance of random effects
          show.df = FALSE,     # Don't display degrees of freedom
          show.obs = TRUE,    # Don't display number of observations
          show.ngroups = FALSE, # Don't display number of groups for random effects
          show.stat = TRUE,    # Show model statistics (e.g., p-values, F-values)
          collapse.ci = TRUE,  # Collapse confidence intervals into one line
          show.std = "std", # Show standardized beta,
          df.method = "satterthwaite",
          file = here("reading_models_online.doc"))

plot(predict_response(lmm_reading_online, c("task", "stim_type"), margin = "marginalmeans"))
emmeans(lmm_reading_online, pairwise ~ stim_type * task, adjust = "none")
```

### Plots reading time models
```{r}
# GAMM plots ----
##1) ONLINE trials: stim type x task x time – three-way interaction from online trials GAMM ----
# first build a grid for plotting and comparisons
sm_names <- smooths(gamm_reading_online)
rand_terms <- sm_names[grepl("participant|text_nr", sm_names)]
mf <- model.frame(gamm_reading_online)

tasks     <- unique(mf$task)
stimtypes <- unique(mf$stim_type)

# for plotting
reading_df_online$stim_task <- interaction(reading_df_online$stim_type, reading_df_online$task, drop = TRUE)

# build grid manually to make sure we only include surprisal values in predictions actually present in the different tasks and stimulation conditions (should be balanced)
reading_grid_time_online <- do.call(
  rbind,
  lapply(tasks, function(tt) {
    lapply(stimtypes, function(ss) {
      mf_sub <- subset(mf, task == tt & stim_type == ss)

      datagrid(
        model = gamm_reading_online,
        time_from_onset_task = seq(
          min(mf_sub$time_from_onset_task, na.rm = TRUE),
          max(mf_sub$time_from_onset_task, na.rm = TRUE),
          length.out = 100
        ),
        task       = tt,
        stim_type  = ss,
        session    = levels(mf$session),
        punctuation = levels(mf$punctuation),
        reaction    = levels(mf$reaction)
      )
    })
  }) |> unlist(recursive = FALSE)
)

pred_time_online <- predictions(
  gamm_reading_online,
  newdata = reading_grid_time_online,
  by = c("time_from_onset_task", "stim_type", "task"),
  type = "link",
  transform = exp,
  exclude = rand_terms
)
#saveRDS(pred_surprisal, file = here("RData/models/gamm_reading_pred_surprisal.rds"))

pred_time_online$stim_task <- interaction(pred_time_online$stim_type, pred_time_online$task, drop = TRUE)

(RT_reading_stimtype_task_time_online <- ggplot(pred_time_online, aes(x = time_from_onset_task, y = estimate, colour = stim_task, fill = stim_task)) +
  #geom_jitter2(data = slice_sample(subset(reading_df, is_trigger == "True"), prop = 0.3), mapping = aes(x = surprisal_2, y = RT), alpha = 0.02) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
  geom_line(linewidth = 1.1) +
  facet_wrap(~ task, labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task")), scales = "free_x") +
  ylab("Reading time in ms") +
  xlab("Time since task onset in s") +
  scale_x_continuous(breaks = breaks_extended(n = 3)) +
  #coord_cartesian(ylim = c(400, 1250)) +
  scale_y_continuous(breaks = breaks_extended(n = 3)) +
  scale_color_manual(values = cols_reading[c(1, 3, 4, 6)]) +
  scale_fill_manual(values = cols_reading[c(1, 3, 4, 6)]) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 8.5, angle = 45, hjust = 1, vjust = 1))
)
ggsave(RT_reading_stimtype_task_surprisal_online, file = here(paste0("Plots/RT_reading_stimtype_task_surprisal_online_", today, ".pdf")), width = 60, height = 60, units = "mm")

### calculate difference smooths ----
cmp_reading_time_online <- comparisons(
  gamm_reading_online,
  newdata = reading_grid_time_online,
  variables = list(stim_type = "pairwise"),
  type = "link",
  transform = exp,
  exclude = rand_terms,
  #cross = TRUE
  comparison = "difference"
  #hypothesis = stim_type * task
)

# with transform = exp we get ratio, otherwise we get log ms
# interpretation: 
# ratio of 0.9999152 means: for one unit of surprisal, RT is 0.0000848% lower relative to sham, multiply this e.g. by 1000 s to get a better picture: 0.0848 --> after 1000s about 8.5% lower than sham

cmp_df_reading_time_online <- as.data.frame(cmp_reading_time_online)
cmp_df_reading_time_online$comp_task <- interaction(cmp_df_reading_time_online$contrast, cmp_df_reading_time_online$task)
cmp_df_reading_time_online$percent_change_rt <- (cmp_df_reading_time_online$estimate - 1)*100
cmp_df_reading_time_online <- cmp_df_reading_time_online %>% 
  mutate(significance = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"),
         significance_ribbon = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"),
         significance_line = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"))

cmp_df_reading_time_online <- cmp_df_reading_time_online %>% 
  arrange(task, comp_task, time_from_onset_task) %>% 
  group_by(task, comp_task) %>% 
  mutate(seg_id = cumsum(significance != dplyr::lag(significance, default = first(significance)))) %>% 
  ungroup()

(RT_comp_reading_stimtype_task_time_online <- ggplot(cmp_df_reading_time_online, aes(x = time_from_onset_task, y = percent_change_rt, colour = comp_task, fill = comp_task, group = interaction(comp_task, seg_id))) +
  #geom_rect(data = sig_ranges, aes(xmin = x_start, xmax = x_end, ymin = -Inf, ymax = Inf), inherit.aes = FALSE, fill  = "grey80", alpha = 0.25) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "#3b4856", linewidth = 0.8, alpha = 0.7) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line)) + #aes(linetype = significance)
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_start), linetype = 2, colour = "black") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_end), linetype = 2, colour = "black") +
  facet_wrap(~ task, labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task")), scales = "free_x") +
  ylab("% change in RT") +
  xlab("Time since task onset in s") +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_x_continuous(breaks = breaks_extended(n = 3)) +
  scale_y_continuous(breaks = breaks_extended(n = 3)) +
  scale_color_manual(values = cols_reading[c(3,6)]) +
  scale_fill_manual(values = cols_reading[c(3,6)]) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5, angle = 45, hjust = 1, vjust = 1))
)

# old 
pr <- predict_response(gamm_reading_online, c("surprisal_2", "stim_type", "task"), back_transform = )
df_pred <- pr %>%
  as.data.frame() %>% 
  rename(
    stim_type   = group,        
    task        = facet,   
    surprisal_2 = x    
  ) %>%
  select(stim_type, task, surprisal_2,
         predicted, conf.low, conf.high)
df_wide <- df_pred %>%
  pivot_wider(
    names_from = c(stim_type, task),
    values_from = c(predicted, conf.low, conf.high)
  )
df_interact <- df_wide %>%
  mutate(
    `ratio_Offline + Online_Sham_Reading` = `predicted_Offline + Online_Reading` / predicted_Sham_Reading,
    `ratio_Offline + Online_Sham_2-back dual` = `predicted_Offline + Online_2-back dual` / `predicted_Sham_2-back dual`,
    interaction_ratio = `ratio_Offline + Online_Sham_2-back dual` / `ratio_Offline + Online_Sham_Reading`,
    percent_change_interaction = (interaction_ratio - 1) * 100
  )
ggplot(df_interact,
       aes(x = surprisal_2,
           y = percent_change_interaction)) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_line(linewidth = 1.2) +
  ylab("% change (interaction A vs B, X vs Y)") +
  xlab("Lexical surprisal") +
  theme_bw()


# LMM plots ----
##1) Parametric effects Online Trials LMM ----
pred_lmm_online <- predictions(
  lmm_reading_online,
  by = c("stim_type", "task"),
  type = "response",
  transform = exp,
  re.form = NA
)
pred_lmm_online$stim_task <- interaction(pred_lmm_online$stim_type, pred_lmm_online$task, drop = TRUE)

stim_task_labels <- c(
  "Sham.Reading" = "Sham",
  "Offline + Online.Reading" = "Active",
  "Sham.2-back dual" = "Sham",
  "Offline + Online.2-back dual" = "Active"
)

(LMM_RT_reading_stim_type_task_online <- ggplot(pred_lmm_online, aes(x = stim_task, y = estimate, color = stim_task, group = stim_task, fill = stim_task)) +
  #geom_point(data = reading_df, mapping = aes(x = task, y = RT, color = stim_task), alpha = 1, position=position_jitterdodge()) +
  geom_point(position = position_dodge(width = 1), size = 3, shape = 23) +
  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high), width = 0.15, position = position_dodge(width = 1), linewidth = 1) +
  ylab("Reading time in ms") +
  xlab("Task") +
  scale_y_continuous(limits = c(300, 1100)) +
  #scale_x_discrete(labels = c("Reading", "Dual task")) +
  scale_x_discrete(labels = stim_task_labels) +
  #coord_cartesian(ylim = c(380, 950)) +
  scale_color_manual(values = cols_reading[c(1,3,4,6)]) +
  scale_fill_manual(values = cols_reading[c(1,3,4,6)]) +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       #strip.text = element_blank(),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1))
)
ggsave(LMM_RT_reading_stim_type_task_online, file = here(paste0("Plots/LMM_RT_reading_stim_type_task_online_", today, ".pdf")), width = 50, height = 57, units = "mm")



##4f) Online TMS plot ----
(figure_RT_reading_online <- ggarrange(RT_reading_stimtype_task_time_online +
                                          theme(axis.title.x = element_blank()),
                                RT_comp_reading_stimtype_task_time_online +
                                  theme(axis.title.x = element_blank()),
                                nrow = 1)
  
)
ggsave(figure_RT_reading_online, file = here(paste0("Plots/figure_RT_reading_online_", today, ".pdf")), width = 120, height = 60, units = "mm")


# old stuff but maybe useful ----
pred_gamm_reading_RT_stimType_task_surprisal <- estimate_slopes(gamm_reading, by = c("stim_type", "task"), trend = "surprisal_2", transform = TRUE, backend = "marginalmeans", include_random = TRUE)

plot(pred_gamm_reading_RT_stimType_task_surprisal)

#pred_gamm_nback_RT_stimType_task2 <- avg_predictions(gamm_RT_only_nback, variables = c("task", "stim_type"), type = "response", transform = exp)
#plot_predictions(gamm_RT_only_nback, condition = c("stim_type", "task"), type = "response", transform = exp)

# plot the predicted values
(plot_gamm_nback_RT_stimType_task <- ggplot(pred_gamm_reading_RT_stimType_task_surprisal, aes(x = stim_type, y = Slope, color = task, fill = task)) +
   geom_point2(size = 3, position = position_dodge(width = 0.5)) +
   geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.2, position = position_dodge(width = 0.5)) +
   geom_line(aes(group = task), position = position_dodge(width = 0.5), alpha = 0.75, linetype = "dashed") +
   #geom_violinhalf(data = nback_only_nback_trials, aes(x = task, y = RT), position = position_dodge(width = 0.4), trim = T) +
   ylab("N-back reaction time in ms") +
   xlab("Stimulation condition") +
   #coord_cartesian(ylim=c(800, 1100)) +
   scale_color_manual(values = cols_nback) +  
   scale_fill_manual(values = cols_nback) +  
   theme_bw() +
   theme(legend.position = "bottom",
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         strip.background = element_blank(),
         axis.line = element_line(),
         #axis.title.y = element_text(size = 8),
         axis.text.y = element_text(size = 10),
         axis.text.x = element_text(size = 10))
         #axis.title = element_blank())
)

ggsave(plot_gamm_nback_RT_stimType_task, file = here::here("Plots/plot_gamm_nback_RT_stimType_task.rds"))

estimate_contrasts(gamm_reading, contrast = c("stim_type"), by = c("task"), transform = TRUE, p_adjust = "fdr", comparison = "reference", integer_as_continuous = TRUE, backend = "marginalmeans")

### Compare time slopes ----
slopes_gamm_nback_RT_stimType_time <- estimate_slopes(gamm_RT_only_nback, 
                                                      by = c("stim_type"), 
                                                      trend = "time_from_onset_session", 
                                                      transform = TRUE, # with transform = TRUE we get ratio, otherwise we get log ms
                                                      hypothesis = difference ~ reference, # gives us the difference in slope
                                                      multcomp = "holm") 
# interpretation: 
# ratio of 0.9999152 means: for one s RT is 0.0000848% lower relative to sham, multiply this e.g. by 1000 s to get a better picture: 0.0848 --> after 1000s about 8.5% lower than sham

# alternative that works equally well:
#estimate_contrasts(gamm_RT_only_nback, contrast = c("time_from_onset_session"), by = c("stim_type"), p_adjust = "fdr", comparison = "pairwise", integer_as_continuous = TRUE, backend = "emmeans", predict = "response", transform = T)

slopes_gamm_nback_RT_stimType_time
plot(slopes_gamm_nback_RT_stimType_time)

```

## Check specificity of surprisal vs other lexical predictors
```{r}
reading_df <- reading_df %>% 
  mutate(across(where(is.character), as.factor))

# ORIGINAL GAMM (SURPRISAL) ----
gamm_reading_orig <- bam(log(RT) ~ 
            # parametric main effects and interactions (factors)  
              #stim_type + 
              #task +
              session + 
              is_trigger + 
              reaction +
              punctuation +
              RS +
              executive_sum +
              education_years +
              Age +
              sideEffects_sum +
              #stim_type:task + 
            # non-parametric main effects (smooths)
              s(time_from_onset_task, k = 20) + 
              s(surprisal_2, k = 20) + 
              s(entropy_2, k = 30) +
              s(word_length_single, k = 20) + 
              s(zipf_frequency, k = 20) +
              s(log(previous_duration), k = 50) +
              s(previous_surprisal_2, k = 20) + 
            # interactions
              s(stim_type, time_from_onset_task, bs = "sz", k = 20) + 
              s(task, time_from_onset_task, bs = "sz", k = 20) + 
              s(stim_type, task, time_from_onset_task, bs = "sz", k = 20) + 
              #s(time_from_onset_task, by = stimType_task, k = 20) + # old way of writing the interaction term
              
              s(stim_type, surprisal_2, bs = "sz", k = 20) + 
              s(task, surprisal_2, bs = "sz", k = 20) + 
              s(stim_type, task, surprisal_2, bs = "sz", k = 20) + 
              #s(surprisal_2, by = stimType_task, k = 20) + # old way of writing the interaction term
            # random terms
              s(participant, bs = "re") +
              s(participant, stim_type, bs = "re") +
              s(participant, task, bs = "re") +  
              #s(surprisal_2, participant, bs = "fs", k = 10) +
              s(time_from_onset_task, participant, bs = "fs") +
              s(text_nr, bs = "re"),
    data = reading_df,
    #family = Gamma(link = "log"),
    method = "fREML",
    discrete = TRUE,
    control = gam.control(nthreads = n.cores)
)

gam.check(gamm_reading_orig, k.rep = 1000)

summary(gamm_reading_orig)

# ENTROPY ----
gamm_entropy <- bam(log(RT) ~ 
            # parametric main effects and interactions (factors)  
              #stim_type + 
              #task +
              session + 
              is_trigger + 
              reaction +
              punctuation +
              RS +
              executive_sum +
              education_years +
              Age +
              sideEffects_sum +
              #stim_type:task + 
            # non-parametric main effects (smooths)
              s(time_from_onset_task, k = 20) + 
              s(surprisal_2, k = 20) + 
              s(entropy_2, k = 30) +
              s(word_length_single, k = 20) + 
              s(zipf_frequency, k = 20) +
              s(log(previous_duration), k = 50) +
              s(previous_surprisal_2, k = 20) + 
            # interactions
              s(stim_type, time_from_onset_task, bs = "sz", k = 20) + 
              s(task, time_from_onset_task, bs = "sz", k = 20) + 
              s(stim_type, task, time_from_onset_task, bs = "sz", k = 20) + 
              #s(time_from_onset_task, by = stimType_task, k = 20) + # old way of writing the interaction term
              
              s(stim_type, entropy_2, bs = "sz", k = 20) + 
              s(task, entropy_2, bs = "sz", k = 20) + 
              s(stim_type, task, entropy_2, bs = "sz", k = 20) + 
              #s(surprisal_2, by = stimType_task, k = 20) + # old way of writing the interaction term
            # random terms
              s(participant, bs = "re") +
              s(participant, stim_type, bs = "re") +
              s(participant, task, bs = "re") +  
              #s(surprisal_2, participant, bs = "fs", k = 10) +
              s(time_from_onset_task, participant, bs = "fs") +
              s(text_nr, bs = "re"),
    data = reading_df,
    #family = Gamma(link = "log"),
    method = "fREML",
    discrete = TRUE,
    control = gam.control(nthreads = n.cores)
)

gam.check(gamm_entropy, k.rep = 1000)

summary(gamm_entropy)

# Surprisal vs Entropy ----
compare_performance(gamm_reading_orig, gamm_entropy, rank = TRUE)

AIC(gamm_reading_orig, gamm_entropy) # surprisal model performs better

# WORD LENGTH ----
gamm_word_length <- bam(log(RT) ~ 
            # parametric main effects and interactions (factors)  
              #stim_type + 
              #task +
              session + 
              is_trigger + 
              reaction +
              punctuation +
              RS +
              executive_sum +
              education_years +
              Age +
              sideEffects_sum +
              #stim_type:task + 
            # non-parametric main effects (smooths)
              s(time_from_onset_task, k = 20) + # we don't need this because of its interaction with the unordered factor for stim_type
              s(surprisal_2, k = 20) + # we don't need this because of its interaction with the unordered factor for stim_type
              s(entropy_2, k = 30) +
              s(word_length_single, k = 20) + 
              s(zipf_frequency, k = 20) +
              s(log(previous_duration), k = 35) +
              s(previous_surprisal_2, k = 20) + 
            # interactions
              s(stim_type, time_from_onset_task, bs = "sz", k = 20) + 
              s(task, time_from_onset_task, bs = "sz", k = 20) + 
              s(stim_type, task, time_from_onset_task, bs = "sz", k = 20) + 
              #s(time_from_onset_task, by = stimType_task, k = 20) +
              
              s(stim_type, word_length_single, bs = "sz", k = 20) + 
              s(task, word_length_single, bs = "sz", k = 20) + 
              s(stim_type, task, word_length_single, bs = "sz", k = 20) + 
              #s(surprisal_2, by = stimType_task, k = 20) + 
            # random terms
              s(participant, bs = "re") +
              s(participant, stim_type, bs = "re") +
              s(participant, task, bs = "re") +  
              #s(word_length_single, participant, bs = "fs", k = 10) +
              s(time_from_onset_task, participant, bs = "fs") +
              s(text_nr, bs = "re"),
    data = reading_df,
    #family = Gamma(link = "log"),
    method = "fREML",
    discrete = TRUE,
    control = gam.control(nthreads = n.cores)
)

gam.check(gamm_word_length, k.rep = 1000)

summary(gamm_word_length)


# FREQUENCY ----
gamm_frequency <- bam(log(RT) ~ 
            # parametric main effects and interactions (factors)  
              #stim_type + 
              #task +
              session + 
              is_trigger + 
              reaction +
              punctuation +
              RS +
              executive_sum +
              education_years +
              Age +
              sideEffects_sum +
              #stim_type:task + 
            # non-parametric main effects (smooths)
              s(time_from_onset_task, k = 20) + # we don't need this because of its interaction with the unordered factor for stim_type
              s(surprisal_2, k = 20) + # we don't need this because of its interaction with the unordered factor for stim_type
              s(entropy_2, k = 30) +
              s(word_length_single, k = 20) + 
              s(zipf_frequency, k = 20) +
              s(log(previous_duration), k = 35) +
              s(previous_surprisal_2, k = 20) + 
            # interactions
              s(stim_type, time_from_onset_task, bs = "sz", k = 20) + 
              s(task, time_from_onset_task, bs = "sz", k = 20) + 
              s(stim_type, task, time_from_onset_task, bs = "sz", k = 20) + 
              #s(time_from_onset_task, by = stimType_task, k = 20) +
              
              s(stim_type, zipf_frequency, bs = "sz", k = 20) + 
              s(task, zipf_frequency, bs = "sz", k = 20) + 
              s(stim_type, task, zipf_frequency, bs = "sz", k = 20) + 
              #s(surprisal_2, by = stimType_task, k = 20) + 
            # random terms
              s(participant, bs = "re") +
              s(participant, stim_type, bs = "re") +
              s(participant, task, bs = "re") +  
              #s(zipf_frequency, participant, bs = "fs", k = 10) +
              s(time_from_onset_task, participant, bs = "fs") +
              s(text_nr, bs = "re"),
    data = reading_df,
    #family = Gamma(link = "log"),
    method = "fREML",
    discrete = TRUE,
    control = gam.control(nthreads = n.cores)
)

gam.check(gamm_frequency, k.rep = 1000)

summary(gamm_frequency)


# MODEL COMPARISON
compare_performance(gamm_reading_orig, 
                    gamm_entropy,
                    gamm_frequency,
                    gamm_word_length, 
                    rank = TRUE)

AIC(gamm_reading_orig, gamm_entropy, gamm_frequency, gamm_word_length)
```


## Comprehension question accuracy
```{r}
# Question-wise analysis ----
df_comprehension_Qs <- readRDS(here::here("RData/df_comprehension_questions.rds"))

df_comprehension_Qs$participant <- str_pad(df_comprehension_Qs$participant, width = 2, side = "left", pad = "0")
reading_subset <- reading_df %>% 
  select(participant, stim_type, session, task, block_nr_exp, text_nr, education_years, Age, RS, executive_sum, sideEffects_sum) %>% 
  distinct()
df_comprehension_Qs <- full_join(reading_subset, df_comprehension_Qs)
df_comprehension_Qs$ans_correct <- as.factor(df_comprehension_Qs$ans_correct)
df_comprehension_Qs <- df_comprehension_Qs %>% 
  filter(!is.na(stim_type)) # exclude blocks from participants also excluded from the main analysis
df_comprehension_Qs$stim_task <- interaction(df_comprehension_Qs$stim_type, df_comprehension_Qs$task)

glmer_question_acc <- glmmTMB(ans_correct ~ 
    stim_type +
    task +
    session +
    scale(block_nr_exp, scale = FALSE) +
    scale(education_years, scale = FALSE) +
    scale(Age, scale = FALSE) +
    scale(executive_sum, scale = FALSE) +
    scale(RS, scale = FALSE) +
    scale(sideEffects_sum, scale = FALSE) +
    stim_type:task +
    (1 + stim_type + task || participant) +
    (1 | text_nr),
  data = df_comprehension_Qs, 
  family = binomial(link = "logit"),
)

summary(glmer_question_acc)
Anova(glmer_question_acc, type = 3)

pred_glmm_questions <- predict_response(glmer_question_acc, c("stim_type", "task"), margin = "marginalmeans", bias_correction = TRUE)

pred_glmm_questions <- pred_glmm_questions %>% 
  mutate(
    stim_type = x,
    task = group,
    stim_task = interaction(stim_type, task)
  ) %>% 
  filter(!is.na(x))

(GLMM_questions_stim_type_task <- ggplot(pred_glmm_questions, aes(x = x, y = predicted*100, color = stim_task, fill = stim_task)) +
  geom_jitter(data = df_comprehension_Qs, mapping = aes(x = stim_type, y = question_acc*100, color = stim_task), alpha = 0.05, position = position_jitterdodge(dodge.width = 1, jitter.width = 0.5)) +
  geom_point(size = 3.5, shape = 23) +
  geom_errorbar(mapping = aes(ymin = conf.low*100, ymax = conf.high*100), width = 0.15, linewidth = 1) +
  ylab("Question accuracy in %") +
  xlab("Task") +
  #scale_y_continuous(limits = c(400, 1290)) +
  #scale_y_continuous(limits = c(450, 1100)) +
  #scale_x_discrete(labels = c("Reading", "Dual task")) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_color_manual(values = cols_reading) +
  scale_fill_manual(values = cols_reading) +
  facet_wrap(~ task, scales = "free_x", labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task"))) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, hjust = 1, vjust = 1))
)
ggsave(GLMM_questions_stim_type_task, file = here(paste0("Plots/GLMM_questions_stim_type_task_", today, ".pdf")), width = 60, height = 65, units = "mm")

# tab model together for question accuracy and d-prime
tab_model(glmer_question_acc,
          lmm_nback_dprime,
  show.intercept = FALSE,
  show.icc = TRUE,   # ICC (Intraclass Correlation) is not always needed
  show.re.var = TRUE,  # Show variance of random effects
  show.df = FALSE,     # Don't display degrees of freedom
  show.obs = TRUE,    # Don't display number of observations
  show.ngroups = FALSE, # Don't display number of groups for random effects
  show.stat = TRUE,    # Show model statistics (e.g., p-values, F-values)
  collapse.ci = TRUE,  # Collapse confidence intervals into one line
  show.std = "std", # Show standardized beta,
  df.method = "satterthwaite",
  dv.labels = c("´Question accuracy", "D-prime"),
  file = here("Model_tables/accuracy_models.doc")
)

# Old: analysis of % correct (doesn't matter though, no TMS effects) ----
quest_acc_df <- reading_df %>% 
  select(participant, stim_type, task, session, cognitive_load, question_acc, sideEffects_sum, block_nr_exp, RS, executive_sum, education_years, Age, task_onset, text_nr) %>% 
  distinct()

ggplot(quest_acc_df, aes(x = stim_type, y = question_acc*100)) +
  geom_boxplot()

## GAMM ----
quest_acc_df <- quest_acc_df %>% 
  ungroup() %>% 
  mutate(across(where(is.character), as.factor))

gamm_quest_acc <- bam(question_acc ~
                         stim_type +
                         session +
                         task +
                         s(block_nr_exp, k = 10) + 
                         RS +
                         executive_sum +
                         education_years +
                         Age +
                         sideEffects_sum +
                         stim_type:task +
                         s(participant, bs = "re") +
                         s(participant, by = stim_type, bs = "re") +
                         s(participant, by = task, bs = "re") +
                         s(text_nr, bs = "re"),
              data = quest_acc_df,
              method = "fREML",
              discrete = TRUE,
              control = gam.control(nthreads = n.cores),
)

k.check(gamm_quest_acc, n.rep = 1000)

summary(gamm_quest_acc)

## LMM on percent accuracy ----
reading_quest_acc <- lmerTest::lmer(question_acc ~
    stim_type +
    session +
    task +
    stim_type:task +
    scale(block_nr_exp, scale = FALSE) +
    scale(education_years, scale = FALSE) +
    scale(Age, scale = FALSE) +
    scale(executive_sum, scale = FALSE) +
    scale(RS, scale = FALSE) +
    scale(sideEffects_sum, scale = FALSE) +
    (1 | participant) +
    (1 | text_nr),
  data = quest_acc_df, 
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(reading_quest_acc)
```

## Raw Data Plots
### Plot RTs
```{r plot single n-back tasks}
reading_df <- subset(reading_df, !is.na(surprisal_2))
reading_df <- subset(reading_df, surprisal_2 < 40)
reading_df <- reading_df %>% 
  mutate(task = dplyr::recode(task, "Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))

# Summary df by condition
reading_df_summary <- reading_df %>% 
  group_by(stim_type, task) %>%
  summarise(mean_rt = mean(RT),
            SD_rt = sd(RT),
            std.error_rt = std.error(RT)) %>% 
  mutate(task = factor(task, levels = c("Reading", "2-back dual")),
         stim_type = factor(stim_type, levels = c("Sham", "Offline", "Offline + Online")))
#reading_df_summary$stim_task <- interaction(reading_df_summary$stim_type, reading_df_summary$task, drop = TRUE)

RT_reading_part <- reading_df %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_rt = mean(RT)) %>% 
  mutate(task = factor(task, levels = c("Reading", "2-back dual")),
         stim_type = factor(stim_type, levels = c("Sham", "Offline", "Offline + Online")))
RT_reading_part$stim_task <- interaction(RT_reading_part$stim_type, RT_reading_part$task, drop = TRUE)

#1) Boxplot of RTs by Task and Stimulation ----
(RT_reading_raw_boxplot <- ggplot(reading_df_summary, aes(x = stim_type, y = mean_rt, group = task)) +
    #geom_bar(aes(), stat = "identity", width = 0.5) +
    #geom_errorbar(aes(ymin = mean_rt - std.error_rt, ymax = mean_rt + std.error_rt), width =0.07, linewidth=0.7) +
    geom_boxplot(RT_reading_part, mapping = aes(x = stim_type, y = mean_rt, fill = stim_task, group = stim_task)) +
    geom_point2(shape = 18, size = 2, position = position_dodge(width = 0.75)) +
    geom_line(aes(x = stim_type, y = mean_rt, group = 1), color="black", linetype="dotted", position = position_dodge(width = 0.75))+
    scale_fill_manual(values = cols_reading) +
    scale_color_manual(values = cols_reading) +
    #scale_y_continuous(limits = c(250, 1290), breaks = c(400, 800, 1200)) +
    scale_x_discrete(labels = c(rep(c("Sham", "Offline", "Offline+Online"), 2))) +
    coord_cartesian(ylim = c(250, 1550)) +
    facet_grid(~ task, scales = "free_x", space = "free_x") +
    ylab("Reading Time in ms") +
    xlab("Task") +
    theme_bw(base_size = 9.5)+
    theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1)) 
)

#2) Violin plot with individual participant lines
(RT_reading_raw_violin <- ggplot(RT_reading_part, aes(x = stim_type, y = mean_rt, group = task)) +
  geom_violinhalf(data = RT_reading_part, mapping = aes(fill = stim_task, group = stim_task), alpha = 1, color = NA, trim = TRUE, flip = FALSE, position = position_nudge(x =  0.15)) +
  geom_point2(position = position_jitter(width = 0.1, seed = 42), size = 1.5, alpha = .35) +
  geom_line(mapping = aes(group = participant), color = "#878787", linewidth = 0.2, alpha = 0.55, position = position_jitter(width = 0.1, seed = 42)) +
  facet_grid(~ task, scales = "free_x", space = "free_x") +
  scale_fill_manual(values = cols_reading) +
  scale_color_manual(values = cols_reading) +
  scale_x_discrete(expand = expansion(mult = c(0.1, 0.35)), labels = c(rep(c("Sham", "Offline", "Offline+Online"), 2))) +
  coord_cartesian(ylim = c(250, 1550)) +
  ylab("Reading Time in ms") +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1))
)

## arrange plots ----
RT_reading_raw <- ggarrange(RT_reading_raw_boxplot,
            RT_reading_raw_violin +
              theme(axis.title.y = element_blank(),
                    axis.text.y = element_blank(),
                    axis.ticks.y = element_blank(),
                    axis.line.y = element_blank()),
            nrow = 1)
            #heights = c(1,1))
            #widths = c(0.7,0.55),

ggsave(RT_reading_raw, file = here::here(paste0("Plots/RT_reading_raw_", today, ".pdf")), width = 130, height = 70, units = "mm")

#3) Plot RT across time from task onset by stim_type ----
RT_reading_part <- reading_df %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_rt = mean(RT))

RT_reading_part$stim_task <- interaction(RT_reading_part$stim_type, RT_reading_part$task, drop = TRUE)
(RT_raw_time <- ggplot(reading_df, aes(x = time_from_onset_task, y = RT, fill = stim_type, color = stim_type)) +
    #geom_boxplot(RT_nback_part, mapping = aes(x = task, y = mean_rt, fill = stim_type)) +
    #geom_point2(size = 1, alpha = 0.05) +
    geom_smooth(method = "loess") +
    #geom_line(aes(x = task, y = mean_rt, group = stim_type), color="black", linetype="dotted", position = position_dodge(width = 0.75))+
    #geom_violinhalf(RT_nback_part, mapping = aes(x = task, y = mean_rt, fill = stim_type)) +
    scale_fill_manual(values = cols_reading) +
    scale_color_manual(values = cols_reading) +
    facet_wrap(~ task, scales = "free_x") +
    #scale_y_continuous(breaks = c(1000, 2000, 3000, 4000, 5000, 6000)) +
    coord_cartesian(ylim = c(300, 1500)) +
    ylab("Reading Time in ms") +
    xlab("Time from Session Onset in s") +
    theme_bw()+
    theme(legend.position = "bottom",
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         axis.line = element_line(),
         axis.text.y = element_text(size = 10),
         #axis.title.x = element_blank(),
         axis.text.x.bottom = element_text(size = 9.5)) 
    #facet_wrap(~ block_name, nrow = 2)
)

ggsave(RT_single_nback_raw, file = here::here(paste0("Plots/RT_single_nback_raw_", today, ".png")), width = 210, height = 100, units = "mm")

#4) Plot RT across surprisal ----
(RT_reading_raw_surprisal <- ggplot(slice_sample(reading_df, prop = 0.1), aes(x = surprisal_2, y = RT)) +
    geom_point2(size = 1, alpha = 0.04) +
    geom_smooth(method = "loess", color = "darkslategrey") +
    facet_wrap(~ task, labeller = labeller(task = as_labeller(c("Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "Dual task")))) +
    scale_y_continuous(limits = c(250, 1290), breaks = c(400, 800, 1200)) +
    #coord_cartesian(ylim = c(250, 1290)) +
    ylab("Reading time in ms") +
    xlab("Lexical surprisal") +
    theme_bw(base_size = 9.5)+
    theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5))
)

ggsave(RT_reading_raw_surprisal, file = here::here(paste0("Plots/RT_reading_raw_surprisal.pdf")), width = 70, height = 60, units = "mm")

# Plot online trials only ----
RT_reading_online <- reading_df_online %>% 
  group_by(stim_type, task) %>%
  summarise(mean_rt = mean(RT),
            SD_rt = sd(RT),
            std.error_rt = std.error(RT))

RT_reading_online_part <- reading_df_online %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_rt = mean(RT))
RT_reading_online_part$stim_task <- interaction(RT_reading_online_part$stim_type, RT_reading_online_part$task)

##1) Boxplot of RTs by Task and Stimulation ----
(RT_reading_raw_online_boxplot <- ggplot(RT_reading_online, aes(x = stim_type, y = mean_rt, group = task)) +
    #geom_bar(aes(), stat = "identity", width = 0.5) +
    #geom_errorbar(aes(ymin = mean_rt - std.error_rt, ymax = mean_rt + std.error_rt), width =0.07, linewidth=0.7) +
    geom_boxplot(RT_reading_online_part, mapping = aes(x = stim_type, y = mean_rt, fill = stim_task, group = stim_task)) +
    geom_point2(shape = 18, size = 2, position = position_dodge(width = 0.75)) +
    geom_line(aes(x = stim_type, y = mean_rt, group = 1), color = "black", linetype = "dotted", position = position_dodge(width = 0.75))+
    scale_fill_manual(values = cols_reading[c(1,3,4,6,7,9)]) +
    scale_color_manual(values = cols_reading[c(1,3,4,6,7,9)]) +
    #scale_y_continuous(limits = c(350, 1200), breaks = c(400, 800, 1200)) +
    scale_x_discrete(labels = c(rep(c("Sham", "Active"), 2))) +
    #coord_cartesian(ylim = c(400, 1600)) +
    facet_grid(~ task) +
    ylab("Reaction time in ms") +
    xlab("Task") +
    theme_bw(base_size = 9.5)+
    theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1)) 
)

#2) Violin plot with individual participant lines
(RT_reading_raw_online_violin <- ggplot(RT_reading_online_part, aes(x = stim_type, y = mean_rt, group = task)) +
  geom_violinhalf(data = RT_reading_online_part, mapping = aes(fill = stim_task, group = stim_task), alpha = 1, color = NA, trim = TRUE, flip = FALSE, position = position_nudge(x =  0.15)) +
  geom_point2(position = position_jitter(width = 0.1, seed = 42), size = 1.5, alpha = .35) +
  geom_line(mapping = aes(group = participant), color = "#878787", linewidth = 0.2, alpha = 0.55, position = position_jitter(width = 0.1, seed = 42)) +
  facet_grid(~ task) +
  scale_fill_manual(values = cols_reading[c(1,3,4,6)]) +
  scale_color_manual(values = cols_nback[c(1,3,4,6)]) +
  scale_x_discrete(expand = expansion(mult = c(0.2, 0.65)), labels = c(rep(c("Sham", "Active"), 2))) +
  #scale_y_continuous(limits = c(350, 1200), breaks = c(400, 800, 1200)) +
  ylab("Reaction time in ms") +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1)) #angle = 45, vjust = 1, hjust = 1
)

## arrange plots ----
RT_reading_online_raw <- ggarrange(RT_reading_raw_online_boxplot,
            RT_reading_raw_online_violin +
              theme(axis.title.y = element_blank(),
                    axis.text.y = element_blank(),
                    axis.ticks.y = element_blank(),
                    axis.line.y = element_blank()),
            nrow = 1)
            #heights = c(1,1))
            #widths = c(0.7,0.55),


ggsave(RT_reading_online_raw, file = here::here(paste0("Plots/RT_reading_raw_online_", today, ".pdf")), width = 120, height = 62, units = "mm")
```

## E-FIELDS
### Correlations with raw data
```{r efields prepare df}
# Read in file with e-fields (95 percentile from 10 mm ROI around stim coordinates) and prepare df
df_efields = read.table(here::here("average_efields_sphere_10mm_percentile_95.txt"), header = T, sep = ",")
df_efields$participant <- gsub("sub-", "", df_efields$participant)

df_efields <- df_efields %>% 
  rename(stim_type = session)
df_efields$stim_type <- as.factor(df_efields$stim_type)
df_efields$stim_type <- dplyr::recode(df_efields$stim_type, 
                               "offline" = "Offline", 
                               "offline_online" = "Offline + Online")

# Prepare df
df_reading <- reading_df %>% 
  filter(stim_type != "Sham") %>% 
  droplevels() %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_RT = mean(RT)) %>% 
  mutate(task = dplyr::recode(task, "Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))

df_reading <- full_join(df_reading, df_efields, relationship = "many-to-many")

# Correlation for offline AG session ----
cor_results_reading_offline <- df_reading %>%
  filter(stim_type == "Offline" & participant != "07") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$mean_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value
    )
  })

# Correlation for offline AG during offline+online session ----
cor_results_reading_offline_online_AG <- df_reading %>%
  filter(stim_type == "Offline + Online" & roi == "AG") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$mean_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
    )
  })

# Correlation for online DLPFC during offline+online session ----
cor_results_reading_offline_online_DLPFC <- df_reading %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$mean_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
    )
  })

# Check separately for trials with and without trigger during offline+online session ----
df_reading <- reading_df %>% 
  filter(stim_type != "Sham") %>% 
  droplevels() %>% 
  group_by(participant, stim_type, task, is_trigger) %>% 
  summarise(mean_RT = mean(RT)) %>% 
  mutate(task = dplyr::recode(task, "Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))

df_reading <- full_join(df_reading, df_efields, relationship = "many-to-many")

# Correlation for online DLPFC during offline+online session ----
cor_results_reading_offline_online_DLPFC_trigger <- df_reading %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC") %>%
  droplevels() %>%
  group_by(task, is_trigger) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$mean_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
    )
  }) %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"))

df_DLPFC_offline_online <- df_reading %>%
  filter(
    stim_type == "Offline + Online",
    roi == "DLPFC",
  ) %>%
  droplevels()

ann_RT <- cor_results_reading_offline_online_DLPFC_trigger %>%
  transmute(
    task,
    is_trigger,
    label = sprintf("r = %.2f\np = %.3f", estimate_RT, p.value_RT),
    # choose a fixed position for annotations (e.g., top-right of each facet)
    x = max(df_DLPFC_offline_online$mean_field, na.rm = TRUE),
    y = case_when(is_trigger == "True" ~ 1350,
                  is_trigger == "False" ~ 1200)
  )

(reading_RT_DLPFC_efield_trigger <- ggplot(
  df_DLPFC_offline_online,
  aes(x = mean_field, y = mean_RT,
      colour = is_trigger, shape = is_trigger)
) +
  geom_point(size = 2) +
  geom_smooth(data = subset(df_DLPFC_offline_online, is_trigger == "True"), method = "lm", se = FALSE, linewidth = 0.5) +
  geom_text(
    data = ann_RT,
    aes(x = x, y = y, label = label, colour = is_trigger),
    hjust = 1, vjust = 1, size = 3, show.legend = FALSE
  ) +
  facet_wrap(~ task) +
  labs(
    x = "Mean E-field (DLPFC)",
    y = "Reading time",
    colour = "Trigger",
    shape  = "Trigger",
    title  = "Reading: Mean E-field vs RT (DLPFC, Offline + Online)"
  ) +
  theme_bw()
)

ggsave(reading_RT_DLPFC_efield_trigger, file = here("Plots/E-field_Correlations/reading_RT_DLPFC_efield_trigger.png"))

# Linear regression for offline + online session ----
df_reading_wide <- df_reading %>% 
  filter(stim_type == "Offline + Online") %>% 
  droplevels() %>%
  pivot_wider(names_from = roi, values_from = mean_field)

for(load in unique(df_reading_wide$task)) {
  dat <- df_reading_wide %>% filter(task == load)
  assign(
    paste0("rt_model_", load),
    lm(mean_RT ~ AG + DLPFC * is_trigger, data = dat)
  )
}

summary(rt_model_Reading)
summary(`rt_model_2-back dual`)
```

### Moderating role of e-fields
```{r}
# AG ----
reading_df_No_sham <- subset(reading_df, stim_type != "Sham")
reading_df_No_sham <- droplevels(reading_df_No_sham)

c <- contr.treatment(2) 
my.coding <- matrix(rep(1/2, 2), ncol = 1) 
my.simple <- c-my.coding
contrasts(reading_df_No_sham$task) <- my.simple
contrasts(reading_df_No_sham$stim_type) <- my.simple

lmm_reading_Efield_AG <- lmerTest::lmer(
  log(RT) ~ task * scale(efield_AG, scale = TRUE) +
    (1 + task | participant),
  data = reading_df_No_sham,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(lmm_reading_Efield_AG)
anova(lmm_reading_Efield_AG)

plot(predict_response(lmm_reading_Efield_AG, c("efield_AG")))

emtrends(lmm_reading_Efield_AG, pairwise ~ task, var = "efield_AG", type = "response")

## Plot ----
pred_reading_efield_AG <- predict_response(lmm_reading_Efield_AG, c("efield_AG", "task"), margin = "marginalmeans")
#pred_reading_efield_AG$stim_task <- interaction(pred_reading_efield_AG$group, pred_reading_efield_AG$facet, drop = TRUE)
pred_reading_efield_AG <- pred_reading_efield_AG %>% 
  as.data.frame() %>% 
  rename(task = group)

participant_points <- collapse_by_group(pred_reading_efield_AG, lmm_reading_Efield_AG, "participant")
#participant_points$stim_task <- interaction(participant_points$stim_type, participant_points$task)

(RT_reading_efield_AG <- ggplot(pred_reading_efield_AG, aes(x = x, y = predicted, color = task, fill = task)) +
  geom_jitter2(participant_points, mapping = aes(x = efield_AG, y = RT, color = task), inherit.aes = FALSE, alpha = 0.35, size = 2.2, position = position_jitter(width = 1)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
  geom_line(linewidth = .7) +
  #facet_wrap(~ task, labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task")), scales = "free_x") +
  ylab("Predicted reading time in ms") +
  xlab("E-field AG in V/m") +
  #scale_y_continuous(limits = c(400, 1290)) +
  scale_x_continuous(breaks = c(50,80,110)) +
  coord_cartesian(ylim = c(230, 1530)) +
  #scale_color_manual(values = cols_reading) +
  #scale_fill_manual(values = cols_reading) +
  scale_color_manual(values = cols_reading[c(2,5)]) +
  scale_fill_manual(values = cols_reading[c(2,5)]) +
  theme_bw(base_size = 8)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 9),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 8))
)
ggsave(RT_reading_efield_AG, file = here(paste0("Plots/RT_reading_efield_AG_", today, ".pdf")), width = 40, height = 45, units = "mm")

# DLPFC ----
reading_df_No_sham_offline_online <- subset(reading_df, stim_type == "Offline + Online")
reading_df_No_sham_offline_online <- droplevels(reading_df_No_sham_offline_online)

c <- contr.treatment(2) 
my.coding <- matrix(rep(1/2, 2), ncol = 1) 
my.simple <- c-my.coding
contrasts(reading_df_No_sham_offline_online$task) <- my.simple
contrasts(reading_df_No_sham_offline_online$is_trigger) <- my.simple

lmm_reading_Efield_DLPFC <- lmerTest::lmer(log(RT) ~ 
    task +
    scale(efield_DLPFC, scale = FALSE) + 
    is_trigger +
    task : scale(efield_DLPFC, scale = FALSE) + 
    task : is_trigger +
    scale(efield_DLPFC, scale = FALSE) : is_trigger +
    task : scale(efield_DLPFC, scale = FALSE) : is_trigger +
    (1 + task | participant),
  data = reading_df_No_sham_offline_online,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa"))

summary(lmm_reading_Efield_DLPFC)
anova(lmm_reading_Efield_DLPFC)

## Plot ----
pred_reading_efield_DLPFC <- predict_response(lmm_reading_Efield_DLPFC, c("efield_DLPFC", "is_trigger"), margin = "marginalmeans")

(RT_reading_efield_DLPFC <- plot(pred_reading_efield_DLPFC, collapse_group = TRUE) +
  ylab("Predicted reading time in ms") +
  xlab("E-field DLPFC in V/m") +
  scale_x_continuous(breaks = extended_breaks(3)) +
  #coord_cartesian(ylim = c(230, 1530)) +
  scale_color_manual(values = cols_dualContrast) +
  scale_fill_manual(values = cols_dualContrast) +
  theme_bw(base_size = 8)+
  theme(legend.position = "bottom",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       plot.title = element_blank(),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8),
       #axis.title.x = element_text(size = 9),
       axis.text.x = element_text(size = 8))
)
ggsave(RT_reading_efield_DLPFC, file = here(paste0("Plots/RT_reading_efield_DLPFC.pdf")), width = 60, height = 45, units = "mm")

tab_model(lmm_reading_Efield_AG,
          lmm_reading_Efield_DLPFC,
  show.intercept = FALSE,
  show.icc = TRUE,   # ICC (Intraclass Correlation) is not always needed
  show.re.var = TRUE,  # Show variance of random effects
  show.df = FALSE,     # Don't display degrees of freedom
  show.obs = FALSE,    # Don't display number of observations
  show.ngroups = FALSE, # Don't display number of groups for random effects
  show.stat = TRUE,    # Show model statistics (e.g., p-values, F-values)
  collapse.ci = TRUE,  # Collapse confidence intervals into one line
  dv.labels = c("E-field AG", "E-field DLPFC"),
  file = here("Model_tables/reading_efields.doc")
)

(plot_RT_reading_efield <- ggarrange(RT_reading_efield_AG,
                                    RT_reading_efield_DLPFC,
                                    nrow = 1,
                                    widths = c(1, 0.8)))
ggsave(plot_RT_reading_efield, file = here(paste0("Plots/plot_RT_reading_efield.pdf")), width = 90, height = 70, units = "mm")
```


## DELTAS
### Classify TMS reaction
```{r}
# Prepare df
reading_df <- subset(reading_df, !is.na(surprisal_2))
reading_df <- subset(reading_df, surprisal_2 < 40)
reading_df <- reading_df %>% 
  mutate(task = dplyr::recode(task, "Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))

df_reading <- reading_df %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_RT = mean(RT))

df_reading_deltas <- df_reading %>% 
  pivot_wider(
    id_cols  = c(participant, task),
    names_from  = stim_type,
    values_from = mean_RT
  ) %>% 
  mutate(
    delta_RT_Offline = Offline - Sham,
    delta_RT_Offline_Online = `Offline + Online` - Sham
  ) %>% 
  select(participant, task, delta_RT_Offline, delta_RT_Offline_Online) %>% 
  pivot_longer(
    cols = starts_with("delta_"),
    names_to = c(".value", "stim_type"),
    names_pattern = "(delta_(?:RT))_(.*)") %>% 
  mutate(stim_type = dplyr::recode(stim_type,
      "Offline"          = "Offline",
      "Offline_Online"   = "Offline + Online"),
    direction_RT = case_when(
        delta_RT < 0 ~ "Faster",
        delta_RT > 0 ~ "Slower",
        is.na(delta_RT) ~ NA,
        TRUE ~ "No change"),
    direction_RT = factor(direction_RT, levels = c("Faster", "No change", "Slower")),
    task = dplyr::recode(task, "Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))

# run LMMs on data
m1 <- lmer(delta_RT ~ task * stim_type + (1+task+stim_type|participant), data = df_reading_deltas)
summary(m1)

# Plots ----
# scatter plot
(reading_change_RT <- ggplot(df_reading_deltas[!is.na(df_reading_deltas$delta_RT),], aes(x = task, y = delta_RT, colour = direction_RT, label = participant, group = participant)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_point(position = position_dodge(width = 0.2), size = 1.3) +
  #geom_line(position = position_dodge(width = 0.2), alpha = 0.5) +
  geom_text_repel(size = 1.5, position = position_dodge(width = 0.2), show.legend = FALSE, max.overlaps = 60) +
  facet_wrap(~ stim_type, nrow = 1) +
  scale_fill_manual(values = cols_reading) +
  scale_color_manual(values = cols_reading) +
  labs(x = "Task", y = "Δ RT (TMS – Sham)", colour = "RT direction", title = "RT changes per participant and task") +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "bottom",
     text = element_text(family = "Helvetica"),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     strip.background = element_blank(),
     strip.text = element_text(size = 10),
     axis.line = element_line(),
     axis.text.y = element_text(size = 8.5),
     axis.title.x = element_blank(),
     axis.text.x = element_text(size = 8.5))
)
ggsave(reading_change_RT, file = here("Plots/reading_delta_RT_scatter.png"), width = 100, height = 80, units = "mm")

# donut plot
df_RT_donut <- df_reading_deltas %>% 
  filter(!is.na(delta_RT)) %>% 
  group_by(task, stim_type, direction_RT) %>% 
  summarise(n = n(), .groups = "drop_last") %>% 
  mutate(
    prop = n / sum(n),
    ymax = cumsum(prop),
    ymin = dplyr::lag(ymax, default = 0),
    label_pos = (ymax + ymin) / 2
  )

(reading_donut_RT <- ggplot(df_RT_donut, aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = direction_RT)) +
  geom_rect() +
  coord_polar(theta = "y") +
  xlim(c(2, 4)) +
  facet_wrap(~ stim_type + task, labeller = labeller(task = as_labeller(c("Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))), nrow = 1) +
  geom_text(aes(y = label_pos,x = 3.5, label = percent(prop, accuracy = 1)), colour = "black", size = 2) +
  scale_fill_manual(values = cols_reading) +
  scale_color_manual(values = cols_reading) +
  theme_void(base_size = 9.5) +
  theme(legend.position = "none",
        aspect.ratio = 1,
        text = element_text(family = "Helvetica"),)
)
ggsave(reading_donut_RT, file = here("Plots/reading_donut_RT.png"), width = 100, height = 80, units = "mm")

reading_delta_RT <- ggarrange(reading_change_RT,
                            reading_donut_RT,
                            nrow = 1,
                            heights = c(0.9, 2.3))

ggsave(reading_delta_RT, file = here("Plots/reading_delta_RT.png"), width = 130, height = 140, units = "mm")
```

### Correlate reaction with e-fields
Do people with a stronger reaction (either faster or slower) also have a stronger e-field?
```{r}
# Read in file with e-fields (95 percentile from 10 mm ROI around stim coordinates) and prepare df
df_efields = read.table(here::here("average_efields_sphere_10mm_percentile_95.txt"), header = T, sep = ",")
df_efields$participant <- gsub("sub-", "", df_efields$participant)

df_efields <- df_efields %>% 
  rename(stim_type = session)
df_efields$stim_type <- as.factor(df_efields$stim_type)
df_efields$stim_type <- dplyr::recode(df_efields$stim_type, 
                               "offline" = "Offline", 
                               "offline_online" = "Offline + Online")

df_reading_deltas_efields <- full_join(df_reading_deltas, df_efields, relationship = "many-to-many")

# Correlation for offline AG session ----
cor_results_reading_offline_delta_direction <- df_reading_deltas_efields %>%
  filter(stim_type == "Offline" & participant != "07") %>% #& direction_dprime != "No change"
  droplevels() %>%
  group_by(task, direction_RT) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
    )
  }) %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"))

# Correlation for offline AG during offline+online session ----
cor_results_reading_offline_online_AG_delta_direction <- df_reading_deltas_efields %>%
  filter(stim_type == "Offline + Online" & roi == "AG" & !is.na(direction_RT)) %>%
  droplevels() %>%
  group_by(task, direction_RT) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
    )
  }) %>%
  ungroup %>% 
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"))

# plot result for RT
df_ag_offline_online <- df_reading_deltas_efields %>%
  filter(
    stim_type == "Offline + Online",
    roi == "AG",
    !is.na(direction_RT)
  ) %>%
  droplevels()

ann_RT <- cor_results_reading_offline_online_AG_delta_direction %>%
  transmute(
    task,
    direction_RT,
    label = sprintf("r = %.2f\np = %.3f", estimate_RT, p.value_RT),
    x = max(df_ag_offline_online$mean_field, na.rm = TRUE),
    y = case_when(
      direction_RT == "Slower" ~ 390,
      direction_RT == "Faster" ~ 300
    ))

(reading_RT_AG_efield_direction <- ggplot(
  df_ag_offline_online,
  aes(x = mean_field, y = delta_RT, colour = direction_RT, shape = direction_RT)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.5) +
  geom_text(
    data = ann_RT,
    aes(x = x, y = y, label = label, colour = direction_RT),
    hjust = 1, vjust = 1, size = 3, show.legend = FALSE
  ) +
  facet_wrap(~ task) +
  labs(
    x = "Mean E-field (AG)",
    y = "Δ RT (TMS – Sham)",
    colour = "RT direction",
    shape  = "RT direction",
    title  = "Mean E-field vs RT delta (AG, Offline + Online)"
  ) +
  theme_bw()
)

ggsave(reading_RT_AG_efield_direction, file = here("Plots/E-field_Correlations/reading_RT_AG_efield_direction.png"))

# Correlation for online DLPFC during offline+online session ----
cor_results_reading_offline_online_DLPFC_delta_direction <- df_reading_deltas_efields %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC" & !is.na(direction_RT)) %>%
  droplevels() %>%
  group_by(task, direction_RT) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
    )
  }) %>% 
  ungroup() %>% 
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"))
```

### Correlations with raw delta values
```{r efields prepare df}
# Read in file with e-fields (95 percentile from 10 mm ROI around stim coordinates) and prepare df
df_efields = read.table(here::here("average_efields_sphere_10mm_percentile_95.txt"), header = T, sep = ",")
df_efields$participant <- gsub("sub-", "", df_efields$participant)

df_efields <- df_efields %>% 
  rename(stim_type = session)
df_efields$stim_type <- as.factor(df_efields$stim_type)
df_efields$stim_type <- dplyr::recode(df_efields$stim_type, 
                               "offline" = "Offline", 
                               "offline_online" = "Offline + Online")

# Prepare df
df_reading <- reading_df %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_RT = mean(RT))

df_reading_deltas <- df_reading %>% 
  pivot_wider(
    id_cols  = c(participant, task),
    names_from  = stim_type,
    values_from = mean_RT
  ) %>% 
  mutate(
    delta_RT_Offline = Offline - Sham,
    delta_RT_Offline_Online = `Offline + Online` - Sham
  ) %>% 
  select(participant, task, delta_RT_Offline, delta_RT_Offline_Online) %>% 
  pivot_longer(
    cols = starts_with("delta_"),
    names_to = c(".value", "stim_type"),
    names_pattern = "(delta_(?:RT))_(.*)") %>% 
  mutate(stim_type = dplyr::recode(stim_type,
      "Offline"          = "Offline",
      "Offline_Online"   = "Offline + Online"),
      task = dplyr::recode(task, "Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))

df_reading_deltas <- full_join(df_reading_deltas, df_efields, relationship = "many-to-many")

# Correlation for offline AG session ----
cor_results_reading_delta_offline <- df_reading_deltas %>%
  filter(stim_type == "Offline" & participant != "07") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
    )
  }) %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"))

# Correlation for offline AG during offline+online session ----
cor_results_reading_delta_offline_online_AG <- df_reading_deltas %>%
  filter(stim_type == "Offline + Online" & roi == "AG") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
    )
  }) %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"))

# Correlation for online DLPFC during offline+online session ----
cor_results_reading_delta_offline_online_DLPFC <- df_reading_deltas %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
    )
  }) %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"))

# Linear regression for offline + online session ----
df_reading_deltas_wide <- df_reading_deltas %>% 
  filter(stim_type == "Offline + Online") %>% 
  droplevels() %>%
  pivot_wider(names_from = roi, values_from = mean_field)

for(load in unique(df_reading_deltas_wide$task)) {
  dat <- df_reading_deltas_wide %>% filter(task == load)
  assign(
    paste0("rt_model_", load),
    lm(delta_RT ~ AG + DLPFC, data = dat)
  )
}

summary(rt_model_Reading)
summary(`rt_model_2-back dual`)

# Check for effect of is_trigger ----
df_reading <- reading_df %>% 
  group_by(participant, stim_type, task, is_trigger) %>% 
  summarise(mean_RT = mean(RT))

df_reading_deltas <- df_reading %>% 
  filter(stim_type != "Offline") %>% 
  pivot_wider(
    id_cols  = c(participant, task, is_trigger),
    names_from  = stim_type,
    values_from = mean_RT
  ) %>% 
  mutate(
    delta_RT_Offline_Online = `Offline + Online` - Sham
  ) %>% 
  select(participant, task, is_trigger, delta_RT_Offline_Online) %>% 
  pivot_longer(
    cols = starts_with("delta_"),
    names_to = c(".value", "stim_type"),
    names_pattern = "(delta_(?:RT))_(.*)") %>% 
  mutate(stim_type = dplyr::recode(stim_type,
      "Offline_Online"   = "Offline + Online"),
       task = dplyr::recode(task, "Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))

df_reading_deltas <- full_join(df_reading_deltas, df_efields, relationship = "many-to-many")

# Correlation for online DLPFC during offline+online session ----
cor_results_reading_offline_online_DLPFC_trigger <- df_reading_deltas %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC" & !is.na(delta_RT)) %>%
  droplevels() %>%
  group_by(task, is_trigger) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
    )
  }) %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"))
```

### Correlate delta in reading time with accuracy
```{r}
reading_df_wide <- reading_df %>%
  group_by(participant, stim_type, task) %>% 
  mutate(mean_RT = mean(RT, rm.na = TRUE), mean_acc = mean(question_acc)) %>% 
  select(participant, task, stim_type, mean_RT, mean_acc) %>% 
  distinct() %>% 
  pivot_wider(
    names_from = stim_type,
    values_from = c(mean_RT, mean_acc)
  )

reading_df_wide <- reading_df_wide %>%
  mutate(
    delta_RT_offline_sham        = mean_RT_Offline - mean_RT_Sham,
    delta_RT_offline_online_sham = `mean_RT_Offline + Online` - mean_RT_Sham,
    delta_acc_offline_sham        = mean_acc_Offline - mean_acc_Sham,
    delta_acc_offline_online_sham = `mean_acc_Offline + Online` - mean_acc_Sham
  ) %>% 
  rename(mean_RT_Offline_Online  = `mean_RT_Offline + Online`,
    mean_acc_Offline_Online = `mean_acc_Offline + Online`)

cor.test(reading_df_wide$delta_RT_offline_sham, reading_df_wide$delta_acc_offline_sham)
cor.test(reading_df_wide$delta_RT_offline_online_sham, reading_df_wide$delta_acc_offline_online_sham)

reading_df_wide %>% ggscatter(x = "delta_RT_offline_online_sham", y = "delta_acc_offline_online_sham", facet.by = "task", add = "reg.line", conf.int = T, cor.coef = T, size = 1, alpha = 1)

reading_df_wide %>% ggscatter(x = "delta_RT_offline_sham", y = "delta_acc_offline_sham", facet.by = "task", add = "reg.line", conf.int = T, cor.coef = T, size = 1, alpha = 1) #label = "participant"

# Explore effect of trigger (only offline+online and sham sessions) ----
reading_df_wide <- reading_df %>%
  filter(stim_type != "Offline") %>% 
  group_by(participant, stim_type, task, is_trigger) %>% 
  mutate(mean_RT = mean(RT, rm.na = TRUE), mean_acc = mean(question_acc)) %>% 
  select(participant, task, stim_type, mean_RT, mean_acc, is_trigger) %>% 
  distinct() %>% 
  pivot_wider(
    names_from = stim_type,
    values_from = c(mean_RT, mean_acc)
  )


reading_df_wide <- reading_df_wide %>%
  mutate(
    delta_RT_offline_online_sham = `mean_RT_Offline + Online` - mean_RT_Sham,
    delta_acc_offline_online_sham = `mean_acc_Offline + Online` - mean_acc_Sham
  ) %>% 
  rename(mean_RT_Offline_Online  = `mean_RT_Offline + Online`,
    mean_acc_Offline_Online = `mean_acc_Offline + Online`) %>% 
  mutate(task = dplyr::recode(task, "Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))

corr_Acc_RT_reading_offline_online <- reading_df_wide %>% ggscatter(x = "delta_RT_offline_online_sham", y = "delta_acc_offline_online_sham", facet.by = c("task", "is_trigger"), add = "reg.line", conf.int = T, cor.coef = T, size = 1, alpha = 1)

ggsave(corr_Acc_RT_reading_offline_online, file = here("Plots/corr_Acc_RT_reading_offline_online.png"), width = 110, height = 100, units = "mm")
```

## EFFECT OF BASELINE PERFORMANCE
How much is reaction to TMS moderated by baseline performance during sham?
```{r}
# RT ----
reading_df <- subset(reading_df, !is.na(surprisal_2))
reading_df <- subset(reading_df, surprisal_2 < 40)
reading_df <- reading_df %>% 
  mutate(task = dplyr::recode(task, "Reading_Baseline_main_click" = "Reading", "2back_dual_main_click" = "2-back dual"))

sham_baseline <- reading_df %>% 
  filter(stim_type == "Sham") %>% 
  group_by(participant, task) %>% 
  summarise(sham_RT = median(log(RT), na.rm = TRUE))

reading_df <- reading_df %>% 
  left_join(sham_baseline) %>%
  filter(stim_type != "Sham") %>% 
  group_by(task) %>% 
  mutate(sham_RT_centered = sham_RT - mean(sham_RT))

lmm_reading_shamBaseline <- lmerTest::lmer(log(RT) ~
          stim_type +
          task +
          scale(sham_RT, scale = FALSE) + 
          stim_type:task +
          stim_type:scale(sham_RT, scale = FALSE) +
          stim_type:task:scale(sham_RT, scale = FALSE) +
          (1 + stim_type + task | participant),
        data = reading_df,
        REML = FALSE,
        control = lmerControl(optimizer = "bobyqa"))

summary(lmm_reading_shamBaseline)
anova(lmm_reading_shamBaseline)

plot(predict_response(lmm_reading_shamBaseline, c("sham_RT", "stim_type", "task"), margin = "marginalmeans"), limit_range = TRUE)

slopes_stimType_task <- emtrends(
  lmm_reading_shamBaseline,
  specs = ~ stim_type | task,
  var = "sham_RT",
  type = "response"
)

summary(slopes_stimType_task)
pairs(slopes_stimType_task, adjust = "holm")

# Plot ----
pred_reading_shamBaseline <- predictions(
  lmm_reading_shamBaseline,
  #newdata = reading_grid_surprisal,
  by = c("sham_RT", "stim_type", "task"),
  type = "response",
  transform = exp,
  re.form = NA
)

# for plotting
pred_reading_shamBaseline$stim_task <- interaction(pred_reading_shamBaseline$stim_type, pred_reading_shamBaseline$task, drop = TRUE)
participant_points <- collapse_by_group(pred_reading_shamBaseline, lmm_reading_shamBaseline, "participant")
participant_points$stim_task <- interaction(participant_points$stim_type, participant_points$task)

(RT_reading_shamBaseline_lmm <- ggplot(subset(pred_reading_shamBaseline, stim_type != "Sham"), aes(x = exp(sham_RT), y = estimate, colour = stim_task, fill = stim_task)) +
  geom_jitter2(subset(participant_points, stim_type != "Sham"), mapping = aes(x = exp(sham_RT), y = RT, color = stim_task), inherit.aes = FALSE, alpha = 0.35, size = 2.2, position = position_jitter(width = 1)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
  geom_line(linewidth = .7) +
  facet_wrap(~ task, labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task")), scales = "free_x") +
  ylab("Predicted reading time in ms") +
  xlab("Baseline reading time in ms") +
  scale_y_continuous(breaks = pretty_breaks(3)) +
  scale_x_continuous(breaks = extended_breaks(n = 3)) +
  coord_cartesian(ylim = c(230, 1530)) +
  scale_color_manual(values = cols_reading[c(2,3,5,6)]) +
  scale_fill_manual(values = cols_reading[c(2,3,5,6)]) +
  theme_bw(base_size = 8)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 9),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 8))
)
ggsave(RT_reading_shamBaseline_lmm, file = here(paste0("Plots/RT_reading_shamBaseline_lmm_", today, ".pdf")), width = 50, height = 85, units = "mm")

# Plot change in ratio/% for low, average, and high performers ----
base_vals <- reading_df %>%
  group_by(task) %>%
  reframe(
    sham_RT = c(
      quantile(sham_RT, .25, na.rm = TRUE),
      mean(sham_RT, na.rm = TRUE),
      quantile(sham_RT, .75, na.rm = TRUE)
    ),
    base_label = c("Fast", "Average", "Slow"),
    .groups = "drop"
  )
newdat <- tidyr::crossing(
  base_vals,
  stim_type = levels(reading_df$stim_type)
)

cmp_all <- comparisons(
  lmm_reading_shamBaseline,
  newdata = newdat,
  variables = list(stim_type = "reference"),
  transform = exp,
  re.form = NA,
  comparison = "difference"
)

cmp_all$stim_task <- interaction(cmp_all$contrast, cmp_all$task)
cmp_all$base_label <- factor(cmp_all$base_label, levels = c("Slow", "Average", "Fast"))

(RT_reading_shamBaseline_comparisons <- ggplot(cmp_all, aes(y = (estimate-1)*100, x = base_label, group = contrast)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey45") +
  geom_line(linewidth = 0.65, aes(colour = stim_task)) +
  geom_point(size = 3, aes(colour = stim_task, fill = stim_task), shape = 23) +
  geom_errorbar(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, colour = stim_task), width = 0.15, linewidth = 1) +
  #scale_x_continuous(breaks = base_vals$sham_RT, labels = base_vals$base_label) +
  #scale_x_reverse() +
  facet_grid(contrast ~ task, scales = "free", labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task"))) +
  scale_color_manual(values = cols_reading[c(2,3,5,6)]) +
  scale_fill_manual(values = cols_reading[c(2,3,5,6)]) +
  ylab("% change in reading time vs Sham") +
  xlab("Baseline performance") +
  theme_bw(base_size = 8)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 9),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 8, angle = 45, hjust = 1, vjust = 1))
)
ggsave(RT_reading_shamBaseline_comparisons, file = here(paste0("Plots/RT_reading_shamBaseline_comparisons_", today, ".pdf")), width = 60, height = 85, units = "mm")
```

## Correlation of different psycholinguistic predictors
```{r}
df_psycholing <- reading_df |> 
  select(trial_nr, text_nr, word_length_single, zipf_frequency, surprisal_2, entropy_2, previous_surprisal_2) |> 
  distinct()
df_psycholing <- lapply(df_psycholing, as.numeric)
df_psycholing <- as.data.frame(df_psycholing)

# Calculate correlation matrix
cor_mat <- cor(df_psycholing[, 3:7])
p_mat <- matrix(NA, ncol = ncol(df_psycholing[, 3:7]), nrow = ncol(df_psycholing[, 3:7]))
colnames(p_mat) <- rownames(p_mat) <- colnames(df_psycholing[, 3:7])

for (i in 1:ncol(df_psycholing[, 3:7])) {
  for (j in 1:ncol(df_psycholing[, 3:7])) {
    p_mat[i, j] <- cor.test(df_psycholing[, 3:7][, i],
                            df_psycholing[, 3:7][, j])$p.value
  }
}

# set diagonales to NA
diag(cor_mat) <- NA
diag(p_mat) <- NA

# Long format
melted_cor <- reshape2::melt(cor_mat, na.rm = T)
melted_p   <- reshape2::melt(p_mat, na.rm = T)

plot_df <- merge(melted_cor, melted_p, by = c("Var1", "Var2"))
colnames(plot_df) <- c("Var1", "Var2", "cor", "p")

# Visualize correlation heatmap
ggplot(plot_df, aes(Var1, Var2, fill = cor)) +
  geom_tile(color = "white") +
  geom_tile(data = subset(plot_df, p < 0.05), fill = NA, color = "black", linewidth = .2) +
  geom_text(aes(label = sprintf("%.2f", cor)), size = 2) +
  scale_fill_gradient2(high = "#3F132F", low = "#447696", mid = "white") +
  theme_minimal(base_size = 9)+
  theme(legend.position = "right",
     text = element_text(family = "Helvetica"),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(),
     axis.text.y = element_text(size = 8),
     axis.title = element_blank(),
     axis.text.x = element_text(size = 8, angle = 45, vjust = 1, hjust = 1))

```

