---
title: "EXNAT_4_TMS_Stats_Nback"
author: "Sandra Martin"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    code-fold: true
editor_options:
  chunk_output_type: console
---

```{r file setup, echo = FALSE}
rm(list = ls()) # clear environment
knitr::opts_chunk$set() # set default options for all code blocks in this document
options(scipen = 999) # don't use scientific notation for very large or small numbers
n.cores <- max(1, parallel::detectCores() %/% 2, na.rm = T) # Use half of the available cores
```

# Load packages
```{r packages, echo = FALSE, message = FALSE, warning = TRUE}
# Create a list with needed libraries
pkgs <- c("here", # for working with relative paths
          "ggeffects",
          "marginaleffects",
          "emmeans",
          "ggplot2", # for plots
          "dplyr", # for replacing multiple values in vector with different values
          "tidyverse", # for aggregating
          "easystats", # includes performance, see, insight, modelbased
          #"lme4", # also for linear mixed emodels, but no p-values in the summary
          "lmerTest", # extension of lme4 - for tab_model() for showing lme4 model results
          "glmmTMB",
          "mgcv",
          "gratia",
          "itsadug",
          "ggside",
          "ggpubr",
          "car", # for basic Anova() function & aGSIFs (= basically weird adjusted VIFs)
          "sjPlot", # for running Anova & showing results in a HTML table in the Viewer
          "ggnewscale",
          "colorspace", # for beautiful and balanced color palettes
          "ggrepel", # for labels
          "scales",
          "egg") # creating patchwork plots

# Load each listed library, check if it's already installed
# and install if necessary
for (pkg in pkgs){
  if(!require(pkg, character.only = TRUE)){
    install.packages(pkg)
    library(pkg, character.only = TRUE)
  }
}

today <- Sys.Date()
today <- format(today, format="%y%m%d")

emm_options(rg.limit = 1000000) # for emm calculations
```

# Load R Data
```{r}
df_all_data_clean <- readRDS(here::here("RData/df_all_data_clean.rds")) # df with all trials and participants incl demographic information
```

# Settings for plots
```{r Theme for plots, echo = FALSE}
# Custom colour palettes for the plots:
palet_task_condition <- c("#D2BFE7",
                      "#977FB2") 
palet_task_condition_lines <- c("#ad8bd3",
                      "#7B5EC6") 

# for distinguishing between cognitive load conditions: 
 cols_reading <- c("#575A7B", # Reading Only
                 "#ED9201", # 1-back
                 "#982126") # 2-back
#cols_reading <- c("#F8A29E", "#9F4D48", "#4B201D", "#D2BFF5", "#9b84b7", "#56476D")
cols_reading <- c("#F8A29E", "#9F4D48", "#4B201D", "#E9B3FB", "#85409D", "#3B0270")
#cols_dual <- c("#D2BFE7", "#9b84b7", "#56476D")

cols_dualContrast <- c("#B29675", "#575A7B")

# creating a function for std.error
std.error <- function(x, na.rm = TRUE){sd(x, na.rm = TRUE)/sqrt(length(x[!is.na(x)]))}
```

# N-BACK ANALYSIS: N-BACK TASK & DUAL TASK
## Df for n-back tasks
```{r df for single n-back}
nback_df <- subset(df_all_data_clean, task != "Reading_Baseline_main_click")
nback_df <- droplevels(nback_df)
```

## Prepare df, contrast coding
```{r prepare data for stats single n-back, echo = FALSE}
# add column with information whether there was a TMS burst in a certain trial or not
nback_df <- nback_df %>% 
  mutate(is_trigger = case_when(
    stim_type != "Offline" & !is.na(trigger_time) ~ "True",
    stim_type != "Offline" & is.na(trigger_time) ~ "False",
    stim_type == "Offline" ~ "False"
  ))

# if the n-back trial was in the dual task (adding level to cognitive load column)
nback_df <- nback_df %>% 
  mutate(cognitive_load = case_when(
    task == "2back_dual_main_click" ~ "dual task",
    TRUE ~ "single task"
  ))

# simple coding ----
# create a simple coding scheme for reaction (2 levels), is_trigger, cognitive_load
c <- contr.treatment(2) 
my.coding <- matrix(rep(1/2, 2), ncol = 1) 
my.simple <- c-my.coding

nback_df$reaction <- as.factor(nback_df$reaction)
contrasts(nback_df$reaction) <- my.simple

nback_df$is_trigger <- as.factor(nback_df$is_trigger)
contrasts(nback_df$is_trigger) <- my.simple

nback_df$cognitive_load <- as.factor(nback_df$cognitive_load)
contrasts(nback_df$cognitive_load) <- my.simple

# simple coding for stimulation type, session, block name, cognitive_load
c <- contr.treatment(3) 
my.coding <- matrix(rep(1/3, 6), ncol = 2) 
my.simple <- c-my.coding

nback_df$stim_type <- factor(nback_df$stim_type, levels = c("Sham", "Offline", "Offline + Online"))
contrasts(nback_df$stim_type) <- my.simple

nback_df$session <- as.factor(nback_df$session)
contrasts(nback_df$session) <- my.simple

nback_df$task <- factor(nback_df$task, levels = c("1back_single_main_click", "2back_single_main_click", "2back_dual_main_click"))
contrasts(nback_df$task) <- my.simple

# simple coding for stimulation order (6 levels)
c <- contr.treatment(6) 
my.coding <- matrix(rep(1/6, 30), ncol = 5) 
my.simple <- c-my.coding
nback_df$Stim_Order <- as.factor(nback_df$Stim_Order)
contrasts(nback_df$Stim_Order) <- my.simple

# create a column for time that sets first trial of each task to 0 and calculates time to next trial so we get a measure of time progress in s across one session
nback_df <- nback_df %>%
  arrange(participant, stim_type, trial_index_session) %>%
  group_by(participant, stim_type, date, task) %>%
  mutate(
    time_from_onset_task = as.numeric(global_onset_time - first(global_onset_time), units = "secs"),
    task_onset = first(time_from_onset_session),
    block_nr_task = cumsum(trial_nr == 1)
  ) %>%
  ungroup()

# change RT for n-back trials
# if participants pressed the target nback button, use the nback_RT as reaction time instead of RT
nback_df$nback_RT <- as.integer(nback_df$nback_RT)
nback_df <- nback_df %>% 
  mutate(new_RT = case_when(
    str_detect(task, "back") & reaction == TRUE ~ nback_RT,
    .default = RT
  ))

# add column whether the previous trial and second to last trials were an n-back target or not and whether the previous response was correct or incorrect
nback_df <- nback_df %>%
  group_by(participant, stim_type, block_nr_exp) %>%
  mutate(
    # Previous trial was target (lag 1)
    prev_target = lag(target, n = 1, default = NA),
    
    # Second-to-last trial was target (lag 2)
    prev2_target = lag(target, n = 2, default = NA),
    
    # Previous trial accuracy (for post-error effects)
    prev_correct = lag(nback_response, n = 1, default = NA),
    
    # RT of previous trial
    previous_duration = lag(RT, n = 1, default = NA)
  ) %>%
  ungroup()

# Create column that codes nback acc as correct/incorrect instead of four levels (avoids collinearity with reaction predictor in model)
nback_df <- nback_df %>% 
  mutate(nback_acc = case_when(
    nback_response == "correct rejection" ~ "correct",
    nback_response == "hit" ~ "correct",
    nback_response == "false alarm" ~ "incorrect",
    nback_response == "miss" ~ "incorrect",
  ))

# simple coding previous reaction, previous target, previous2 target, nback_acc
c <- contr.treatment(2) 
my.coding <- matrix(rep(1/2, 2), ncol = 1) 
my.simple <- c-my.coding

nback_df$previous_reaction[nback_df$previous_reaction == ""] <- NA
nback_df$previous_reaction <- as.factor(nback_df$previous_reaction)
nback_df$previous_reaction <- droplevels(nback_df$previous_reaction)
contrasts(nback_df$previous_reaction) <- my.simple

nback_df$prev_target <- as.factor(nback_df$prev_target)
contrasts(nback_df$prev_target) <- my.simple

nback_df$prev2_target <- as.factor(nback_df$prev2_target)
contrasts(nback_df$prev2_target) <- my.simple

nback_df$nback_acc <- as.factor(nback_df$nback_acc)
contrasts(nback_df$nback_acc) <- my.simple

# Re-calculate d-prime: separate d-prime for trials with online stimulation and not (makes 2 d-prime values per text)
nback_df <- nback_df %>% 
  group_by(participant, stim_type, task, block_nr_exp, is_trigger) %>% 
  mutate(dprime_new = get_dprime(nback_response))

nback_df$Age <- as.numeric(nback_df$Age)

# Add the information how many triggers there were per block 
# Ultimately doesn't perform well in models because there was no online trigger in the offline session leading to overall weird estimates
# CAVE: this is centred within the offline+online & sham session and NOT the offline session since there were no triggers per block in this session
# nback_df <- nback_df %>% 
#   group_by(participant, stim_type, block_names_numbered) %>% 
#   mutate(trigger_per_block = sum(is_trigger == "True")) %>% 
#   ungroup()
# nback_df <- nback_df %>%
#   mutate(
#     grand_mean_nonoffline = mean(trigger_per_block[stim_type != "Offline"], na.rm = TRUE),
#     trigger_per_block_centered = case_when(
#       stim_type == "Offline" ~ 0,
#       TRUE ~ trigger_per_block - grand_mean_nonoffline
#     )
#   ) %>%
#   select(-grand_mean_nonoffline, -trigger_per_block)  # Clean up temporary variable
# nback_df$trigger_per_block_centered <- as.numeric(nback_df$trigger_per_block_centered)

# save single n-back df ----
# saveRDS(nback_df, file = here::here("RData/nback_df.rds"))

# For statistical models, remove first trials w/o previous duration ----
nback_df <- subset(nback_df, !is.na(previous_duration))

# only trials with correct n-back response ----
nback_only_correct_nback_trials <- subset(nback_df, reaction == TRUE & nback_acc == "correct")
nback_only_correct_nback_trials <- subset(nback_only_correct_nback_trials, nback_RT > 150)
nback_only_correct_nback_trials <- nback_only_correct_nback_trials %>% 
  mutate(task = dplyr::recode(task, "1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual"))
```

## Reaction time analysis
```{r}
## LMM ----
lmm_nback_only_correct <- lmerTest::lmer(log(nback_RT) ~
                         stim_type +
                         session +
                         task +
                         is_trigger +
                         scale(time_from_onset_task, scale = FALSE) +
                         RS +
                         executive_sum +
                         education_years +
                         Age +
                         sideEffects_sum +
                         stim_type:task +
                         stim_type:scale(time_from_onset_task, scale = FALSE) +
                         stim_type:task:scale(time_from_onset_task, scale = FALSE) +
                         (1 + stim_type | participant), # slope for task yields singularity
                       data = nback_only_correct_nback_trials,
                       REML = FALSE,
                       control = lmerControl(optimizer = "bobyqa")
)
summary(lmm_nback_only_correct)

anova(lmm_nback_only_correct)

# contrast stim_types by task:
estimate_contrasts(lmm_nback_only_correct, contrast = "stim_type", by = "task", transform = T, estimate = "average", backend = "emmeans")

# calculate subject-specific predictions for the three-way int (or for two-way int remove "task")
nback_pred <- predict_response(lmm_nback_only_correct, c("stim_type", "participant[all]"), type = "random")

# extract subject-specific random slopes for Miniblock by TMS condition
fe <- fixef(lmm_nback_only_correct)
re <- ranef(lmm_nback_only_correct)$participant

subj_slopes <- data.frame(
  Subject = rownames(re),
  # subject-specific slopes at Sham
  slope_Sham = -(fe["stim_type2"] + fe["stim_type3"]) -
              (re[, "stim_type2"] + re[, "stim_type3"]),
  # subject-specific at TMS level 1
  slope_TMS_offline = fe["stim_type2"] + re[, "stim_type2"],
  # subject-specific at TMS level 2
  slope_TMS_offline_online = fe["stim_type3"] + re[, "stim_type3"]
)

# plot slopes
ggplot(subj_slopes, aes(y = factor(Subject, levels = unique(Subject[order(as.numeric(Subject))])))) +
  geom_point(aes(x = slope_Sham, color = "Sham"), size = 2, alpha = .7) +
  geom_point(aes(x = slope_TMS_offline, color = "offline"), size = 2, alpha = .7) +
  geom_point(aes(x = slope_TMS_offline_online, color = "offline_online"), size = 2, alpha = .7) +
  geom_vline(aes(xintercept = -(fe["stim_type2"] + fe["stim_type3"]), color = "Sham"),
             linetype = "dashed", linewidth = 1, show.legend = TRUE) +
  geom_vline(aes(xintercept = fe["stim_type2"], color = "offline"),
             linetype = "dashed", linewidth = 1, show.legend = TRUE) +
  geom_vline(aes(xintercept = fe["stim_type3"], color = "offline_online"),
             linetype = "dashed", linewidth = 1, show.legend = TRUE) +
  scale_color_manual(name = "TMS condition", labels = c("Sham", "Offline", "Offline + Online"), values = c("#d95f02", "#1b9e77", "steelblue")) +
  scale_y_discrete(drop = FALSE) +
  labs(x = "Subject-specific Effect", y = "Subject") +
  theme_classic() +
  theme(axis.text.y = element_text(size = 7),
        legend.position = "bottom")

## GAMM ----
nback_only_correct_nback_trials <- nback_only_correct_nback_trials %>% 
  ungroup() %>% 
  mutate(across(where(is.character), as.factor))

gamm_RT_nback_only_correct <- bam(log(nback_RT) ~
                         # PARAMETRIC TERMS
                         #stim_type +
                         #task +
                         session +
                         is_trigger +
                         RS +
                         executive_sum +
                         education_years +
                         Age +
                         sideEffects_sum +
                         #task:stim_type + # assess with LMM
                         # SMOOTH TERMS
                         s(time_from_onset_task, k = 20) +   
                         #log(previous_duration) + # doesn't really work here because we're excluding trials w/o nback button press
                         s(stim_type, time_from_onset_task, bs = "sz", k = 20) + 
                         s(task, time_from_onset_task, bs = "sz", k = 20) + 
                         s(stim_type, task, time_from_onset_task, bs = "sz", k = 20) + 
                         # RANDOM TERMS
                         s(participant, bs = "re") +
                         s(participant, stim_type, bs = "re") +
                         s(participant, task, bs = "re") +
                         s(time_from_onset_task, participant, bs = "fs"),
              data = nback_only_correct_nback_trials,
              method = "fREML",
              discrete = TRUE,
              control = gam.control(nthreads = n.cores),
)

gam.check(gamm_RT_nback_only_correct)

summary(gamm_RT_nback_only_correct)

tab_model(lmm_nback_only_correct, gamm_RT_nback_only_correct, file = here("nback_models.html"))

compare_performance(lmm_nback_only_correct, gamm_RT_only_correct_nback)

# TEST for PCD: no sham ----
nback_only_nback_trials_NO_Sham <- subset(nback_only_nback_trials, stim_type != "Sham") 
gamm_RT_only_nback_PCD <- bam(log(new_RT) ~
                         stim_type +
                         session +
                         task +
                         nback_acc + # 
                         is_trigger +
                         # task_onset + # better without
                         s(trial_nr, k = 30) + # slope no
                         s(time_from_onset_session, k = 20) + # time from onset session performs slightly better
                         #s(time_from_onset_task, k = 20) +   
                         s(PCD, k = 20) +
                         RS +
                         executive_sum +
                         education_years +
                         Age +
                         sideEffects_sum +
                         #log(previous_duration) +
                         #efield_AG +
                         #efield_DLPFC +  
                         stim_type:task +
                         stim_type:nback_acc +
                         #task:trial_nr+
                         #stim_type:task:trial_nr +
                         #nback_acc:is_trigger + # unnecessary
                         s(time_from_onset_session, by = stim_type, k = 20) + # better model with time_from_onset_session int
                         s(PCD, by = stim_type, k = 20) + # better model with time_from_onset_session int
                         s(participant, bs = "re") +
                         s(participant, by = stim_type, bs = "re") +
                         s(participant, by = task, bs = "re"),
              data = nback_only_nback_trials_NO_Sham,
              method = "fREML",
              discrete = TRUE,
              #nthreads = n.cores,
              control = gam.control(nthreads = n.cores),
)

# ONLINE TRIALS ONLY (Separate analysis for online trials) ----
nback_df_online <- subset(nback_only_correct_nback_trials, is_trigger == "True")
nback_df_online <- droplevels(nback_df_online)

# new contrast coding for stim type since we're loosing one level
c <- contr.treatment(2) 
my.coding <- matrix(rep(1/2, 2), ncol = 1) 
my.simple <- c-my.coding
contrasts(nback_df_online$stim_type) <- my.simple

## LMM ----
lmm_nback_online <- lmerTest::lmer(log(nback_RT) ~
                         stim_type +
                         session +
                         task +
                         scale(time_from_onset_task, scale = FALSE) +
                         RS +
                         executive_sum +
                         education_years +
                         Age +
                         sideEffects_sum +
                         stim_type:task +
                         stim_type:scale(time_from_onset_task, scale = FALSE) +
                         stim_type:task:scale(time_from_onset_task, scale = FALSE) +
                         (1 + stim_type | participant), # slope for task yields singularity
                       data = nback_df_online,
                       REML = FALSE,
                       control = lmerControl(optimizer = "bobyqa")
)
summary(lmm_nback_online)
anova(lmm_nback_online)

## GAMM ----
nback_df_online <- nback_df_online %>% 
  ungroup() %>% 
  mutate(across(where(is.character), as.factor))

gamm_RT_nback_online <- bam(log(nback_RT) ~
                         # PARAMETRIC TERMS
                         #stim_type +
                         #task +
                         session +
                         #nback_acc +
                         RS +
                         executive_sum +
                         education_years +
                         Age +
                         sideEffects_sum +
                         #task:stim_type + # assess with LMM
                         #stim_type:nback_acc + #assess with LMM
                         # SMOOTH TERMS
                         s(time_from_onset_task, k = 20) +   
                         #log(previous_duration) + # doesn't really work here because we're excluding trials w/o nback button press
                         s(stim_type, time_from_onset_task, bs = "sz", k = 20) + 
                         s(task, time_from_onset_task, bs = "sz", k = 20) + 
                         s(stim_type, task, time_from_onset_task, bs = "sz", k = 20) + 
                         # RANDOM TERMS
                         s(participant, bs = "re") +
                         s(participant, stim_type, bs = "re") +
                         s(participant, task, bs = "re") + 
                         s(time_from_onset_task, participant, bs = "fs"),
              data = nback_df_online,
              method = "fREML",
              discrete = TRUE,
              control = gam.control(nthreads = n.cores),
)

k.check(gamm_RT_nback_online, n.rep = 1000)
gam.check(gamm_RT_nback_online)

summary(gamm_RT_nback_online)

# simulate some data to check how well observed data fall into range of predicted data ----
library(mgcViz)
library(data.table)
sim <- simulate.gam(gamm_RT_nback_only_correct, nsim = 1000) 
dq <- lapply(seq_len(ncol(sim)), function(i) {
  d <- copy(as.data.table(nback_only_correct_nback_trials))
  d[, sim := sim[, i]]
  d[, .(
    obs = mean(log(nback_RT)),
    sim = mean(sim)
  ), by = .(stim_type, task, time_from_onset_task)]
})
dl <- rbindlist(dq, idcol = ".id")
df <- dl[, .(obs = mean(obs), min = quantile(sim, probs = 0.025), 
             max = quantile(sim, probs = 0.975)), keyby = .(stim_type, task, time_from_onset_task)]
ggplot(df, aes(x = time_from_onset_task, y = obs)) +
  geom_ribbon(aes(ymin = min, ymax = max),
              alpha = 0.2, fill = "forestgreen") +
  geom_point(color = "forestgreen", size = 1) +
  facet_wrap(~ stim_type + task) +
  theme(panel.grid = element_blank())

### experimental model only considering e-field values instead of factor stim_type ----
# works well (actually outperforms other model despite much larger df but super complex to explain)

# if there's no online TMS trigger, set efield to 0
nback_only_nback_trials <- nback_only_nback_trials %>% 
  mutate(efield_DLPFC = case_when(
    is_trigger == "False" ~ 0,
    TRUE ~ efield_DLPFC
  ))

gamm_RT_only_nback_efields <- bam(log(nback_RT) ~
                         #stim_type +
                         session +
                         task +
                         nback_acc +  
                         is_trigger +
                         #s(trial_nr, k = 30) + # time from onset task is clearly preffered
                         #s(time_from_onset_session, k = 20) + # time from onset task performs slightly better
                         RS +
                         executive_sum +
                         education_years +
                         Age +
                         sideEffects_sum +
                         s(time_from_onset_task, k = 20) +   
                         #s(task_onset, k = 20) + # correlates too strong with task
                         #log(previous_duration) + # doesn't really work here because we're excluding trials w/o nback button press
                         s(efield_AG) +
                         s(efield_DLPFC) +  
                         s(efield_AG, by = task) +
                         s(efield_AG, by = nback_acc) +
                         s(efield_DLPFC, by = task) +
                         s(efield_DLPFC, by = nback_acc) +
                         s(efield_DLPFC, by = is_trigger) +
                         ti(time_from_onset_task, efield_AG, k = 20) + # better model with time_from_onset_session int
                         ti(time_from_onset_task, efield_DLPFC, k = 20) +
                         s(participant, bs = "re") +
                         s(time_from_onset_task, participant, bs = "fs") +
                         #s(efield_AG, participant, bs = "re") +
                         #s(efield_DLPFC, participant, bs = "re") +
                         s(task, participant, bs = "re"),
              data = nback_only_nback_trials,
              method = "fREML",
              discrete = TRUE,
              control = gam.control(nthreads = n.cores),
)


```

### Plots reaction time models
```{r}
nback_only_correct_nback_trials$stim_task <- interaction(nback_only_correct_nback_trials$stim_type, nback_only_correct_nback_trials$task)

#1) stim type x task x time ----
##1a) Three-way interaction from GAM ----
# first build a grid for plotting and comparisons
sm_names <- smooths(gamm_RT_nback_only_correct)
rand_terms <- sm_names[grepl("participant", sm_names)]
mf <- model.frame(gamm_RT_nback_only_correct)

tasks     <- unique(mf$task)
stimtypes <- unique(mf$stim_type)

reaction_grid_time <- do.call(
  rbind,
  lapply(tasks, function(tt) {
    lapply(stimtypes, function(ss) {
      mf_sub <- subset(mf, task == tt & stim_type == ss)

      datagrid(
        model = gamm_RT_nback_only_correct,
        time_from_onset_task = seq(
          min(mf_sub$time_from_onset_task, na.rm = TRUE),
          max(mf_sub$time_from_onset_task, na.rm = TRUE),
          length.out = 100
        ),
        task       = tt,
        stim_type  = ss,
        session    = levels(mf$session),
        is_trigger  = levels(mf$is_trigger)
      )
    })
  }) |> unlist(recursive = FALSE)
)

pred_nback_time <- predictions(
  gamm_RT_nback_only_correct,
  newdata = reaction_grid_time,
  by = c("time_from_onset_task", "stim_type", "task"),
  type = "link",
  transform = exp,
  exclude = rand_terms
)
pred_nback_time$stim_task <- interaction(pred_nback_time$stim_type, pred_nback_time$task)

df_labels <- pred_nback_time %>% 
  group_by(task, stim_type) %>%
  slice_max(
    order_by = time_from_onset_task,
    n = 1,
    with_ties = FALSE
  ) %>%
  ungroup()

# plot smooths for all stim types
(RT_nback_stimtype_task_time <- ggplot(pred_nback_time, aes(x = time_from_onset_task, y = estimate, colour = stim_task, fill = stim_task)) +
    geom_jitter2(data = slice_sample(nback_only_correct_nback_trials, prop = .2), mapping = aes(x = time_from_onset_task, y = nback_RT), alpha = 0.15) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
    geom_line(linewidth = 1.1) +
    geom_text_repel(data = df_labels, aes(x = time_from_onset_task, y = estimate, label = stim_type, colour = stim_task), inherit.aes = FALSE, direction = "y", hjust = 0, nudge_x = 0.25, nudge_y = 5, box.padding = 0.35,  point.padding = 0.1, size = 2.5,  show.legend = FALSE,  max.overlaps = Inf, fontface = "bold") +
    facet_wrap(~ task, labeller = labeller(task = c("1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual task")), scales = "free_x") +
    ylab("Reaction time in ms") +
    xlab("Time since task onset in s") +
    scale_y_continuous(limits = c(450, 800)) +
    scale_x_continuous(expand = expansion(mult = c(0.02, 0.15))) +
    #coord_cartesian(ylim = c(400, 1600)) +
    scale_color_manual(values = cols_nback) +
    scale_fill_manual(values = cols_nback) +
    theme_bw(base_size = 9.5)+
    theme(legend.position = "none",
          text = element_text(family = "Helvetica"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.background = element_blank(),
          strip.text = element_text(size = 10),
          axis.line = element_line(),
          axis.text.y = element_text(size = 8.5),
          #axis.title.x = element_blank(),
          axis.text.x.bottom = element_text(size = 8.5))
)

# Three-way interaction from LMM ----
pred_nback_time_lmm <- predictions(
  lmm_nback_only_correct,
  newdata = reaction_grid_time,
  by = c("time_from_onset_task", "stim_type", "task"),
  type = "response",
  transform = exp,
  re.form = NA
)

pred_nback_time_lmm$stim_task <- interaction(pred_nback_time_lmm$stim_type, pred_nback_time_lmm$task)

# plot smooths for all stim types
(RT_nback_stimtype_task_time_lmm <- ggplot(pred_nback_time_lmm, aes(x = time_from_onset_task, y = estimate, colour = stim_task, fill = stim_task)) +
    geom_jitter2(data = slice_sample(nback_only_correct_nback_trials, prop = .2), mapping = aes(x = time_from_onset_task, y = nback_RT), alpha = 0.15) +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
    geom_line(linewidth = 1.1) +
    facet_wrap(~ task, labeller = labeller(task = c("1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual task")), scales = "free_x") +
    ylab("Reaction time in ms") +
    xlab("Time since task onset in s") +
    scale_y_continuous(limits = c(450, 800)) +
    #coord_cartesian(ylim = c(400, 1600)) +
    scale_color_manual(values = cols_nback) +
    scale_fill_manual(values = cols_nback) +
    theme_bw(base_size = 9.5)+
    theme(legend.position = "none",
          text = element_text(family = "Helvetica"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.background = element_blank(),
          strip.text = element_text(size = 10),
          axis.line = element_line(),
          axis.text.y = element_text(size = 8.5),
          #axis.title.x = element_blank(),
          axis.text.x.bottom = element_text(size = 8.5))
)

##1b) Comparison of different smooths ----
# calculate difference smooths
cmp_nback_time <- comparisons(
  gamm_RT_nback_only_correct,
  newdata = reaction_grid_time,
  variables = list(stim_type = "pairwise"),
  type = "link",
  transform = exp,
  exclude = rand_terms,
  comparison = "difference",
  #hypothesis = difference ~ reference
)

cmp_df_nback_time <- as.data.frame(cmp_nback_time)
cmp_df_nback_time$comp_task <- interaction(cmp_df_nback_time$contrast, cmp_df_nback_time$task)
cmp_df_nback_time$percent_change_rt <- (cmp_df_nback_time$estimate - 1)*100
cmp_df_nback_time <- cmp_df_nback_time %>% 
  mutate(significance = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"),
         significance_ribbon = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"),
         significance_line = case_when(p.value < 0.05 ~ "significant",
                                  TRUE ~ "not significant"))

cmp_df_nback_time <- cmp_df_nback_time %>% 
  arrange(contrast, comp_task, time_from_onset_task) %>% 
  group_by(contrast, comp_task) %>% 
  mutate(seg_id = cumsum(significance != dplyr::lag(significance, default = first(significance)))) %>% 
  ungroup()

# for adding vertical lines/geom_rect
sig_ranges <- cmp_df_nback_time |>
  filter(significance == "significant") |>
  group_by(task, comp_task) |>
  summarise(
    x_start = min(time_from_onset_task),
    x_end   = max(time_from_onset_task),
    .groups = "drop")

df_labels <- cmp_df_nback_time %>% 
  filter(contrast != "Offline + Online - Offline") %>% 
  group_by(task, comp_task) %>%
  slice_max(
    order_by = time_from_onset_task,
    n = 1,
    with_ties = FALSE
  ) %>%
  ungroup()


(RT_comp_nback_stimtype_task_time <- ggplot(subset(cmp_df_nback_time, contrast != "Offline + Online - Offline"), aes(x = time_from_onset_task, y = percent_change_rt, colour = comp_task, fill = comp_task, group = interaction(comp_task, seg_id))) +
  #geom_rect(data = sig_ranges, aes(xmin = x_start, xmax = x_end, ymin = -Inf, ymax = Inf), inherit.aes = FALSE, fill  = "grey80", alpha = 0.25) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line)) + #aes(linetype = significance)
  geom_text_repel(data = df_labels, aes(x = time_from_onset_task, y = percent_change_rt, label = contrast, colour = comp_task), inherit.aes = FALSE, direction = "y", hjust = 0, nudge_x = 0.25, box.padding = 0.35,  point.padding = 0.1, size = 2.5,  show.legend = FALSE,  max.overlaps = Inf, fontface = "bold") +
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_start), linetype = 2, colour = "black") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_end), linetype = 2, colour = "black") +
  facet_wrap(~ task, labeller = labeller(task = c("1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual task")), scales = "free_x") +
  ylab("% change in reaction time") +
  xlab("Time since task onset in s") +
  #scale_y_continuous(limits = c(0, 1.6)) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_x_continuous(expand = expansion(mult = c(0.02, 0.15))) +
  scale_color_manual(values = cols_nback[c(2,3,5,6,8,9)]) +
  scale_fill_manual(values = cols_nback[c(2,3,5,6,8,9)]) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5)) # angle = 45, vjust = 1, hjust = 1
)

# also plot online+offline vs offline 
(RT_comp_nback_stimtype_task_time_active <- ggplot(subset(cmp_df_nback_time, contrast == "Offline + Online - Offline"), aes(x = time_from_onset_task, y = percent_change_rt, colour = comp_task, fill = comp_task, group = interaction(comp_task, seg_id))) +
  #geom_rect(data = sig_ranges, aes(xmin = x_start, xmax = x_end, ymin = -Inf, ymax = Inf), inherit.aes = FALSE, fill  = "grey80", alpha = 0.25) +
  geom_hline(yintercept = 0, linetype = 2) +
  geom_ribbon(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, alpha = significance_ribbon), colour = NA) +
  scale_alpha_manual(values = c("not significant" = 0.1, "significant" = 0.3), name = "ribbon") +
  new_scale("alpha") +
  geom_line(linewidth = 1.5, aes(alpha = significance_line)) + #aes(linetype = significance)
  scale_alpha_manual(values = c("not significant" = 0.3, "significant" = 1), name = "line") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_start), linetype = 2, colour = "black") +
  #geom_vline(data = sig_ranges, aes(xintercept = x_end), linetype = 2, colour = "black") +
  facet_wrap(~ task, labeller = labeller(task = c("1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual task")), scales = "free_x") +
  ylab("% change in RT") +
  xlab("Time since task onset in s") +
  #scale_y_continuous(limits = c(0, 1.6)) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_color_manual(values = cols_nback[c(3,6,9)]) +
  scale_fill_manual(values = cols_nback[c(3,6,9)]) +
  #scale_linetype_manual(values = c(1,3)) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       #axis.title.x = element_blank(),
       axis.text.x.bottom = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1))
)

##1c) Forest plot: stim type x task x time ----
cmp_nback_time_selected <- comparisons(
  gamm_RT_nback_only_correct,
  newdata = datagrid(
    time_from_onset_task = c(100, 300, 500),
    stim_type = unique(mf$stim_type),
    task = unique(mf$task)
  ),
  variables = list(stim_type = "pairwise"),
  type = "link",
  transform = exp,
  exclude = rand_terms,
  comparison = "difference"
)

cmp_nback_time_selected <- cmp_nback_time_selected %>% 
  filter(contrast != "Offline + Online - Offline") %>% 
  filter(stim_type != "Sham") %>% 
  mutate(significance = case_when(p.value < 0.05 ~ "*", .default = ""),
         y_pos = time_from_onset_task + case_when(
           contrast == "Offline - Sham"        ~  20,
           contrast == "Offline + Online - Sham" ~ -20,
           TRUE ~ 0),
         percent_change = (estimate-1)*100,
         CI_low_percent = (conf.low-1)*100,
         CI_high_percent = (conf.high-1)*100)

(RT_comp_nback_stimtype_time_forest <- ggplot(cmp_nback_time_selected, aes(x = percent_change, y = y_pos, color = interaction(contrast, task), group = contrast)) +
  geom_vline(xintercept = 0, color = "#3b4856", linetype = "dashed", linewidth = 0.8, alpha = 0.7) +
  geom_errorbar(aes(xmin = CI_low_percent, xmax = CI_high_percent), linewidth = .5, orientation = "y", width = 1) +
  geom_point(shape = 18, size = 4.5) +
  geom_text(aes(x = conf.high, label = significance), color = "#3b4856", nudge_x = 0.01, hjust = -0.1, vjust = 0.7, size = 5, show.legend = FALSE) +
  facet_wrap(~ task, labeller = labeller(task = c("1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual task")), scales = "free_x") +
  scale_color_manual(values = cols_nback[c(2,3,5,6,8,9)], labels = c("Offline", "Offline + Online"), name = "Condition") +
  scale_y_continuous(name = "Time since task onset in s", breaks = unique(cmp_nback_time_selected$time_from_onset_task), labels = unique(cmp_nback_time_selected$time_from_onset_task)) +
  scale_x_continuous(name = "% change in RT relative to Sham TMS", limits = c(-40, 30), breaks = c(-40, -20, 0, 20, 30)) +
  theme_bw(base_size = 9.5) +
  theme(panel.background  = element_blank(),
    panel.grid.major  = element_blank(),
    panel.grid.minor  = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(size = 10),
    text = element_text(family = "Helvetica"),
    axis.line = element_line(),
    axis.text = element_text(size = 8.5),
    #axis.title.x = element_text(size = 10),
    legend.position = "none")
)
ggsave(paste0(folder, "fig_gam_diff_emm_", today, ".png"), fig_gamm_diff_emm, width = 100, height = 155, units = "mm")

##1d) GAMM vs LMM ----
pred_nback_time_gamm <- pred_nback_time
pred_nback_time_lmm <- predictions(
  lmm_nback_only_correct,
  newdata = reaction_grid_time,
  by = c("time_from_onset_task", "stim_type", "task"),
  type = "response",
  transform = exp,
  re.form = NA
)

pred_nback_time_gamm$stim_task <- interaction(pred_nback_time_gamm$stim_type, pred_nback_time_gamm$task, drop = TRUE)
pred_nback_time_gamm$model <- "GAMM"
pred_nback_time_lmm$stim_task <- interaction(pred_nback_time_lmm$stim_type, pred_nback_time_lmm$task, drop = TRUE)
pred_nback_time_lmm$model <- "LMM"

data_fig_models <- rbind(pred_nback_time_gamm, pred_nback_time_lmm)

(RT_nback_stimtype_task_time_LMM_GAMM <- ggplot(data_fig_models, aes(x = time_from_onset_task, y = estimate, colour = stim_task, fill = stim_task)) +
  geom_jitter2(data = nback_only_correct_nback_trials, mapping = aes(x = time_from_onset_task, y = nback_RT), alpha = 0.1) +
  #geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
  geom_line(aes(linetype = model), linewidth = 1, color = "black") +
  facet_wrap(~ task + stim_type) +
  ylab("Reaction time in ms") +
  xlab("Time since task onset in s") +
  scale_y_continuous(limits = c(340, 800)) +
  #coord_cartesian(ylim = c(400, 1600)) +
  scale_color_manual(values = cols_nback) +
  #scale_fill_manual(values = cols_reading) +
  theme_bw(base_size = 10)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       #strip.text = element_blank(),
       axis.line = element_line(),
       axis.text.y = element_text(size = 9),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 9))
)

#2) Parametric effects LMM ----
pred_lmm <- predictions(
  lmm_nback_only_correct,
  by = c("stim_type", "task"),
  type = "response",
  transform = exp,
  re.form = NA
)
pred_lmm$stim_task <- interaction(pred_lmm$stim_type, pred_lmm$task, drop = TRUE)

stim_task_labels <- c(
  "Sham.1-back" = "Sham",
  "Offline.1-back" = "Offline",
  "Offline + Online.1-back" = "Offline+Online",
  "Sham.2-back" = "Sham",
  "Offline.2-back" = "Offline",
  "Offline + Online.2-back" = "Offline+Online",
  "Sham.2-back dual" = "Sham",
  "Offline.2-back dual" = "Offline",
  "Offline + Online.2-back dual" = "Offline+Online"
)

(LMM_RT_nback_stim_type_task <- ggplot(pred_lmm, aes(x = stim_task, y = estimate, color = stim_task, group = stim_task, fill = stim_task)) +
  #geom_jitter(data = slice_sample(nback_only_correct_nback_trials, prop = 1), mapping = aes(x = task, y = nback_RT, color = stim_task), alpha = 0.02, position = position_jitterdodge(dodge.width = 1, jitter.width = 0.5)) +
  geom_point(position = position_dodge(width = 1), size = 3, shape = 23) +
  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high), width = 0.15, position = position_dodge(width = 1), linewidth = 1) +
  ylab("Reaction time in ms") +
  xlab("Task") +
  scale_y_continuous(breaks = breaks_extended(n = 3)) +
  scale_x_discrete(labels = stim_task_labels) +
  coord_cartesian(ylim = c(500, 750)) +
  scale_color_manual(values = cols_nback) +
  scale_fill_manual(values = cols_nback) +
  theme_bw(base_size = 9.5)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       #strip.text = element_blank(),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, hjust = 1, vjust = 1))
)
ggsave(LMM_RT_nback_stim_type_task, file = here(paste0("Plots/LMM_RT_nback_stim_type_task_", today, ".pdf")), width = 50, height = 65, units = "mm")

#3) Arrange plots ----
##3a) Time plots ----
(figure_RT_nback_time <- ggarrange(RT_nback_stimtype_task_time,
                                   RT_comp_nback_stimtype_task_time,
                                   nrow = 1))
ggsave(figure_RT_nback_time, file = here(paste0("Plots/figure_RT_nback_time_", today, ".pdf")), width = 180, height = 60, units = "mm")

##3b) Main plots ----
(figure_RT_nback <- ggarrange(LMM_RT_nback_stim_type_task,
                                RT_nback_stimtype_task_time +
                                  theme(axis.title.y = element_blank(),
                                  axis.text.y = element_blank(),
                                  axis.ticks.y = element_blank(),
                                  axis.line.y = element_blank()),
                                nrow = 1, 
                                widths = c(0.45,1))
  
)
ggsave(figure_RT_nback, file = here(paste0("Plots/figure_RT_nback_", today, ".pdf")), width = 180, height = 65, units = "mm")

##4b) Difference smooths time ----
(figure_RT_nback_time <- ggarrange(RT_comp_nback_stimtype_task_time,
                                RT_comp_nback_stimtype_time_forest,
                                nrow = 1, 
                                widths = c(1,1))
  
)
ggsave(figure_RT_nback_time, file = here(paste0("Plots/figure_RT_nback_time_", today, ".pdf")), width = 180, height = 65, units = "mm")


# old stuff but maybe useful ----
pred_gamm_reading_RT_stimType_task_surprisal <- estimate_slopes(gamm_reading, by = c("stim_type", "task"), trend = "surprisal_2", transform = TRUE, backend = "marginalmeans", include_random = TRUE)

plot(pred_gamm_reading_RT_stimType_task_surprisal)

#pred_gamm_nback_RT_stimType_task2 <- avg_predictions(gamm_RT_only_nback, variables = c("task", "stim_type"), type = "response", transform = exp)
#plot_predictions(gamm_RT_only_nback, condition = c("stim_type", "task"), type = "response", transform = exp)

# plot the predicted values
(plot_gamm_nback_RT_stimType_task <- ggplot(pred_gamm_reading_RT_stimType_task_surprisal, aes(x = stim_type, y = Slope, color = task, fill = task)) +
   geom_point2(size = 3, position = position_dodge(width = 0.5)) +
   geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.2, position = position_dodge(width = 0.5)) +
   geom_line(aes(group = task), position = position_dodge(width = 0.5), alpha = 0.75, linetype = "dashed") +
   #geom_violinhalf(data = nback_only_nback_trials, aes(x = task, y = RT), position = position_dodge(width = 0.4), trim = T) +
   ylab("N-back reaction time in ms") +
   xlab("Stimulation condition") +
   #coord_cartesian(ylim=c(800, 1100)) +
   scale_color_manual(values = cols_nback) +  
   scale_fill_manual(values = cols_nback) +  
   theme_bw() +
   theme(legend.position = "bottom",
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         strip.background = element_blank(),
         axis.line = element_line(),
         #axis.title.y = element_text(size = 8),
         axis.text.y = element_text(size = 10),
         axis.text.x = element_text(size = 10))
         #axis.title = element_blank())
)

ggsave(plot_gamm_nback_RT_stimType_task, file = here::here("Plots/plot_gamm_nback_RT_stimType_task.rds"))

estimate_contrasts(gamm_reading, contrast = c("stim_type"), by = c("task"), transform = TRUE, p_adjust = "fdr", comparison = "reference", integer_as_continuous = TRUE, backend = "marginalmeans")

### Compare time slopes ----
slopes_gamm_nback_RT_stimType_time <- estimate_slopes(gamm_RT_only_nback, 
                                                      by = c("stim_type"), 
                                                      trend = "time_from_onset_session", 
                                                      transform = TRUE, # with transform = TRUE we get ratio, otherwise we get log ms
                                                      hypothesis = difference ~ reference, # gives us the difference in slope
                                                      multcomp = "holm") 
# interpretation: 
# ratio of 0.9999152 means: for one s RT is 0.0000848% lower relative to sham, multiply this e.g. by 1000 s to get a better picture: 0.0848 --> after 1000s about 8.5% lower than sham

# alternative that works equally well:
#estimate_contrasts(gamm_RT_only_nback, contrast = c("time_from_onset_session"), by = c("stim_type"), p_adjust = "fdr", comparison = "pairwise", integer_as_continuous = TRUE, backend = "emmeans", predict = "response", transform = T)

slopes_gamm_nback_RT_stimType_time
plot(slopes_gamm_nback_RT_stimType_time)

```

## D-prime analysis
```{r}
nback_df_dprime <- nback_df %>% 
  ungroup() %>% 
  select(participant, stim_type, task, session, cognitive_load, dprime, sideEffects_sum, block_nr_exp, RS, executive_sum, education_years, Age, task_onset) %>% 
  distinct()

# LMM ----
lmm_nback_dprime <- lmerTest::lmer(dprime ~
    stim_type +
    task +
    session +
    scale(block_nr_exp, scale = FALSE) +
    scale(education_years, scale = FALSE) +
    scale(Age, scale = FALSE) +
    scale(executive_sum, scale = FALSE) +
    scale(RS, scale = FALSE) +
    scale(sideEffects_sum, scale = FALSE) +
    stim_type:task +
    (1 + stim_type + task | participant),
  data = nback_df_dprime, 
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

check_model(lmm_nback_dprime)
summary(lmm_nback_dprime)
anova(lmm_nback_dprime)

plot(predict_response(lmm_nback_dprime, "stim_type", margin = "marginalmeans"))
#plot(predict_response(lmm_nback_dprime, "is_trigger", margin = "marginalmeans"))
plot(predict_response(lmm_nback_dprime, c("stim_type", "task"), margin = "marginalmeans"))

###1) Plot stim type ----
pred_lmm_nback_dprime_stimType <- estimate_means(lmm_nback_dprime, by = c("stim_type"), estimate = "average", transform = TRUE, backend = "marginalmeans", include_random = FALSE)

# plot the predicted values
(plot_lmm_nback_dprime_stimType <- ggplot(pred_lmm_nback_dprime_stimType, aes(x = stim_type, y = Mean)) +
   geom_jitter2(data = nback_df_dprime, aes(x = stim_type, y = dprime), alpha = 0.05, width = 0.2, color = "#3b4856") +
   geom_point2(size = 3) +
   geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1)+
   geom_line(aes(group = 1), position = position_dodge(width = 0.5), alpha = 0.75, linetype = "dashed") +
   ylab("N-back d-prime") +
   xlab("Stimulation condition") +
   #coord_cartesian(ylim=c(900, 1150)) +
   scale_color_manual(values = cols_nback) +  
   scale_fill_manual(values = cols_nback) +  
   theme_bw(base_size = 9.5) +
   theme(legend.position = "none",
         text = element_text(family = "Helvetica"),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         strip.background = element_blank(),
         axis.line = element_line(),
         #axis.title.y = element_text(size = 8),
         axis.text.y = element_text(size = 8.5),
         axis.title.x = element_blank(),
         axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1))
         #axis.title = element_blank())
)

ggsave(plot_lmm_nback_dprime_stimType, file = here::here("Plots/plot_lmm_nback_dprime_stimType.pdf"), width = 47, height = 58, units = "mm")

###2) Plot stim type x task ----
pred_gamm_nback_dprime_stimType_task <- estimate_means(lmm_nback_dprime, by = c("stim_type", "task"), estimate = "average", transform = TRUE, backend = "marginalmeans", include_random = FALSE)

# plot the predicted values
(plot_gamm_nback_dprime_stimType_task <- ggplot(pred_gamm_nback_dprime_stimType_task, aes(x = stim_type, y = Mean, colour = task, fill = task)) +
   geom_jitter2(data = nback_df_dprime, aes(x = stim_type, y = dprime, colour = task, fill = task), alpha = 0.2, width = 0.2) +
   geom_point2(size = 3, position = position_dodge(width = 0.25)) +
   geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1, position = position_dodge(width = 0.25))+
   geom_line(aes(group = task), position = position_dodge(width = 0.25), alpha = 0.75, linetype = "dashed") +
   ylab("N-back d-prime") +
   xlab("Stimulation condition") +
   #coord_cartesian(ylim=c(900, 1150)) +
   scale_color_manual(values = cols_nback) +  
   scale_fill_manual(values = cols_nback) +  
   theme_bw() +
   theme(legend.position = "bottom",
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         strip.background = element_blank(),
         axis.line = element_line(),
         #axis.title.y = element_text(size = 8),
         axis.text.y = element_text(size = 10),
         axis.text.x = element_text(size = 10))
         #axis.title = element_blank())
)

ggsave(plot_gamm_nback_dprime_stimType, file = here::here("Plots/plot_gamm_nback_dprime_stimType.png"))

# Only with online trials ----
nback_df_dprime_online <- subset(nback_df_dprime, stim_type != "Offline")
#nback_df_dprime_online <- subset(nback_df_dprime_online, is_trigger != "False")
nback_df_dprime_online <- droplevels(nback_df_dprime_online)



## GAMM ----
nback_df_dprime_online <- nback_df_dprime_online %>% 
  ungroup() %>% 
  mutate(across(where(is.character), as.factor))

gamm_dprime_nback_online <- bam(dprime ~
                         stim_type +
                         session +
                         task +
                         s(block_nr_exp, k = 20) + 
                         RS +
                         executive_sum +
                         education_years +
                         Age +
                         sideEffects_sum +
                         stim_type:task +
                         s(participant, bs = "re") +
                         s(participant, by = stim_type, bs = "re") +
                         s(participant, by = task, bs = "re"),
              data = nback_df_dprime_online,
              method = "fREML",
              discrete = TRUE,
              control = gam.control(nthreads = n.cores),
)

k.check(gamm_dprime_nback_online, n.rep = 1000)
gam.check(gamm_dprime_nback_online)

summary(gamm_dprime_nback_online)

###1) Plot stim type x task ----
pred_gamm_nback_dprime_online_stimType_task <- estimate_means(gamm_dprime_nback_online, by = c("task", "stim_type"), estimate = "average", transform = TRUE, backend = "marginalmeans", include_random = TRUE)

#plot(pred_gamm_nback_dprime_stimType)

# plot the predicted values
(plot_gamm_nback_dprime_online_stimType_task <- ggplot(pred_gamm_nback_dprime_online_stimType_task, aes(x = stim_type, y = Mean, color = task, fill = task)) +
   geom_jitter2(data = nback_df_dprime_online, aes(x = stim_type, y = dprime, colour = task, fill = task), alpha = 0.1, width = 0.2) +
   geom_point2(size = 3) +
   geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1)+
   geom_line(aes(group = task), alpha = 0.75, linetype = "dashed") +
   ylab("N-back d-prime") +
   xlab("Stimulation condition") +
   #coord_cartesian(ylim=c(900, 1150)) +
   scale_color_manual(values = cols_nback) +  
   scale_fill_manual(values = cols_nback) +  
   theme_bw() +
   theme(legend.position = "bottom",
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         strip.background = element_blank(),
         axis.line = element_line(),
         #axis.title.y = element_text(size = 8),
         axis.text.y = element_text(size = 10),
         axis.text.x = element_text(size = 10))
         #axis.title = element_blank())
)

ggsave(plot_gamm_nback_dprime_stimType, file = here::here("Plots/plot_gamm_nback_dprime_stimType.rds"))

plot(predict_response(gamm_RT_nback_dprime, c("participant", "stim_type"), type = "random"))


## LMM ----
lmm_nback_dprime_online <- lmerTest::lmer(dprime ~
    stim_type +
    task +
    session +
    is_trigger +
    scale(block_nr_exp, scale = FALSE) +
    scale(education_years, scale = FALSE) +
    scale(Age, scale = FALSE) +
    scale(executive_sum, scale = FALSE) +
    scale(RS, scale = FALSE) +
    scale(sideEffects_sum, scale = FALSE) +
    stim_type:task +
    stim_type:is_trigger + 
    (1 + task | participant),
  data = nback_df_dprime_online, 
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(lmm_nback_dprime_online)
anova(lmm_nback_dprime_online)
plot(predict_response(lmm_single_nback_dprime_online, c("stim_type", "cognitive_load"), margin = "marginalmeans"))

# only d-prime for trials with trigger
nback_df_dprime_online <- nback_df_dprime %>% 
  group_by(participant, stim_type, session, task, block_nr_exp, is_trigger) %>%
  summarise(dprime_new = mean(dprime),
            SD_dprime_new = sd(dprime),
            std.error_dprime_new = std.error(dprime), .groups = "drop_last")

lmm_nback_dprime_online <- lmerTest::lmer(dprime_new ~
    stim_type +
    task +
    session +
    is_trigger +
    scale(block_nr_exp, scale = FALSE) +
    #scale(education_years, scale = FALSE) +
    #scale(Age, scale = FALSE) +
    #scale(executive_sum, scale = FALSE) +
    #scale(RS, scale = FALSE) +
    #scale(sideEffects_sum, scale = FALSE) +
    stim_type:task +
    stim_type:is_trigger + 
    (1 + task | participant),
  data = subset(nback_df_dprime_online, stim_type != "Offline"), 
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

anova(lmm_nback_dprime_online)
summary(lmm_nback_dprime_online)
```

## Raw Data Plots
### Plot RTs
```{r plot single n-back tasks}
nback_only_correct_nback_trials <- nback_only_correct_nback_trials %>% 
  mutate(task = dplyr::recode(task, "1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual"))

# Summary df by condition
nback_summary <- nback_only_correct_nback_trials %>% 
  group_by(stim_type, task) %>%
  summarise(mean_rt = mean(RT),
            SD_rt = sd(RT),
            std.error_rt = std.error(RT))
nback_summary$stim_task <- interaction(nback_summary$stim_type, nback_summary$task, drop = TRUE)

RT_nback_part <- nback_only_correct_nback_trials %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_rt = mean(RT))
RT_nback_part$stim_task <- interaction(RT_nback_part$stim_type, RT_nback_part$task, drop = TRUE)

#1) Boxplot of RTs by Task and Stimulation ----
(RT_nback_raw_boxplot <- ggplot(nback_summary, aes(x = stim_type, y = mean_rt, group = task)) +
    #geom_bar(aes(), stat = "identity", width = 0.5) +
    #geom_errorbar(aes(ymin = mean_rt - std.error_rt, ymax = mean_rt + std.error_rt), width =0.07, linewidth=0.7) +
    geom_boxplot(RT_nback_part, mapping = aes(x = stim_type, y = mean_rt, fill = stim_task, group = stim_task)) +
    geom_point2(shape = 18, size = 2, position = position_dodge(width = 0.75)) +
    geom_line(aes(x = stim_type, y = mean_rt, group = 1), color="black", linetype="dotted", position = position_dodge(width = 0.75))+
    scale_fill_manual(values = cols_nback) +
    scale_color_manual(values = cols_nback) +
    scale_y_continuous(limits = c(550, 1800), breaks = c(800, 1200, 1600)) +
    scale_x_discrete(labels = c(rep(c("Sham", "Offline", "Offline+Online"), 3))) +
    #coord_cartesian(ylim = c(400, 1600)) +
    facet_grid(~ task, scales = "free_x", space = "free_x") +
    ylab("Reaction time in ms") +
    xlab("Task") +
    theme_bw(base_size = 9.5)+
    theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1))
)

#2) Violin plot with individual participant lines ----
(RT_nback_raw_violin <- ggplot(RT_nback_part, aes(x = stim_type, y = mean_rt, group = task)) +
  geom_violinhalf(data = RT_nback_part, mapping = aes(fill = stim_task, group = stim_task), alpha = 1, color = NA, trim = TRUE, flip = FALSE, position = position_nudge(x =  0.15)) +
  geom_point2(position = position_jitter(width = 0.1, seed = 42), size = 1.5, alpha = .35) +
  geom_line(mapping = aes(group = participant), color = "#878787", linewidth = 0.2, alpha = 0.55, position = position_jitter(width = 0.1, seed = 42)) +
  facet_grid(~ task, scales = "free_x", space = "free_x") +
  scale_fill_manual(values = cols_nback) +
  scale_color_manual(values = cols_nback) +
  scale_x_discrete(expand = expansion(mult = c(0.15, 0.35))) +
  scale_y_continuous(limits = c(550, 1800), breaks = c(800, 1200, 1600)) +
  ylab("Reaction time in ms") +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1))
)

## arrange plots ----
RT_nback_raw <- ggarrange(RT_nback_raw_boxplot,
            RT_nback_raw_violin +
              theme(axis.title.y = element_blank(),
                    axis.text.y = element_blank(),
                    axis.ticks.y = element_blank(),
                    axis.line.y = element_blank()),
            nrow = 1)
            #heights = c(1,1))
            #widths = c(0.7,0.55),


ggsave(RT_nback_raw, file = here::here(paste0("Plots/RT_nback_raw_", today, ".pdf")), width = 130, height = 70, units = "mm")

#2) Plot RT across time_from_task by stim_type ----
(RT_raw_time <- ggplot(nback_only_correct_nback_trials, aes(x = time_from_onset_task, y = nback_RT, fill = stim_type, color = stim_type)) +
    #geom_boxplot(RT_nback_part, mapping = aes(x = task, y = mean_rt, fill = stim_type)) +
    geom_point2(size = 1, alpha = 0.2) +
    geom_smooth(method = "loess") +
    #geom_line(aes(x = task, y = mean_rt, group = stim_type), color="black", linetype="dotted", position = position_dodge(width = 0.75))+
    #geom_violinhalf(RT_nback_part, mapping = aes(x = task, y = mean_rt, fill = stim_type)) +
    scale_fill_manual(values = cols_nback) +
    scale_color_manual(values = cols_nback) +
    #scale_y_continuous(breaks = c(1000, 2000, 3000, 4000, 5000, 6000)) +
    coord_cartesian(ylim = c(400, 1000)) +
    ylab("Reaction Time in ms") +
    xlab("Time from Task Onset in s") +
    theme_bw()+
    theme(legend.position = "bottom",
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         axis.line = element_line(),
         axis.text.y = element_text(size = 10),
         #axis.title.x = element_blank(),
         axis.text.x.bottom = element_text(size = 9.5)) 
    #facet_wrap(~ block_name, nrow = 2)
)

ggsave(RT_single_nback_raw, file = here::here(paste0("Plots/RT_single_nback_raw_", today, ".png")), width = 210, height = 100, units = "mm")

# Plot online trials only ----
RT_nback_online <- nback_df_online %>% 
  group_by(stim_type, task) %>%
  summarise(mean_rt = mean(nback_RT),
            SD_rt = sd(nback_RT),
            std.error_rt = std.error(nback_RT))

RT_nback_online_part <- nback_df_online %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_rt = mean(nback_RT))
RT_nback_online_part$stim_task <- interaction(RT_nback_online_part$stim_type, RT_nback_online_part$task)

##1) Boxplot of RTs by Task and Stimulation ----
(RT_nback_raw_online_boxplot <- ggplot(RT_nback_online, aes(x = stim_type, y = mean_rt, group = task)) +
    #geom_bar(aes(), stat = "identity", width = 0.5) +
    #geom_errorbar(aes(ymin = mean_rt - std.error_rt, ymax = mean_rt + std.error_rt), width =0.07, linewidth=0.7) +
    geom_boxplot(RT_nback_online_part, mapping = aes(x = stim_type, y = mean_rt, fill = stim_task, group = stim_task)) +
    geom_point2(shape = 18, size = 2, position = position_dodge(width = 0.75)) +
    geom_line(aes(x = stim_type, y = mean_rt, group = 1), color = "black", linetype = "dotted", position = position_dodge(width = 0.75))+
    scale_fill_manual(values = cols_nback[c(1,3,4,6,7,9)]) +
    scale_color_manual(values = cols_nback[c(1,3,4,6,7,9)]) +
    scale_y_continuous(limits = c(350, 1200), breaks = c(400, 800, 1200)) +
    scale_x_discrete(labels = c(rep(c("Sham", "Online"), 3))) +
    #coord_cartesian(ylim = c(400, 1600)) +
    facet_grid(~ task) +
    ylab("Reaction time in ms") +
    xlab("Task") +
    theme_bw(base_size = 9.5)+
    theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1)) 
)

#2) Violin plot with individual participant lines
(RT_nback_raw_online_violin <- ggplot(RT_nback_online_part, aes(x = stim_type, y = mean_rt, group = task)) +
  geom_violinhalf(data = RT_nback_online_part, mapping = aes(fill = stim_task, group = stim_task), alpha = 1, color = NA, trim = TRUE, flip = FALSE, position = position_nudge(x =  0.15)) +
  geom_point2(position = position_jitter(width = 0.1, seed = 42), size = 1.5, alpha = .35) +
  geom_line(mapping = aes(group = participant), color = "#878787", linewidth = 0.2, alpha = 0.55, position = position_jitter(width = 0.1, seed = 42)) +
  facet_grid(~ task) +
  scale_fill_manual(values = cols_nback[c(1,3,4,6,7,9)]) +
  scale_color_manual(values = cols_nback[c(1,3,4,6,7,9)]) +
  scale_x_discrete(expand = expansion(mult = c(0.2, 0.65)), labels = c(rep(c("Sham", "Online"), 3))) +
  scale_y_continuous(limits = c(350, 1200), breaks = c(400, 800, 1200)) +
  ylab("Reaction time in ms") +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 10),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.5),
       axis.title.x = element_blank(),
       axis.text.x = element_text(size = 8.5, angle = 45, vjust = 1, hjust = 1)) #angle = 45, vjust = 1, hjust = 1
)

## arrange plots ----
RT_nback_online_raw <- ggarrange(RT_nback_raw_online_boxplot,
            RT_nback_raw_online_violin +
              theme(axis.title.y = element_blank(),
                    axis.text.y = element_blank(),
                    axis.ticks.y = element_blank(),
                    axis.line.y = element_blank()),
            nrow = 1)
            #heights = c(1,1))
            #widths = c(0.7,0.55),


ggsave(RT_nback_online_raw, file = here::here(paste0("Plots/RT_nback_raw_online_", today, ".pdf")), width = 130, height = 60, units = "mm")
```

### Plot D-prime
```{r plot single n-back tasks}
# Create d-prime df from n-back_df
nback_df_dprime <- nback_df %>% 
  select(participant, stim_type, task, session, cognitive_load, dprime, is_trigger, sideEffects_sum, block_nr_exp, RS, executive_sum, education_years, Age, task_onset) %>% 
  distinct()

# Summary df by task and stim
dprime_nback <- nback_df_dprime %>% 
  group_by(stim_type, task) %>%
  summarise(mean_dprime = mean(dprime),
            SD_dprime = sd(dprime),
            std.error_dprime = std.error(dprime), .groups = "drop_last")

# Summary df by task, stim, participant
dprime_nback_part <- nback_df_dprime %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_dprime = mean(dprime), .groups = "drop_last")

# Plot raw d-primes ----
(dprime_nback_raw_boxplot <- ggplot(dprime_nback, aes(x = stim_type, y = mean_dprime, fill = stim_type)) +
    geom_boxplot(dprime_nback_part, mapping = aes(x = stim_type, y = mean_dprime, fill = stim_type)) +
    geom_point2(shape = 18, size = 3.5) +
    geom_line(aes(x = stim_type, y = mean_dprime, group=1), color="black", linetype="dotted")+
    scale_fill_manual(values = cols_nback) +
    scale_color_manual(values = cols_nback) +
    #scale_x_discrete(expand = expansion(add = c(0.8, 0.5))) +
    ylab("D-prime") +
    xlab("Stimulation condition") +
    facet_grid(~ task, scales = "free_x", space = "free_x") +
    theme_bw()+
    theme(legend.position = "none",
         strip.background = element_blank(),
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         axis.line = element_line(),
         axis.text.y = element_text(size = 10),
         axis.title.x = element_blank(),
         axis.text.x = element_text(angle = 45, hjust = 1),
         axis.text.x.bottom = element_text(size = 9.5)) 
)

(dprime_nback_raw_violin <- ggplot(dprime_nback_part, aes(x = stim_type, y = mean_dprime, fill = stim_type)) +
    geom_violinhalf(dprime_nback_part[dprime_nback_part$stim_type == "Sham",], mapping = aes(x = stim_type, y = mean_dprime, group = stim_type, fill = stim_type), alpha = 1, color = NA, trim = TRUE, flip = F, position = position_nudge(x = .25)) +
    geom_violinhalf(dprime_nback_part[dprime_nback_part$stim_type == "Offline",], mapping = aes(x = stim_type, y = mean_dprime, group = stim_type, fill = stim_type), alpha = 1, color = NA, trim = TRUE, flip = F, position = position_nudge(x = .25)) +
    geom_violinhalf(dprime_nback_part[dprime_nback_part$stim_type == "Offline + Online",], mapping = aes(x = stim_type, y = mean_dprime, group = stim_type, fill = stim_type), alpha = 1, color = NA, trim = TRUE, flip = F, position = position_nudge(x = .25)) +
    geom_point2(position = position_jitter(width = 0.1, seed = 42), size = 2.5, alpha = .35) +
    geom_line(mapping = aes(group = participant), color = "#878787", linewidth = 0.2, alpha = 0.55, position = position_jitter(width = 0.1, seed = 42)) +
    scale_fill_manual(values = cols_nback) +
    scale_color_manual(values = cols_nback) +
    scale_x_discrete(expand = expansion(add = c(0.2, 0.8))) +
    facet_grid(~ task) +
    ylab("Dprime") +
    xlab("Stimulation condition") +
    theme_bw()+
    theme(legend.position = "none",
         strip.background = element_blank(),
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         axis.line = element_line(),
         axis.text.y = element_text(size = 10),
         axis.title.x = element_blank(),
         axis.text.x = element_text(angle = 45, hjust = 1),
         axis.text.x.bottom = element_text(size = 9.5))
)

(dprime_nback_raw <- ggarrange(dprime_nback_raw_boxplot +
                                 theme(strip.text.y = element_blank()),
            dprime_nback_raw_violin +
              theme(axis.title.y = element_blank(),
                    axis.text.y = element_blank(),
                    axis.ticks.y = element_blank(),
                    axis.line.y = element_blank()),
            #widths = c(0.7,0.55),
            nrow = 1)
)

ggsave(dprime_nback_raw, file = here::here(paste0("Plots/Dprime_nback_raw_", today, ".png")), width = 150, height = 120, units = "mm")

# Split by is_trigger ----
# Summary df by condition
dprime_nback <- nback_df_dprime %>% 
  group_by(stim_type, task, is_trigger) %>%
  summarise(mean_dprime = mean(dprime_new),
            SD_dprime = sd(dprime_new),
            std.error_dprime = std.error(dprime_new), .groups = "drop_last")

# Summary df by condition, participant
dprime_nback_part <- nback_df_dprime %>% 
  group_by(participant, stim_type, task, is_trigger) %>% 
  summarise(mean_dprime = mean(dprime_new), .groups = "drop_last")

(dprime_nback_raw_boxplot_trigger <- ggplot(dprime_nback, aes(x = stim_type, y = mean_dprime, fill = stim_type)) +
    geom_boxplot(dprime_nback_part, mapping = aes(x = stim_type, y = mean_dprime, fill = stim_type)) +
    geom_point2(shape = 18, size = 3.5) +
    geom_line(aes(x = stim_type, y = mean_dprime, group=1), color="black", linetype="dotted")+
    scale_fill_manual(values = cols_nback) +
    scale_color_manual(values = cols_nback) +
    #scale_x_discrete(expand = expansion(add = c(0.8, 0.5))) +
    ylab("N-back task\nD-prime") +
    xlab("Stimulation Condition") +
    facet_grid(task ~ is_trigger, scales = "free_x", space = "free_x", labeller = labeller(is_trigger = c("False" = "No TMS train", "True" = "With TMS train")),) +
    theme_bw()+
    theme(legend.position = "none",
         strip.background = element_blank(),
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         axis.line = element_line(),
         axis.text.y = element_text(size = 10),
         axis.title.x = element_blank(),
         axis.text.x = element_text(angle = 45, hjust = 1),
         axis.text.x.bottom = element_text(size = 9.5)) 
)

ggsave(dprime_nback_raw, file = here::here(paste0("Plots/Dprime_nback_raw_", today, ".png")), width = 150, height = 120, units = "mm")

# Plot numbers of hits and errors ----

# Summary df by condition, participant
count_summary_df <- nback_df %>%
  filter(nback_response != "correct rejection") %>%
  group_by(participant, stim_type, task, is_trigger, nback_response) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(stim_type, task, is_trigger, nback_response) %>%
  summarise(
    mean_count = mean(count),
    se_count = sd(count) / sqrt(n()),
    ci_lower = mean_count - qt(0.975, n()-1) * se_count,
    ci_upper = mean_count + qt(0.975, n()-1) * se_count,
    .groups = "drop"
  )

# Plot with error bars
(nback_acc_nback_task <- ggplot(count_summary_df, aes(x = stim_type, y = mean_count, fill = nback_response)) +
  geom_col(position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = mean_count - se_count, ymax = mean_count + se_count),
                position = position_dodge(width = 0.9), 
                width = 0.25) +
  scale_fill_manual(values = cols_nback) +
  ylab("Mean Count") +
  xlab("Stimulation Condition") +
  facet_grid(task ~ is_trigger, scales = "free_x", space = "free_x",
             labeller = labeller(is_trigger = c("False" = "No TMS train", 
                                                "True" = "With TMS train"))) +
  theme_bw()+
    theme(legend.position = "bottom",
         strip.background = element_blank(),
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         axis.line = element_line(),
         axis.text.y = element_text(size = 10),
         axis.title.x = element_blank(),
         axis.text.x = element_text(angle = 45, hjust = 1),
         axis.text.x.bottom = element_text(size = 9.5)) 
)

ggsave(nback_acc_nback_task, file = here::here(paste0("Plots/Nback_acc_nback_raw_", today, ".png")), width = 150, height = 120, units = "mm")
```

## Prepare df for HSSM 
Required Data Structure for HSSM
- we need variables labeled as "rt" and "response"
- make sure rt are in seconds
- responses are (1,-1) because you are in a classical DDM setting
- make sure regressors are z-scored (particularly important when you have more than two regressors)
```{r}
# df with all trials
# n-back RT when n-back button was pressed, else regular RT
nback_hssm <- nback_df %>% 
  ungroup() %>% 
  select(participant, stim_type, session, task, RT, nback_RT, nback_acc, surprisal_2, entropy_2, zipf_frequency, word_length_single, is_trigger, time_from_onset_task) %>% 
  mutate(response = case_when(
    nback_acc == "correct" ~ 1,
    nback_acc == "incorrect" ~ -1,
    TRUE ~ NA),
    rt = case_when(
      !is.na(nback_RT) ~ nback_RT,
      is.na(nback_RT) ~ RT,
      TRUE ~ NA)) %>% 
  mutate(rt = rt/1000) %>% 
  filter(rt > 0.15) # excldue values below 150 ms

# save df only for n-back tasks (no dual task, no surprisal, etc)
df_nback_hssm <- nback_hssm %>% 
  filter(task != "2back_dual_main_click") %>% 
  select(-c(RT, nback_RT, nback_acc, surprisal_2, entropy_2, zipf_frequency, word_length_single)) %>% 
  mutate(across(c(time_from_onset_task), ~ scale(.x, scale = TRUE)))

write.csv(df_nback_hssm, file = "/data/p_03049/EXNAT_4_TMS/HSSM/Data/HSSM_nback_df.csv", row.names = FALSE)

# save df only for actual n-back trials (all tasks)
hssm_nback_only_nback_trials <- nback_hssm %>% 
  select(participant, stim_type, task, rt, response)

# df only for dual task to include surprisal as well
dual_task_hssm <- nback_df %>% 
  filter(task == "2back_dual_main_click") %>% 
  filter(!is.na(surprisal_2)) %>% 
  filter(surprisal_2 < 40) %>% 
  ungroup() %>% 
  select(participant, stim_type, session, task, RT, nback_RT, nback_acc, surprisal_2, entropy_2, zipf_frequency, word_length_single, is_trigger, time_from_onset_task) %>% 
  mutate(response = case_when(
    nback_acc == "correct" ~ 1,
    nback_acc == "incorrect" ~ -1,
    TRUE ~ NA),
    rt = case_when(
      !is.na(nback_RT) ~ nback_RT,
      is.na(nback_RT) ~ RT,
      TRUE ~ NA)) %>% 
  mutate(rt = rt/1000) %>% 
  filter(rt > 0.15) # exclude values below 150 ms

# save df
df_dual_task_hssm <- dual_task_hssm %>% 
  select(-c(task, RT, nback_RT, nback_acc)) %>% 
  mutate(across(c(time_from_onset_task, surprisal_2, entropy_2, zipf_frequency, word_length_single), ~ scale(.x, scale = TRUE)))

write.csv(df_dual_task_hssm, file = "/data/p_03049/EXNAT_4_TMS/HSSM/Data/HSSM_dual_task_df.csv", row.names = FALSE)
```

## E-FIELDS
### Correlations with raw data
```{r efields prepare df}
# Read in file with e-fields (95 percentile from 10 mm ROI around stim coordinates) and prepare df
df_efields = read.table(here::here("average_efields_sphere_10mm_percentile_95.txt"), header = T, sep = ",")
df_efields$participant <- gsub("sub-", "", df_efields$participant)

df_efields <- df_efields %>% 
  rename(stim_type = session)
df_efields$stim_type <- as.factor(df_efields$stim_type)
df_efields$stim_type <- dplyr::recode(df_efields$stim_type, 
                               "offline" = "Offline", 
                               "offline_online" = "Offline + Online")

# Prepare df
df_nback <- nback_only_correct_nback_trials %>% 
  filter(stim_type != "Sham") %>% 
  droplevels() %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_RT = mean(nback_RT),
            mean_dprime = mean(dprime)) %>% 
  mutate(task = dplyr::recode(task, "1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual"))

df_nback <- full_join(df_nback, df_efields, relationship = "many-to-many")

# Correlation for offline AG session ----
cor_results_nback_offline <- df_nback %>%
  filter(stim_type == "Offline" & participant != "07") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$mean_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$mean_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  })

# plot result
df_nback_offline <- df_nback %>%
  filter(
    stim_type == "Offline",
    !is.na(mean_RT)
  ) %>%
  droplevels()

ann_RT <- cor_results_nback_offline %>%
  transmute(
    task,
    label = sprintf("r = %.2f\np = %.3f", estimate_RT, p.value_RT),
    x = max(df_nback_offline$mean_field, na.rm = TRUE),
    y = 1100)

(corr_nback_offline_RT_efield <- ggplot(
  df_nback_offline, aes(x = mean_field, y = mean_RT)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.5) +
  geom_text(
    data = ann_RT,
    aes(x = x, y = y, label = label),
    hjust = 1, vjust = 1, size = 3, show.legend = FALSE
  ) +
  facet_wrap(~ task) +
  labs(
    x = "Mean E-field (AG)",
    y = "Mean RT N-back",
    title  = "Mean E-field vs N-back RT (AG, Offline)"
  ) +
  theme_bw()
)

ggsave(corr_nback_offline_RT_efield, file = here("Plots/E-field_Correlations/corr_nback_offline_RT_efield.png"))

# Correlation for offline AG during offline+online session ----
cor_results_nback_offline_online_AG <- df_nback %>%
  filter(stim_type == "Offline + Online" & roi == "AG") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$mean_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$mean_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  })

# plot result
df_nback_offline_online <- df_nback %>%
  filter(stim_type == "Offline + Online" & roi == "AG" & !is.na(mean_RT)) %>%
  droplevels()

ann_RT <- cor_results_nback_offline_online_AG %>%
  transmute(
    task,
    label = sprintf("r = %.2f\np = %.3f", estimate_RT, p.value_RT),
    x = max(df_nback_offline_online$mean_field, na.rm = TRUE),
    y = 1100)

(corr_nback_offline_online_AG_RT_efield <- ggplot(
  df_nback_offline_online, aes(x = mean_field, y = mean_RT)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.5) +
  geom_text(
    data = ann_RT,
    aes(x = x, y = y, label = label),
    hjust = 1, vjust = 1, size = 3, show.legend = FALSE
  ) +
  facet_wrap(~ task) +
  labs(
    x = "Mean E-field (AG)",
    y = "Mean RT N-back",
    title  = "Mean E-field vs N-back RT (AG, Offline + Online)"
  ) +
  theme_bw()
)

ggsave(corr_nback_offline_online_AG_RT_efield, file = here("Plots/E-field_Correlations/corr_nback_offline_online_AG_RT_efield.png"))


# Correlation for online DLPFC during offline+online session ----
cor_results_nback_offline_online_DLPFC <- df_nback %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$mean_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$mean_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  })

# plot result
df_nback_offline_online <- df_nback %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC" & !is.na(mean_RT)) %>%
  droplevels()

ann_RT <- cor_results_nback_offline_online_DLPFC %>%
  transmute(
    task,
    label = sprintf("r = %.2f\np = %.3f", estimate_RT, p.value_RT),
    x = max(df_nback_offline_online$mean_field, na.rm = TRUE),
    y = 1100)

(corr_nback_offline_online_DLPFC_RT_efield <- ggplot(
  df_nback_offline_online, aes(x = mean_field, y = mean_RT)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.5) +
  geom_text(
    data = ann_RT,
    aes(x = x, y = y, label = label),
    hjust = 1, vjust = 1, size = 3, show.legend = FALSE
  ) +
  facet_wrap(~ task) +
  labs(
    x = "Mean E-field (DLPFC)",
    y = "Mean RT N-back",
    title  = "Mean E-field vs N-back RT (DLPFC, Offline + Online)"
  ) +
  theme_bw()
)

ggsave(corr_nback_offline_online_DLPFC_RT_efield, file = here("Plots/E-field_Correlations/corr_nback_offline_online_DLPFC_RT_efield.png"))

# Check separately for trials with and without trigger during offline+online session ----
df_nback <- nback_only_correct_nback_trials %>% 
  filter(stim_type != "Sham") %>% 
  droplevels() %>% 
  group_by(participant, stim_type, task, is_trigger) %>% 
  summarise(mean_RT = mean(nback_RT),
            mean_dprime = mean(dprime)) %>% 
  mutate(task = dplyr::recode(task, "1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual"))

df_nback <- full_join(df_nback, df_efields, relationship = "many-to-many")

# Correlation for online DLPFC during offline+online session
cor_results_nback_offline_online_DLPFC <- df_nback %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC" & !is.na(mean_RT)) %>%
  droplevels() %>%
  group_by(task, is_trigger) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$mean_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$mean_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  }) %>% 
  ungroup() %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"),
    p_FDR_dprime  = p.adjust(p.value_dprime, method = "fdr"))

# plot result
df_nback_offline_online_trigger <- df_nback %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC" & !is.na(mean_RT)) %>%
  droplevels()

ann_RT <- cor_results_nback_offline_online_DLPFC %>%
  transmute(
    task,
    is_trigger,
    label = sprintf("r = %.2f\np = %.3f", estimate_RT, p.value_RT),
    x = max(df_nback_offline_online_trigger$mean_field, na.rm = TRUE),
    y = case_when(
      is_trigger == "True" ~ 1100,
      is_trigger == "False" ~ 1000,
    ))
  #filter(is_trigger == "True")

(corr_nback_offline_online_DLPFC_RT_efield_trigger <- ggplot(df_nback_offline_online_trigger, aes(x = mean_field, y = mean_RT, color = is_trigger)) +
  geom_point(size = 2, aes(shape = is_trigger)) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.5) +
  geom_text(
    data = ann_RT,
    aes(x = x, y = y, label = label, colour = is_trigger),
    hjust = 1, vjust = 1, size = 3, show.legend = FALSE
  ) +
  facet_wrap(~ task) +
  labs(
    x = "Mean E-field (DLPFC)",
    y = "Mean RT N-back",
    title  = "Mean E-field vs N-back RT (DLPFC, Offline + Online)"
  ) +
  theme_bw(base_size = 8.5) +
  theme(legend.position = "bottom")
)

ggsave(corr_nback_offline_online_DLPFC_RT_efield_trigger, file = here("Plots/E-field_Correlations/corr_nback_offline_online_DLPFC_RT_efield_trigger.png"), width = 110, height = 80, units = "mm")

# Look at all n-back responses with a trigger (no matter if false or correct) ----
# the difference in n reactions (only correct vs all) is actually only 143 trials
df_nback_all_trigger <- nback_df %>% 
  filter(stim_type != "Sham" & (nback_response == "false alarm" | nback_response == "hit")) %>% 
  droplevels() %>% 
  group_by(participant, stim_type, task, is_trigger) %>% 
  summarise(mean_RT = mean(nback_RT),
            mean_dprime = mean(dprime)) %>% 
  mutate(task = dplyr::recode(task, "1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual"))

df_nback_all_trigger <- full_join(df_nback_all_trigger, df_efields, relationship = "many-to-many")

# Correlation for online DLPFC during offline+online session
cor_results_nback_offline_online_DLPFC_trigger <- df_nback_all_trigger %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC" & !is.na(mean_RT)) %>%
  droplevels() %>%
  group_by(task, is_trigger) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$mean_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$mean_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  }) %>% 
  ungroup() %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"),
    p_FDR_dprime  = p.adjust(p.value_dprime, method = "fdr"))

# Linear regression for offline + online session ----
df_nback_wide <- df_nback %>% 
  filter(stim_type == "Offline + Online") %>% 
  droplevels() %>%
  pivot_wider(names_from = roi, values_from = mean_field)

for(load in unique(df_nback_wide$task)) {
  dat <- df_nback_wide %>% filter(task == load)
  assign(
    paste0("rt_model_", load),
    lm(mean_RT ~ AG + DLPFC * is_trigger, data = dat)
  )
  assign(
    paste0("dprime_model_", load),
    lm(mean_dprime ~ AG + DLPFC * is_trigger, data = dat)
  )
}

summary(`rt_model_1-back`)
summary(`rt_model_2-back`)
summary(`rt_model_2-back dual`)

#----- correlate e-field with subject-specific slopes for TMS
subj_slopes <- subj_slopes %>% 
  rename(participant = Subject)

df_efields_wide <- df_efields %>% 
  pivot_wider(names_from = c(stim_type, roi), values_from = mean_field)

df_efield_slopes <- left_join(df_efields_wide, subj_slopes)
df_efield_slopes <- df_efield_slopes %>% 
  rename(offline_online_AG = `Offline + Online_AG`,
         offline_online_DLPFC = `Offline + Online_DLPFC`) 

ggscatterhist(df_efield_slopes, x = "Offline_AG", y = "slope_TMS_offline", 
              add = "reg.line", cor.coef = TRUE)
ggscatterhist(df_efield_slopes, x = "offline_online_AG", y = "slope_TMS_offline_online", 
              add = "reg.line", cor.coef = TRUE)
ggscatterhist(df_efield_slopes, x = "offline_online_DLPFC", y = "slope_TMS_offline_online", 
              add = "reg.line", cor.coef = TRUE)
```

### Moderating role of e-fields
```{r}
# AG ----
nback_only_correct_nback_trials_No_sham <- subset(nback_only_correct_nback_trials, stim_type != "Sham")
nback_only_correct_nback_trials_No_sham <- droplevels(nback_only_correct_nback_trials_No_sham)

c <- contr.treatment(2) 
my.coding <- matrix(rep(1/2, 2), ncol = 1) 
my.simple <- c-my.coding
contrasts(nback_only_correct_nback_trials_No_sham$stim_type) <- my.simple

c <- contr.treatment(3) 
my.coding <- matrix(rep(1/3, 6), ncol = 2) 
my.simple <- c-my.coding
contrasts(nback_only_correct_nback_trials_No_sham$task) <- my.simple

lmm_nback_Efield_AG <- lmerTest::lmer(
  log(nback_RT) ~ task * scale(efield_AG, scale = FALSE) +
    (1 + task | participant),
  data = nback_only_correct_nback_trials_No_sham,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

summary(lmm_nback_Efield_AG)
anova(lmm_nback_Efield_AG)

plot(predict_response(lmm_nback_Efield_AG, c("efield_AG", "task")))

## Plot ----
pred_nback_efield_AG <- predict_response(lmm_nback_Efield_AG, c("efield_AG", "task"), margin = "marginalmeans")

participant_points <- collapse_by_group(pred_nback_efield_AG, lmm_nback_Efield_AG, "participant")
participant_points <- participant_points %>% 
  group_by(participant, task) %>% 
  summarise(efield_AG = mean(efield_AG),
            nback_RT = mean(nback_RT))

(RT_nback_efield_AG <- ggplot(pred_nback_efield_AG, aes(x = x, y = predicted, color = group, fill = group)) +
  geom_jitter2(participant_points, mapping = aes(x = efield_AG, y = nback_RT, color = task), inherit.aes = FALSE, alpha = 0.35, size = 2.2, position = position_jitter(width = 1)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
  geom_line(linewidth = .7) +
  #facet_wrap(~ task, labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task")), scales = "free_x") +
  ylab("Predicted reaction time in ms") +
  xlab("E-field AG in V/m") +
  scale_x_continuous(breaks = c(50,80,110)) +
  #coord_cartesian(ylim = c(230, 1530)) +
  scale_color_manual(values = cols_nback[c(2,5,8)]) +
  scale_fill_manual(values = cols_nback[c(2,5,8)]) +
  theme_bw(base_size = 8)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 9),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 8))
)
ggsave(RT_nback_efield_AG, file = here(paste0("Plots/RT_nback_efield_AG_", today, ".pdf")), width = 40, height = 45, units = "mm")

# DLPFC ----
nback_only_correct_nback_trials_No_sham <- subset(nback_only_correct_nback_trials, stim_type == "Offline + Online")
nback_only_correct_nback_trials_No_sham <- droplevels(nback_only_correct_nback_trials_No_sham)

c <- contr.treatment(2) 
my.coding <- matrix(rep(1/2, 2), ncol = 1) 
my.simple <- c-my.coding
contrasts(nback_only_correct_nback_trials_No_sham$is_trigger) <- my.simple

c <- contr.treatment(3) 
my.coding <- matrix(rep(1/3, 6), ncol = 2) 
my.simple <- c-my.coding
contrasts(nback_only_correct_nback_trials_No_sham$task) <- my.simple

lmm_nback_Efield_DLPFC <- lmerTest::lmer(log(nback_RT) ~ 
    task +
    scale(efield_DLPFC, scale = FALSE) + 
    is_trigger +
    task : scale(efield_DLPFC, scale = FALSE) + 
    task : is_trigger +
    scale(efield_DLPFC, scale = FALSE) : is_trigger +
    task : scale(efield_DLPFC, scale = FALSE) : is_trigger +
    (1 + task | participant),
  data = nback_only_correct_nback_trials_No_sham,
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa"))

summary(lmm_nback_Efield_DLPFC)
anova(lmm_nback_Efield_DLPFC)

tab_model(lmm_nback_Efield_AG,
          lmm_nback_Efield_DLPFC,
  show.intercept = FALSE,
  show.icc = TRUE,   # ICC (Intraclass Correlation) is not always needed
  show.re.var = TRUE,  # Show variance of random effects
  show.df = FALSE,     # Don't display degrees of freedom
  show.obs = FALSE,    # Don't display number of observations
  show.ngroups = FALSE, # Don't display number of groups for random effects
  show.stat = TRUE,    # Show model statistics (e.g., p-values, F-values)
  collapse.ci = TRUE,  # Collapse confidence intervals into one line
  dv.labels = c("E-field AG", "E-field DLPFC"),
  file = here("Model_tables/nback_efields.doc")
)

## Plot ----
pred_nback_efield_DLPFC <- predict_response(lmm_nback_Efield_DLPFC, c("is_trigger"), margin = "marginalmeans")

(RT_nback_efield_DLPFC <- plot(pred_nback_efield_DLPFC, collapse_group = TRUE, jitter = 0.08, dot_alpha = 0.15) +
  ylab("Predicted reaction time in ms") +
  xlab("Online TMS trigger") +
  scale_y_continuous(breaks = extended_breaks(3)) +
  #coord_cartesian(ylim = c(230, 1530)) +
  theme_bw(base_size = 8)+
  theme(legend.position = "bottom",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       plot.title = element_blank(),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8),
       #axis.title.x = element_text(size = 9),
       axis.text.x = element_text(size = 8))
)

ggsave(RT_nback_efield_DLPFC, file = here(paste0("Plots/RT_nback_efield_DLPFC.pdf")), width = 40, height = 45, units = "mm")
```


## DELTAS
### Classify TMS reaction
```{r}
# RT ----
# Prepare df
df_nback <- nback_only_correct_nback_trials %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_RT = mean(nback_RT),
            mean_dprime = mean(dprime))

df_nback_deltas <- df_nback %>% 
  pivot_wider(
    id_cols  = c(participant, task),
    names_from  = stim_type,
    values_from = c(mean_RT, mean_dprime)
  ) %>% 
  mutate(
    delta_RT_Offline = mean_RT_Offline - mean_RT_Sham,
    delta_RT_Offline_Online = `mean_RT_Offline + Online` - mean_RT_Sham,
    delta_dprime_Offline = mean_dprime_Offline - mean_dprime_Sham,
    delta_dprime_Offline_Online = `mean_dprime_Offline + Online` - mean_dprime_Sham
  ) %>% 
  select(participant, task, delta_RT_Offline, delta_RT_Offline_Online, delta_dprime_Offline, delta_dprime_Offline_Online) %>% 
  pivot_longer(
    cols = starts_with("delta_"),
    names_to = c(".value", "stim_type"),
    names_pattern = "(delta_(?:RT|dprime))_(.*)") %>% 
  mutate(stim_type = dplyr::recode(stim_type,
      "Offline"          = "Offline",
      "Offline_Online"   = "Offline + Online"), 
    direction_RT = case_when(
        delta_RT < -10 ~ "Faster",
        delta_RT > 10 ~ "Slower",
        is.na(delta_RT) ~ NA,
        TRUE ~ "No change"),
    direction_dprime = case_when(
      delta_dprime > 0 ~ "Better",
      delta_dprime < 0 ~ "Worse",
      is.na(delta_dprime) ~ NA,
      TRUE ~ "No change"),
    direction_RT = factor(direction_RT, levels = c("Faster", "No change", "Slower")),
    direction_dprime = factor(direction_dprime, levels = c("Better", "No change", "Worse")),
    task = dplyr::recode(task, "1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual"))

# run LMMs on data
m1 <- lmer(delta_RT ~ task * stim_type + direction_dprime + (1+task+stim_type|participant), data = df_nback_deltas)
summary(m1)

## Plots ----
# scatter plot
(plot_change_RT <- ggplot(df_nback_deltas[!is.na(df_nback_deltas$delta_RT),], aes(x = task, y = delta_RT, colour = direction_RT, label = participant, group = participant)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_point(position = position_dodge(width = 0.2), size = 1.3) +
  #geom_line(position = position_dodge(width = 0.2), alpha = 0.5) +
  geom_text_repel(size = 1.5, position = position_dodge(width = 0.2), show.legend = FALSE, max.overlaps = 60) +
  facet_wrap(~ stim_type, nrow = 1) +
  scale_fill_manual(values = cols_nback) +
  scale_color_manual(values = cols_nback) +
  labs(x = "Task", y = "Δ RT (TMS – Sham)", colour = "RT direction", title = "N-back: RT direction per participant and task") +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "bottom",
     text = element_text(family = "Helvetica"),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     strip.background = element_blank(),
     strip.text = element_text(size = 10),
     axis.line = element_line(),
     axis.text.y = element_text(size = 8.5),
     axis.title.x = element_blank(),
     axis.text.x = element_text(size = 8.5))
)

# donut plot
df_RT_donut <- df_nback_deltas %>% 
  filter(!is.na(delta_RT)) %>% 
  group_by(task, stim_type, direction_RT) %>% 
  summarise(n = n(), .groups = "drop_last") %>% 
  mutate(
    prop = n / sum(n),
    ymax = cumsum(prop),
    ymin = dplyr::lag(ymax, default = 0),
    label_pos = (ymax + ymin) / 2
  )

(plot_donut_RT <- ggplot(df_RT_donut, aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = direction_RT)) +
  geom_rect() +
  coord_polar(theta = "y") +
  xlim(c(2, 4)) +
  facet_wrap(~ stim_type + task, nrow = 1) +
  geom_text(aes(y = label_pos,x = 3.5, label = percent(prop, accuracy = 1)), colour = "black", size = 2) +
  scale_fill_manual(values = cols_nback) +
  scale_color_manual(values = cols_nback) +
  theme_void(base_size = 9.5) +
  theme(legend.position = "none",
        aspect.ratio = 1,
        text = element_text(family = "Helvetica"),)
)

nback_delta_RT <- ggarrange(plot_change_RT,
                            plot_donut_RT,
                            nrow = 2,
                            heights = c(0.9, 2.3))

ggsave(nback_delta_RT, file = here("Plots/nback_delta_RT.png"), width = 130, height = 140, units = "mm")

# D-prime ----

# run LMM on data
m1 <- lmer(delta_dprime ~ task * stim_type + direction_RT + (1|participant), data = df_nback_deltas)
summary(m1)

plot(predict_response(m1, "stim_type", margin = "marginalmeans"))

## Plots ----
df_nback_deltas <- df_nback_deltas %>% 
  mutate(direction_dprime = factor(direction_dprime, levels = c("Better", "Worse", "No change")))

# scatter plot
(plot_change_dprime <- ggplot(df_nback_deltas[!is.na(df_nback_deltas$delta_dprime),], aes(x = task, y = delta_dprime, colour = direction_dprime, label = participant, group = participant)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey50") +
  geom_point(position = position_dodge(width = 0.2), size = 1.3) +
  #geom_line(position = position_dodge(width = 0.2), color = "grey30", linetype = "dashed", alpha = 0.2) +
  geom_text_repel(size = 1.5, position = position_dodge(width = 0.2), show.legend = FALSE, max.overlaps = 60) +
  facet_wrap(~ stim_type, nrow = 1) +
  scale_fill_manual(values = cols_nback) +
  scale_color_manual(values = cols_nback) +
  labs(x = "Task", y = "Δ D-prime (TMS – Sham)", colour = "D-prime direction", title = "N-back: D-prime direction per participant and task") +
  theme_bw(base_size = 9.5) +
  theme(legend.position = "bottom",
     text = element_text(family = "Helvetica"),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     strip.background = element_blank(),
     strip.text = element_text(size = 10),
     axis.line = element_line(),
     axis.text.y = element_text(size = 8.5),
     axis.title.x = element_blank(),
     axis.text.x = element_text(size = 8.5))
)

# donut plot
df_dprime_donut <- df_nback_deltas %>% 
  filter(!is.na(delta_dprime)) %>% 
  group_by(task, stim_type, direction_dprime) %>% 
  summarise(n = n(), .groups = "drop_last") %>% 
  mutate(
    prop = n / sum(n),
    ymax = cumsum(prop),
    ymin = dplyr::lag(ymax, default = 0),
    label_pos = (ymax + ymin) / 2
  )

(plot_donut_dprime <- ggplot(df_dprime_donut, aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill = direction_dprime)) +
  geom_rect() +
  coord_polar(theta = "y") +
  xlim(c(2, 4)) +
  facet_wrap(~ stim_type + task, nrow = 1) +
  geom_text(aes(y = label_pos,x = 3.5, label = percent(prop, accuracy = 1)), colour = "black", size = 2) +
  scale_fill_manual(values = cols_nback) +
  scale_color_manual(values = cols_nback) +
  theme_void(base_size = 9.5) +
  theme(legend.position = "none",
        aspect.ratio = 1,
        text = element_text(family = "Helvetica"),)
)

nback_delta_dprime <- ggarrange(plot_change_dprime,
                            plot_donut_dprime,
                            nrow = 2,
                            heights = c(0.9, 2.3))

ggsave(nback_delta_dprime, file = here("Plots/nback_delta_dprime.png"), width = 130, height = 140, units = "mm")
```

### Correlate reaction with e-fields
Do people with a stronger reaction (either faster or slower) also have a stronger e-field?
```{r}
# Read in file with e-fields (95 percentile from 10 mm ROI around stim coordinates) and prepare df
df_efields = read.table(here::here("average_efields_sphere_10mm_percentile_95.txt"), header = T, sep = ",")
df_efields$participant <- gsub("sub-", "", df_efields$participant)

df_efields <- df_efields %>% 
  rename(stim_type = session)
df_efields$stim_type <- as.factor(df_efields$stim_type)
df_efields$stim_type <- dplyr::recode(df_efields$stim_type, 
                               "offline" = "Offline", 
                               "offline_online" = "Offline + Online")

df_nback_deltas_efields <- full_join(df_nback_deltas, df_efields, relationship = "many-to-many")

# Correlation for offline AG session ----
cor_results_nback_offline_delta_direction <- df_nback_deltas_efields %>%
  filter(stim_type == "Offline" & participant != "07") %>% #& direction_dprime != "No change"
  droplevels() %>%
  group_by(task, direction_RT) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$delta_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  }) %>% 
  ungroup() %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"),
    p_FDR_dprime  = p.adjust(p.value_dprime, method = "fdr"))

# Logistic regression
df_logit <- df_nback_deltas_efields %>%
  filter(
    stim_type == "Offline",
    participant != "07",
    direction_dprime %in% c("Better", "Worse")
  ) %>%
  mutate(
    better = direction_dprime == "Better"
  )

logit_efield_by_task <- df_logit %>%
  group_by(task) %>%
  group_modify(~ {
    fit <- glm(better ~ mean_field, data = .x, family = binomial())
    broom::tidy(fit, exponentiate = TRUE, conf.int = TRUE)
  }) %>%
  ungroup()

ggplot(df_logit, aes(x = mean_field, y = as.numeric(better), colour = direction_dprime)) +
  geom_jitter(height = 0.05, width = 0, alpha = 0.7, size = 2) +
  geom_smooth(
    aes(y = as.numeric(better)),
    method = "glm",
    method.args = list(family = binomial),
    se = TRUE,
    colour = "black"
  ) +
  facet_wrap(~ task) +
  scale_y_continuous(
    breaks = c(0, 1),
    labels = c("Worse", "Better")
  ) +
  labs(
    x = "E-Field in AG (offline TMS)",
    y = "Predicted response class",
    colour = "Observed direction",
    title = "Probability of faster response from e-field"
  ) +
  theme_bw()

# Correlation for offline AG during offline+online session ----
cor_results_nback_offline_online_AG_delta_direction <- df_nback_deltas_efields %>%
  filter(stim_type == "Offline + Online" & roi == "AG" & !is.na(direction_RT)) %>%
  droplevels() %>%
  group_by(task, direction_dprime) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$delta_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  }) %>% 
  ungroup() %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"),
    p_FDR_dprime  = p.adjust(p.value_dprime, method = "fdr"))

# plot result for d-prime
df_ag_offline_online <- df_nback_deltas_efields %>%
  filter(
    stim_type == "Offline + Online",
    roi == "AG",
    !is.na(direction_RT)
  ) %>%
  droplevels()

ann_dprime <- cor_results_nback_offline_online_AG_delta_direction %>%
  transmute(
    task,
    direction_dprime,
    label = sprintf("r = %.2f\np = %.3f", estimate_dprime, p.value_dprime),
    x = max(df_ag_offline_online$mean_field, na.rm = TRUE),
    y = case_when(
      direction_dprime == "Better" ~ 1.5,
      direction_dprime == "Worse" ~ 1
    ))

(nback_delta_direction_dprime_AG <- ggplot(
  df_ag_offline_online,
  aes(x = mean_field, y = delta_dprime,colour = direction_dprime, shape = direction_dprime)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.5) +
  geom_text(
    data = ann_dprime,
    aes(x = x, y = y, label = label, colour = direction_dprime),
    hjust = 1, vjust = 1, size = 3, show.legend = FALSE
  ) +
  facet_wrap(~ task) +
  labs(
    x = "Mean E-field (AG)",
    y = "Δ d′ (TMS – Sham)",
    colour = "d′ direction",
    shape  = "d′ direction",
    title  = "Mean E-field vs d′ delta (AG, Offline + Online)"
  ) +
  theme_bw()
)

ggsave(nback_delta_direction_dprime_AG, file = here("Plots/E-field_Correlations/nback_delta_direction_dprime_AG.png"))

# Correlation for online DLPFC during offline+online session ----
cor_results_nback_offline_online_DLPFC_delta_direction <- df_nback_deltas_efields %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC" & !is.na(direction_RT)) %>%
  droplevels() %>%
  group_by(task, direction_RT) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$delta_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  })

# Logistic regression
df_logit <- df_nback_deltas_efields %>%
  filter(
    stim_type == "Offline + Online" & 
    roi == "DLPFC" &
    direction_dprime %in% c("Better", "Worse")
  ) %>%
  mutate(
    better = direction_dprime == "Better"
  )

logit_efield_by_task <- df_logit %>%
  group_by(task) %>%
  group_modify(~ {
    fit <- glm(better ~ mean_field, data = .x, family = binomial())
    broom::tidy(fit, exponentiate = TRUE, conf.int = TRUE)
  }) %>%
  ungroup()

ggplot(df_logit, aes(x = mean_field, y = as.numeric(better), colour = direction_dprime)) +
  geom_jitter(height = 0.05, width = 0, alpha = 0.7, size = 2) +
  geom_smooth(
    aes(y = as.numeric(better)),
    method = "glm",
    method.args = list(family = binomial),
    se = TRUE,
    colour = "black"
  ) +
  facet_wrap(~ task) +
  scale_y_continuous(
    breaks = c(0, 1),
    labels = c("Worse", "Better")
  ) +
  labs(
    x = "E-Field in DLPFC (online TMS)",
    y = "Predicted response class",
    colour = "Observed direction",
    title = "Probability of faster response from e-field"
  ) +
  theme_bw()

```

### Correlations with raw delta values
```{r efields prepare df}
# Read in file with e-fields (95 percentile from 10 mm ROI around stim coordinates) and prepare df
df_efields = read.table(here::here("average_efields_sphere_10mm_percentile_95.txt"), header = T, sep = ",")
df_efields$participant <- gsub("sub-", "", df_efields$participant)

df_efields <- df_efields %>% 
  rename(stim_type = session)
df_efields$stim_type <- as.factor(df_efields$stim_type)
df_efields$stim_type <- dplyr::recode(df_efields$stim_type, 
                               "offline" = "Offline", 
                               "offline_online" = "Offline + Online")

# Prepare df
df_nback <- nback_only_correct_nback_trials %>% 
  group_by(participant, stim_type, task) %>% 
  summarise(mean_RT = mean(nback_RT),
            mean_dprime = mean(dprime))

df_nback_deltas <- df_nback %>% 
  pivot_wider(
    id_cols  = c(participant, task),
    names_from  = stim_type,
    values_from = c(mean_RT, mean_dprime)
  ) %>% 
  mutate(
    delta_RT_Offline = mean_RT_Offline - mean_RT_Sham,
    delta_RT_Offline_Online = `mean_RT_Offline + Online` - mean_RT_Sham,
    delta_dprime_Offline = mean_dprime_Offline - mean_dprime_Sham,
    delta_dprime_Offline_Online = `mean_dprime_Offline + Online` - mean_dprime_Sham
  ) %>% 
  select(participant, task, delta_RT_Offline, delta_RT_Offline_Online, delta_dprime_Offline, delta_dprime_Offline_Online) %>% 
  pivot_longer(
    cols = starts_with("delta_"),
    names_to = c(".value", "stim_type"),
    names_pattern = "(delta_(?:RT|dprime))_(.*)") %>% 
  mutate(stim_type = dplyr::recode(stim_type,
      "Offline"          = "Offline",
      "Offline_Online"   = "Offline + Online"),
      task = dplyr::recode(task, "1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual"))

df_nback_deltas <- full_join(df_nback_deltas, df_efields, relationship = "many-to-many")

# Correlation for offline AG session ----
cor_results_nback_delta_offline <- df_nback_deltas %>%
  filter(stim_type == "Offline" & participant != "07") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$delta_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  }) %>% 
  ungroup() %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"),
    p_FDR_dprime  = p.adjust(p.value_dprime, method = "fdr"))

# Correlation for offline AG during offline+online session ----
cor_results_nback_delta_offline_online_AG <- df_nback_deltas %>%
  filter(stim_type == "Offline + Online" & roi == "AG") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$delta_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  }) %>% 
  ungroup() %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"),
    p_FDR_dprime  = p.adjust(p.value_dprime, method = "fdr"))

# Correlation for online DLPFC during offline+online session ----
cor_results_nback_delta_offline_online_DLPFC <- df_nback_deltas %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC") %>%
  droplevels() %>%
  group_by(task) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$delta_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  }) %>% 
  ungroup() %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"),
    p_FDR_dprime  = p.adjust(p.value_dprime, method = "fdr"))

# Linear regression for offline + online session ----
df_nback_deltas_wide <- df_nback_deltas %>% 
  filter(stim_type == "Offline + Online") %>% 
  droplevels() %>%
  pivot_wider(names_from = roi, values_from = mean_field)

for(load in unique(df_nback_deltas_wide$task)) {
  dat <- df_nback_deltas_wide %>% filter(task == load)
  assign(
    paste0("rt_model_", load),
    lm(delta_RT ~ AG + DLPFC, data = dat)
  )
  assign(
    paste0("dprime_model_", load),
    lm(delta_dprime ~ AG + DLPFC, data = dat)
  )
}

summary(`rt_model_1-back`)
summary(`rt_model_2-back`)
summary(`rt_model_2-back dual`)

# Check for effect of is_trigger ----
df_nback <- nback_only_correct_nback_trials %>% 
  group_by(participant, stim_type, task, is_trigger) %>% 
  summarise(mean_RT = mean(nback_RT),
            mean_dprime = mean(dprime))

df_nback_deltas <- df_nback %>% 
  filter(stim_type != "Offline") %>% 
  pivot_wider(
    id_cols  = c(participant, task, is_trigger),
    names_from  = stim_type,
    values_from = c(mean_RT, mean_dprime)
  ) %>% 
  mutate(
    delta_RT_Offline_Online = `mean_RT_Offline + Online` - mean_RT_Sham,
    delta_dprime_Offline_Online = `mean_dprime_Offline + Online` - mean_dprime_Sham
  ) %>% 
  select(participant, task, is_trigger, delta_RT_Offline_Online, delta_dprime_Offline_Online) %>% 
  pivot_longer(
    cols = starts_with("delta_"),
    names_to = c(".value", "stim_type"),
    names_pattern = "(delta_(?:RT|dprime))_(.*)") %>% 
  mutate(stim_type = dplyr::recode(stim_type,
      "Offline_Online"   = "Offline + Online"),
      task = dplyr::recode(task, "1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual"))

df_nback_deltas <- full_join(df_nback_deltas, df_efields, relationship = "many-to-many")

## Correlation for online DLPFC during offline+online session ----
cor_results_nback_delta_offline_online_DLPFC_trigger <- df_nback_deltas %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC" & !is.na(delta_RT)) %>%
  droplevels() %>%
  group_by(task, is_trigger) %>%
  group_modify(~ {
    cor1 <- broom::tidy(cor.test(.x$mean_field, .x$delta_RT))
    cor2 <- broom::tidy(cor.test(.x$mean_field, .x$delta_dprime))
    tibble(
      estimate_RT = cor1$estimate,
      p.value_RT = cor1$p.value,
      estimate_dprime = cor2$estimate,
      p.value_dprime = cor2$p.value
    )
  }) %>% 
  ungroup() %>%
  mutate(p_FDR_RT = p.adjust(p.value_RT, method = "fdr"),
    p_FDR_dprime  = p.adjust(p.value_dprime, method = "fdr"))

# plot result
df_nback_offline_online_trigger <- df_nback_deltas %>%
  filter(stim_type == "Offline + Online" & roi == "DLPFC" & !is.na(delta_RT)) %>%
  droplevels()

ann_RT <- cor_results_nback_delta_offline_online_DLPFC_trigger %>%
  transmute(
    task,
    is_trigger,
    label = sprintf("r = %.2f\np = %.3f", estimate_RT, p.value_RT),
    x = max(df_nback_offline_online_trigger$mean_field, na.rm = TRUE),
    y = case_when(
      is_trigger == "True" ~ 400,
      is_trigger == "False" ~ 300,
    ))
  #filter(is_trigger == "True")

(plot_nback_delta_offline_online_DLPFC_trigger <- ggplot(df_nback_offline_online_trigger, aes(x = mean_field, y = delta_RT, color = is_trigger)) +
  geom_point(size = 2, aes(shape = is_trigger)) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 0.5) +
  geom_text(
    data = ann_RT,
    aes(x = x, y = y, label = label, colour = is_trigger),
    hjust = 1, vjust = 1, size = 3, show.legend = FALSE
  ) +
  facet_wrap(~ task) +
  labs(
    x = "Mean E-field (DLPFC)",
    y = "Δ RT N-back",
    title  = "Mean E-field vs Δ N-back RT (DLPFC, Offline + Online)"
  ) +
  theme_bw(base_size = 8.5) +
  theme(legend.position = "bottom")
)

ggsave(plot_nback_delta_offline_online_DLPFC_trigger, file = here("Plots/E-field_Correlations/plot_nback_delta_offline_online_DLPFC_trigger.png"), width = 110, height = 80, units = "mm")
```

### Correlate delta in reaction time with d-prime
```{r}
nback_only_correct_wide <- nback_only_correct_nback_trials %>%
  group_by(participant, stim_type, task) %>% 
  mutate(mean_RT = mean(nback_RT, rm.na = TRUE), mean_dprime = mean(dprime),
         task = dplyr::recode(task, "1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual")) %>% 
  select(participant, task, stim_type, mean_RT, mean_dprime) %>% 
  distinct() %>% 
  pivot_wider(
    names_from = stim_type,
    values_from = c(mean_RT, mean_dprime)
  )

nback_only_correct_wide <- nback_only_correct_wide %>%
  mutate(
    delta_RT_offline_sham = mean_RT_Offline - mean_RT_Sham,
    delta_RT_offline_online_sham = `mean_RT_Offline + Online` - mean_RT_Sham,
    delta_dprime_offline_sham = mean_dprime_Offline - mean_dprime_Sham,
    delta_dprime_offline_online_sham = `mean_dprime_Offline + Online` - mean_dprime_Sham
  ) %>% 
  rename(mean_RT_Offline_Online  = `mean_RT_Offline + Online`,
    mean_dprime_Offline_Online = `mean_dprime_Offline + Online`)

cor.test(nback_only_correct_wide$delta_RT_offline_sham, nback_only_correct_wide$delta_dprime_offline_sham)
cor.test(nback_only_correct_wide$delta_RT_offline_online_sham, nback_only_correct_wide$delta_dprime_offline_online_sham)

nback_only_correct_wide %>% ggscatter(x = "delta_RT_offline_online_sham", y = "delta_dprime_offline_online_sham", facet.by = "task", add = "reg.line", conf.int = T, cor.coef = T, size = 1, alpha = 1)

nback_only_correct_wide %>% ggscatter(x = "delta_RT_offline_sham", y = "delta_dprime_offline_sham", facet.by = "task", add = "reg.line", conf.int = T, cor.coef = T, size = 1, alpha = 1) #label = "participant"

# Explore effect of online trigger (only offline+online and Sham session) ----
nback_only_correct_wide <- nback_only_correct_nback_trials %>%
  filter(stim_type != "Offline") %>% 
  group_by(participant, stim_type, task, is_trigger) %>% 
  mutate(mean_RT = mean(nback_RT, rm.na = TRUE), mean_dprime = mean(dprime),
         task = dplyr::recode(task, "1back_single_main_click" = "1-back", "2back_single_main_click" = "2-back", "2back_dual_main_click" = "2-back dual")) %>% 
  select(participant, task, stim_type, mean_RT, mean_dprime, is_trigger) %>% 
  distinct() %>% 
  pivot_wider(
    names_from = stim_type,
    values_from = c(mean_RT, mean_dprime)
  )

nback_only_correct_wide <- nback_only_correct_wide %>%
  mutate(
    delta_RT_offline_online_sham = `mean_RT_Offline + Online` - mean_RT_Sham,
    delta_dprime_offline_online_sham = `mean_dprime_Offline + Online` - mean_dprime_Sham
  ) %>% 
  rename(mean_RT_Offline_Online  = `mean_RT_Offline + Online`,
    mean_dprime_Offline_Online = `mean_dprime_Offline + Online`)

cor.test(nback_only_correct_wide$delta_RT_offline_online_sham, nback_only_correct_wide$delta_dprime_offline_online_sham)

corr_Acc_RT_nback_offline_online <- nback_only_correct_wide %>% ggscatter(x = "delta_RT_offline_online_sham", y = "delta_dprime_offline_online_sham", facet.by = c("task", "is_trigger"), add = "reg.line", conf.int = T, cor.coef = T, size = 1, alpha = 1)

ggsave(corr_Acc_RT_nback_offline_online, file = here("Plots/corr_Acc_RT_nback_offline_online.png"), width = 110, height = 100, units = "mm")
```

## EFFECT OF BASELINE PERFORMANCE
How much is reaction to TMS moderated by baseline performance during sham?
```{r}
# RT ----
sham_baseline <- nback_only_correct_nback_trials %>% 
  filter(stim_type == "Sham") %>% 
  group_by(participant, task) %>% 
  summarise(sham_RT = median(log(nback_RT), na.rm = TRUE), .groups = "drop_last")

nback_only_correct_nback_trials <- nback_only_correct_nback_trials %>% 
  left_join(sham_baseline) %>%
  ungroup() %>%
  group_by(task) %>% 
  mutate(sham_RT_centered = sham_RT - mean(sham_RT))

lmm_nback_shamBaseline <- lmerTest::lmer(log(nback_RT) ~
          stim_type +
          task +
          scale(sham_RT, scale = FALSE) +
          stim_type:task +
          stim_type:scale(sham_RT, scale = FALSE) +
          stim_type:task:scale(sham_RT, scale = FALSE) +
          (1 + stim_type + task| participant),
        data = nback_only_correct_nback_trials,
        REML = FALSE,
        control = lmerControl(optimizer = "bobyqa"))

summary(lmm_nback_shamBaseline)
anova(lmm_nback_shamBaseline)

emm <- predict_response(lmm_nback_shamBaseline, c("sham_RT", "stim_type[Offline, Offline + Online]"), margin = "marginalmeans")
plot(emm)

slopes_stimType <- emtrends(
  lmm_nback_shamBaseline,
  specs = ~ stim_type,
  var = "sham_RT",
  type = "response"
)

summary(slopes_stimType)
pairs(slopes_stimType, adjust = "holm")

# Plot ----
pred_nback_shamBaseline <- predict_response(lmm_nback_shamBaseline, c("sham_RT", "stim_type"), margin = "marginalmeans")
participant_points <- collapse_by_group(pred_nback_shamBaseline, lmm_nback_shamBaseline, "participant")
participant_points <- participant_points %>% 
  group_by(participant, stim_type) %>% 
  summarise(sham_RT = mean(sham_RT),
            nback_RT = mean(nback_RT))

(RT_nback_shamBaseline_lmm <- ggplot(subset(pred_nback_shamBaseline, group != "Sham"), aes(x = exp(x), y = predicted, colour = group, fill = group)) +
  geom_jitter2(subset(participant_points, stim_type != "Sham"), mapping = aes(x = exp(sham_RT), y = nback_RT, color = stim_type), inherit.aes = FALSE, alpha = 0.35, size = 2.2, position = position_jitter(width = 1)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, colour = NA) +
  geom_line(linewidth = .7) +
  ylab("Predicted reaction time in ms") +
  xlab("Baseline reaction time\nin ms") +
  scale_y_continuous(breaks = pretty_breaks(3)) +
  scale_x_continuous(breaks = pretty_breaks(2)) +
  #coord_cartesian(ylim = c(230, 1530)) +
  scale_color_manual(values = cols_dualContrast) +
  scale_fill_manual(values = cols_dualContrast) +
  theme_bw(base_size = 8)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 9),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8.),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 8))
)
ggsave(RT_nback_shamBaseline_lmm, file = here(paste0("Plots/RT_nback_shamBaseline_lmm_", today, ".pdf")), width = 35, height = 83, units = "mm")

# Plot change in ratio/% for low, average, and high performers ----
base_vals <- nback_only_correct_nback_trials %>%
  ungroup() %>% 
  reframe(
    sham_RT = c(
      quantile(sham_RT, .25, na.rm = TRUE),
      mean(sham_RT, na.rm = TRUE),
      quantile(sham_RT, .75, na.rm = TRUE)
    ),
    base_label = c("Fast", "Average", "Slow"),
  )
newdat <- tidyr::crossing(
  base_vals,
  stim_type = levels(nback_only_correct_nback_trials$stim_type),
  task = levels(nback_only_correct_nback_trials$task)
)

cmp_all <- comparisons(
  lmm_nback_shamBaseline,
  newdata = newdat,
  variables = list(stim_type = "reference"),
  transform = exp,
  re.form = NA,
  comparison = "difference"
)

cmp_all <- cmp_all %>%
  group_by(base_label, contrast) %>%
  summarise(
    estimate = mean(estimate, na.rm = TRUE),
    conf.low = mean(conf.low, na.rm = TRUE),
    conf.high = mean(conf.high, na.rm = TRUE),
    p.value = mean(p.value),
    .groups = "drop"
  )

cmp_all$base_label <- factor(cmp_all$base_label, levels = c("Slow", "Average", "Fast"))

(RT_nback_shamBaseline_comparisons <- ggplot(cmp_all, aes(y = (estimate-1)*100, x = base_label, group = contrast)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey45") +
  geom_line(linewidth = 0.65, aes(colour = contrast), linetype = "dashed") +
  geom_point(size = 3, aes(colour = contrast, fill = contrast), shape = 23) +
  geom_errorbar(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, colour = contrast), width = 0.15, linewidth = 1) +
  #scale_x_continuous(breaks = rev(base_vals_long$sham_RT), labels = rev(base_vals_long$base_label)) +
  facet_grid(~ contrast, scales = "free") +
  scale_color_manual(values = cols_dualContrast) +
  scale_fill_manual(values = cols_dualContrast) +
  ylab("% change in reaction time vs Sham") +
  xlab("Baseline performance") +
  theme_bw(base_size = 8)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 9),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 8, angle = 45, vjust = 1, hjust = 1))
)
ggsave(RT_nback_shamBaseline_comparisons, file = here(paste0("Plots/RT_nback_shamBaseline_comparisons_", today, ".pdf")), width = 55, height = 85, units = "mm")

(plot_RT_nback_baseline <- ggarrange(RT_nback_shamBaseline_lmm, RT_nback_shamBaseline_comparisons, nrow = 1, widths = c(0.8,1)))
ggsave(plot_RT_nback_baseline, file = here("Plots/RT_nback_baseline.pdf"), width = 95, height = 70, units = "mm")

cmp_all$base_label <- factor(cmp_all$base_label, levels = c("Low", "Average", "High"))

(RT_reading_shamBaseline_comparisons <- ggplot(cmp_all, aes(y = (estimate-1)*100, x = base_label, group = contrast)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey45") +
  geom_line(linewidth = 0.65, aes(colour = stim_task)) +
  geom_point(size = 3, aes(colour = stim_task, fill = stim_task), shape = 23) +
  geom_errorbar(aes(ymin = (conf.low-1)*100, ymax = (conf.high-1)*100, colour = stim_task), width = 0.15, linewidth = 1) +
  #scale_x_continuous(breaks = base_vals$sham_RT, labels = base_vals$base_label) +
  #scale_x_reverse() +
  facet_grid(contrast ~ task, scales = "free", labeller = labeller(task = c("Reading" = "Reading", "2-back dual" = "Dual task"))) +
  scale_color_manual(values = cols_reading[c(2,3,5,6)]) +
  scale_fill_manual(values = cols_reading[c(2,3,5,6)]) +
  ylab("% change in reading time vs Sham") +
  xlab("Baseline performance") +
  theme_bw(base_size = 8)+
  theme(legend.position = "none",
       text = element_text(family = "Helvetica"),
       panel.grid.major = element_blank(),
       panel.grid.minor = element_blank(),
       strip.background = element_blank(),
       strip.text = element_text(size = 9),
       axis.line = element_line(),
       axis.text.y = element_text(size = 8),
       #axis.title.x = element_text(size = 10),
       axis.text.x = element_text(size = 8, angle = 45, hjust = 1, vjust = 1))
)
ggsave(RT_reading_shamBaseline_comparisons, file = here(paste0("Plots/RT_reading_shamBaseline_comparisons_", today, ".pdf")), width = 60, height = 85, units = "mm")
```
