---
title: "EXNAT_4_TMS Preprocessing"
author: "Sandra Martin"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    code-fold: true
editor_options:
  chunk_output_type: console
---

```{r file setup, echo = FALSE}
rm(list = ls()) # clear environment
knitr::opts_chunk$set() # set default options for all code blocks in this document
options(scipen = 999) # don't use scientific notation for very large or small numbers
n.cores <- max(1, parallel::detectCores() %/% 2, na.rm = T) # Use half of the available cores
```

# Load packages
```{r packages, echo = FALSE, message = FALSE, warning = TRUE}
# Create a list with needed libraries
pkgs <- c("here", # for working with relative paths
          "ggplot2", # for plots
          "patchwork", # also for plots
          "dplyr", # for replacing multiple values in vector with different values
          "tidyverse", # for aggregating
          "psycho", # for computing d-prime values
          "devtools") # for getting packages from github


# Load each listed library, check if it's already installed
# and install if necessary
for (pkg in pkgs){
  if(!require(pkg, character.only = TRUE)){
    install.packages(pkg)
    library(pkg, character.only = TRUE)
  }
}

# install package with lists of stop words from github
devtools::install_github("quanteda/stopwords")
library(stopwords)

today <- Sys.Date()
today <- format(today, format="%y%m%d")
```

# Load d-prime function from different R script:
```{r source d-prime function, echo = FALSE}
source(here::here("get_dprime.R")) # get script

# creating a function for std.error
std.error <- function(x, na.rm = TRUE){sd(x, na.rm = TRUE)/sqrt(length(x[!is.na(x)]))}
```

# Set path to datasets
```{r path setup}
path_data_folder <- here::here("Raw_data/")
```

# Read in data & do preprocessing on participant-level
In this chunk, we read in every dataset individually, compute reading times, reading speed, d-primes, comprehension question performance, and so on, add a few information on the words we used (e.g. surprisal scores on our 4 time scales, word frequencies, word lengths, punctuation,...), 
```{r Read in data, message=FALSE}
# Get list of all .csv files in the data folder
file_list <- list.files(path = path_data_folder, pattern = "^sub-.*\\.csv$")

# Placeholders df for demographics, questions & text data
df_all_data_raw     <- data.frame()
df_comprehension_Qs <- data.frame()

# Loop files in my file list aka directory
for (i in 1:length(file_list)) {

  # PREPARE FILE FOR PREPROCESSING
  # Read in current file
  subj_df <- read.csv(paste(path_data_folder, file_list[i],sep = ""), sep = ",")

  # If the df is separated by a semicolon instead of a comma, we only get
  # one messed-up column. In this case, use semicolon as separator for csv:
  if (ncol(subj_df) == 1) {
   subj_df <- read.csv(paste(path_data_folder, file_list[i],sep = ""), sep = ";")
  }
  
  id <- subj_df$participant[1]
  
  # print message
  message(paste(i, " - Reading in file ", file_list[i], ", participant ID: ", id, sep = ""))

  # add column with info on whether participant should be excluded
  excl <- FALSE
  
  # rename block_kind column
  subj_df <- subj_df %>% 
    rename(nback_level = n.back_level)

  # GET RAW TEXT & N-BACK DATA

  # get words & information on the text from data
  subj_df <- subj_df[, c("colour", "global_onset_time", "target", "button_pressed", "nback_response", "nback_RT", "RT", "text_nr", "trial_nr", "block_nr_exp", "block_name", "nback_level", "word", "nontarget_triggers_sent_this_condition", "target_triggers_sent_this_condition", "total_triggers_sent_this_condition", "minimum_triggers_this_condition", "maximum_triggers_this_block", "trigger_time", "question", "chosen_ans", "ans_correct", "participant", "session", "date")]
  
  # remove weird empty rows in df, most likely written by Psychopy
  subj_df <- subset(subj_df, !is.na(global_onset_time))

  
  ### ADD NUMBERED BLOCK NAMES ####

  # # We have each main block twice, but I would like to exclude outliers by block and not by condition.
  # # Reason: Reading times in second block might be slightly different than in first block, so don't mix them up.
  # 
  # Separate out sub 7, session 2 because there are two logfiles and we want to fix the block order so they are numbered sequentially
  if (file_list[i] == "sub-07_ses-02_2025-06-04_10h57.19.947.csv"){
    change_df <- subj_df %>%
      filter(!is.na(trial_nr)) %>%
      group_by(block_nr_exp, block_name) %>%
      count() %>%
      ungroup() %>%
      group_by(block_name) %>%
      mutate(Index = row_number() + 1) %>% 
      mutate(block_names_numbered = paste(block_name, Index, sep = "_")) %>%
      ungroup() %>% 
      mutate(block_nr_exp_new = row_number() + 4) %>% 
      select(-c(Index, n))
      
      subj_df <- full_join(subj_df, change_df)
      
      subj_df <- subj_df %>% 
        mutate(block_nr_exp = block_nr_exp_new)
  } else {
    change_df <- subj_df %>%
      filter(!is.na(trial_nr)) %>%
      group_by(block_nr_exp, block_name) %>%
      count() %>%
      ungroup() %>%
      group_by(block_name) %>%
      mutate(Index=1:n()) %>%
      mutate(block_names_numbered = paste(block_name, Index, sep = "_")) %>%
      select(-c(Index, n))
      
      subj_df <- full_join(subj_df, change_df)
  }
  
  #subj_df <- full_join(subj_df, change_df)

  # GET ADDITIONAL INFORMATION ON THE TEXTS:

  ### PUNCTUATION ####

  # Edit the texts a bit. Currently, we have words & punctuation
  # mixed up. Would be nice if we had one word column
  # and some others with info on punctuation.

  punctuation <- c(rep("", times = length(subj_df$participant)))

  # get all .
  punctuation[grep("[.]", subj_df$word)] <- "point"
  # get all ?
  punctuation[grep("[?]", subj_df$word)] <- "question_mark"
  # get all !
  punctuation[grep("[!]", subj_df$word)] <- "exclamation_mark"
  # get all ,
  punctuation[grep("[,]", subj_df$word)] <- "comma"
  # get all ;
  punctuation[grep("[;]", subj_df$word)] <- "semicolon"
  # get all :
  punctuation[grep("[:]", subj_df$word)] <- "colon"

  # get all "
  # This is tricky for various reasons:

  # 1. there could be quotes directly after or
  # before a point for example

  # Idea: Separate column for quotes
  quotes <- c(rep("", times = length(subj_df$participant)))

  # 2. I want to differentiate between opening and closing quotes,
  # but they look the same.

  # Idea: make them all "opening quotes" and change every second one to
  # "closing_quote". This should do the trick.
  quotes[grep("\"", subj_df$word)] <- "opening_quote"
  opening <- TRUE

  # loop list of quotes
  for (x in 1:length(quotes)){
    # get current value in vector "quotes" & current word
    curr_val  <- quotes[x]
    curr_word <- subj_df$word[x]

    if (curr_val == "opening_quote" & # if the current value is not empty
        opening == TRUE & # and we set "opening" to TRUE
        grepl("\"[A-Za-z0-9]+\"", curr_word) == FALSE){ # and there are not 2 quotes around the word

      # leave it as is, next quote is the closing one
      opening <- FALSE

      # if we have a quote, but it has to be a closing one, change it accordingly
    } else if (curr_val == "opening_quote" &
               opening == FALSE &
               grepl("\"[A-Za-z0-9]+\"", curr_word) == FALSE){
      # change value to closing quote
      quotes[x] <- "closing_quote"
      # next quote is the opening one
      opening <- TRUE
      # if it's a quote around a single word, mark as "both"
    } else if (curr_val == "opening_quote" &
               grepl("\"[A-Za-z0-9]+\"", curr_word) == TRUE){
      # change value to both
      quotes[x] <- "both"
    }
  }

  # remove all punctuation
  word_single <- gsub('[[:punct:] ]+',' ', subj_df$word)
  # "trim" away spaces before and after words
  word_single <- trimws(word_single, which = c("left"))
  word_single <- trimws(word_single, which = c("right"))
  # put dashes into spaces between words (words like "ice-cream" for example)
  word_single <- gsub(" ", "-", word_single, fixed = TRUE)

  # get word length for single words
  word_length_single <- nchar(word_single)


  ### N-BACK RESPONSES ####

  # check if we had an n-back reaction while the word was shown
  # create vector with only FALSEs
  reaction <- c(rep(FALSE, times = length(subj_df$participant)))
  # check where in subj_df we have responses (hit or false alarm) and change value in reaction vector to TRUE at that index
  reaction[which(subj_df$nback_response == "hit" | subj_df$nback_response == "false alarm")] <- TRUE

  # APPEND NEW COLUMNS
  # append punctuation and quotes column, column with words without punctuation
  # column with length of each the single words and reaction column as
  # additional columns to subj_df:
  subj_df <- data.frame(cbind(subj_df, word_single, punctuation,
                              quotes, word_length_single, reaction))

  ### STOP WORDS ####

  # Now also get previous reaction and stop words.
  # First, append empty columns to df:
  subj_df[, c("previous_reaction", "previous_duration", "stop_word")] <- ""

  # get list of German stop_words
  stop_words <- stopwords("de", source = "snowball")
  # snowball = stopwords list based on the Snowball stemmer's word lists.
  # --> https://snowballstem.org/texts/introduction.html

  # now loop rows and gradually fill in the empty columns.
  for (idx in 1:length(subj_df$participant)){
    # if it's the first trial of a new block, go to next iteration
    # because in this case we don't have previous data.
    # Also skip the following part if it's a block without text.
    if (subj_df$trial_nr[idx] > 1 && !is.na(subj_df$trial_nr[idx])){
      # fill in the missing data by getting the values from the previous trial:
      subj_df$previous_duration[idx]    <- subj_df$RT[idx-1]
      subj_df$previous_reaction[idx]    <- subj_df$reaction[idx-1]
    }

    if (subj_df$word_single[idx] %in% stop_words){
      # check if current word is a stop word or not
      subj_df$stop_word[idx] <- TRUE 
      }
    else {
      subj_df$stop_word[idx] <- FALSE
    }
  }
  
  ### WORD FREQUENCIES, SURPRISAL & ENTROPY SCORES ####

  # Include word frequencies & surprisal scores for each word

  # append "empty" word frequency & surprisal score columns to df
  # to do so, create a vector of column names
  col_names <- c("word_frequency", "zipf_frequency", "surprisal_2", "entropy_2")
  # then add "empty" columns to data frame subj_df
  subj_df[, col_names] <- 0

  # get word frequency & surprisal scores for each word
  # load word freq df
  word_freqs_df = read.csv(here::here("word_frequencies/EXNAT_4_TMS_word_freqs.csv"), sep = ";", header = TRUE)
  # Explanation: We compute the word frequencies using another
  #              script which is called "calculate_word_frequencies.py".
  #              You can find it in the Analysis folder.
  #              --> word frequencies were taken from this python package:
  #              Speer, R., Chin, J., Lin, A., Jewett, S., & Nathan, L. (2018, October 3).
  #              LuminosoInsight/wordfreq: v3.1.1 Zenodo. https://doi.org/10.5281/zenodo.1443582


  # Load surprisal scores
  surprisal_df = read.csv(here::here("surprisal_scores/vanilla_2words_surprisal_entropy_48Texts_11_2025.csv"), sep = ",", header = TRUE)

  # Explanation: I computed the scores in Python using a German GPT-2 model. For each text you can select a context chunk of x words (e.g. 5 words)
  #              and predict the next word. For each possible continuation of your context, you get probabilities.
  #              If you get the probability for the actual word and compute the negative log of it, you have the surprisal score
  #              for your word on time scale x (e.g. 5 words = TS 5). The time scales are all highly correlated, which might be due to the fact that each
  #              time scale also includes context information from all lower timescales, so it's like a Russian doll situation.
  #              To deal with this problem, we masked all words that were already processed in lower time scales,
  #              so each time scale only uses the "new" parts of the input chunk.


  # loop individual texts
  for (curr_text_nr in unique(subj_df$text_nr)){

    # in some blocks we don't have texts, so skip those
    # CAVE: currently also skipping text 10 because I still need to calculate values for this text
    if (curr_text_nr == ""){
      next
      # if it's a text block, though, assign word frequencies from csv
    } else {
      #print(curr_text_nr) # uncomment this if you'd like to show the texts each participant read

      # get word frequencies for current text nr
      curr_word_freqs <- subset(word_freqs_df, text_nr == curr_text_nr)
      
      # find out where in the subj_df text the current text nr is located
      curr_row <- which(subj_df$text_nr == curr_text_nr & subj_df$question == "")
      
      # find out where in the subj_df text the text is located and add the word frequencies there
      subj_df[curr_row, c("word_frequency", "zipf_frequency")]  <- curr_word_freqs[c("frequency", "zipf_frequency")]

      # Do the same for the surprisal scores.
      curr_surprisals <- subset(surprisal_df, text_nr == curr_text_nr)

      # find out where in the subj_df text the current text nr is located
      curr_row <- which(subj_df$text_nr == curr_text_nr & subj_df$question == "")

      # add the surprisal scores (untransformed & orthogonalized scores) there
      subj_df[curr_row, c("surprisal_2", "entropy_2")]  <- curr_surprisals[c("surprisal_2_words_context", "entropy_2_words_context")]
      
    }# END if
  }# END loop texts

  
  ### GET SURPRISAL SCORES OF PREVIOUS WORD ####
  # --> basically do the same again as before, but add surprisal scores for current for to row of next word.

  # append "empty" word frequency & surprisal score columns to df
  # to do so, create a vector of column names
  col_names <- c("zipf_frequency_previous_word", "previous_surprisal_2", "previous_entropy_2")
  # then add "empty" columns to data frame subj_df
  subj_df[, col_names] <- 0

  # loop individual texts
  for (curr_text_nr in unique(subj_df$text_nr)){

    # in some blocks we don't have texts, so skip those
    if (curr_text_nr == ""){
      next
      # if it's a text block, though, assign word frequencies from csv
    } else {
      print(curr_text_nr) # uncomment this if you'd like to show the texts each participant read

      # get word frequencies for current text nr
      curr_word_freqs <- subset(word_freqs_df, text_nr == curr_text_nr)$zipf_frequency

      # now this is where we do it differently than before: Remove the last value and add 1 NA
      # at idx = 1 of the vector, so the values are moved by 1 position.
      curr_word_freqs <- c(NA, curr_word_freqs[-length(curr_word_freqs)])

      # find out where in the subj_df text the text is located and add the word frequencies there
      subj_df[which(subj_df$text_nr == curr_text_nr & subj_df$question == ""),]$zipf_frequency_previous_word <- curr_word_freqs

      # Do the same for the surprisal scores:
      curr_surprisals <- subset(surprisal_df, text_nr == curr_text_nr)[ , c("surprisal_2_words_context", "entropy_2_words_context")]

      # add 1 NA to the start of the vectors, remove last value in each
      curr_surprisals <- rbind(c(NA, NA), curr_surprisals[-nrow(curr_surprisals), ])

      # find out where in the subj_df text the current text nr is located
      curr_row <- which(subj_df$text_nr == curr_text_nr & subj_df$question == "")

      # add the surprisal scores (untransformed & orthogonalized scores) there
      subj_df[curr_row, c("previous_surprisal_2", "previous_entropy_2")] <- curr_surprisals

    }# END if
  }# END loop texts
  
  ### CHANGE ORDER OF DATAFRAME ####
  # Move around the columns a bit:
  col_order <- c("participant", "session", "nback_level", "block_nr_exp", "block_name", "block_names_numbered",
                 "trial_nr", "text_nr", "word", "global_onset_time", "RT",
                 "colour", "target", "button_pressed", "nback_response", "nback_RT", "reaction",
                 "word_single", "word_length_single", "word_frequency", "zipf_frequency",
                 "surprisal_2", "entropy_2", "previous_surprisal_2", "previous_entropy_2", "zipf_frequency_previous_word", 
                 "previous_duration", "previous_reaction",
                 "nontarget_triggers_sent_this_condition",
                 "target_triggers_sent_this_condition", "total_triggers_sent_this_condition", "minimum_triggers_this_condition", "maximum_triggers_this_block", "trigger_time", "question", "chosen_ans", "ans_correct", "stop_word", "punctuation", "quotes", "date")

  subj_df <- subj_df[, col_order]
  
  ### GET PERFORMANCE MEASURES ####

  #### COMPREHENSION QUESTION PERFORMANCE ####
  
  # get question data:
  Q_df <- subset(subj_df, question != "")[,c("question", "chosen_ans", "ans_correct", "text_nr", "block_name", "participant")]

  Q_df$ans_correct <- as.logical(Q_df$ans_correct)
  
  # calculate accuracy per text
  Q_df <- Q_df %>% 
   group_by(text_nr) %>% 
    mutate(question_acc = sum(ans_correct[ans_correct == TRUE])/3)
  
  Q_subset <- Q_df %>% 
    select(c(text_nr, question_acc)) %>% 
    distinct

  # append Q_subset to bigger df for all participants
  df_comprehension_Qs <- as.data.frame(rbind(df_comprehension_Qs, Q_df))
  
  # append overall accuracy per text to subject df
  subj_df <- full_join(subj_df, Q_subset) %>% 
    select(-c(question, chosen_ans, ans_correct)) %>% 
    filter(!is.na(RT))


  ### N-BACK PERFORMANCE ####

  # set all durations in n-back trials without response to NA
  subj_df[which(subj_df$reaction == F), ]$nback_RT <- NA

  # create vector of n-back blocks in experiment
  nback_block_names <- subj_df %>% 
    filter(str_detect(nback_level, "^1") | str_detect(nback_level, "^2")) %>% 
    distinct(block_nr_exp) %>% 
    pull(block_nr_exp)

  # append empty d-prime column to df:
  subj_df$dprime <- c(rep(NA, times = length(subj_df$word)))

  # loop block names:
  for (nback_block in nback_block_names){

    # get data for current block
    curr_block <- subset(subj_df, block_nr_exp == nback_block)

    # remove trials where the RT was way too fast
    # (= participant reacted by accident)
    curr_block <- subset(curr_block, (nback_RT >= 100 | is.na(nback_RT)))

    # if there are still some trials left (let's say at least 5), compute d-prime
    if (length(curr_block$participant) > 5){
        # compute d-prime & add to bigger df
        d_prime <- get_dprime(curr_block$nback_response)
        subj_df$dprime[subj_df$block_nr_exp == nback_block] <- d_prime
    } # END if loop - check if there are still enough trials left
  }# END loop - compute d-primes
  
    ### MARK PARTICIPANTS/BLOCKS FOR EXCLUSION:

  # append "empty" exclude trial / exclude participant columns to df
  subj_df$excl_trial       <- FALSE

  ### EXCLUDE SINGLE BLOCKS BASED ON COMPREHENSION QUESTION PERFORMANCE: ####
  
  # Idea: only exclude on block level, don't exclude full datasets because they messed up in 1 condition or so.
  # To identify these blocks, we look for a question accuracy of 0

  #subj_df$excl_trial[subj_df$question_acc == 0] <- TRUE
  #message(paste("excluded", length(subj_df[which(subj_df$question_acc == 0), "excl_trial"]), "trials because accuracy was 0%", sep = " "))
  
  ### EXCLUDE SINGLE BLOCKS BASED ON N-BACK TASK PERFORMANCE: ####
  
  # --> exclude all blocks with d-primes == 0.
  
 # message(paste("excluded", length(subj_df[which(subj_df$dprime == 0), "excl_trial"]), "trials because d-prime was 0", sep = " "))
  #subj_df[which(subj_df$dprime == 0), "excl_trial"] <- TRUE

  # append subj_df chunk to df_text_data where we collect the data of all participants we want to keep
  df_all_data_raw <- as.data.frame(rbind(df_all_data_raw, subj_df))

  message("------------------------")

}# END READ IN DATASETS

# exclude all trials that we marked for exclusion:
#df_all_data <- subset(df_all_data, excl_trial == FALSE)


# clean up!
#rm(list=ls()[! ls() %in% c("df_all_data", "df_comprehension_Qs", 
#                           "apatheme", "cols_reading", 
#                           "palet_dprimes", "palet_dprimes_lines", 
#                           "palet_lab_online", "palet9", "today")])

saveRDS(df_comprehension_Qs, file = here::here("RData/df_comprehension_questions.rds"))
```

# Add info on stimulation type and session
```{r add demographic info}
df_participants_info <- read.table(here::here("EXNAT_4_TMS_participants.txt"), header = TRUE, sep = "\t")
df_all_data_raw$participant <- str_pad(df_all_data_raw$participant, 2, pad = "0")
df_participants_info$ID <- gsub("sub-","", df_participants_info$ID)
df_participants_info <- df_participants_info %>% 
  rename(participant = ID)

df_all_data_raw <- full_join(df_all_data_raw, df_participants_info)
# create a new column with stim type
df_all_data_raw <- df_all_data_raw %>% 
  mutate(stim_type = case_when(session == 1 & (Stim_Order == "offline,offline_online,sham" | Stim_Order == "offline,sham,offline_online") ~ "offline",
                               session == 1 & (Stim_Order == "sham,offline_online,offline" | Stim_Order == "sham,offline,offline_online") ~ "sham",
                               session == 1 & (Stim_Order == "offline_online,sham,offline" | Stim_Order == "offline_online,offline,sham") ~ "offline_online",
                               session == 2 & (Stim_Order == "offline,offline_online,sham" | Stim_Order == "sham,offline_online,offline") ~ "offline_online",
                               session == 2 & (Stim_Order == "offline_online,offline,sham" | Stim_Order == "sham,offline,offline_online") ~ "offline",
                               session == 2 & (Stim_Order == "offline_online,sham,offline" | Stim_Order == "offline,sham,offline_online") ~ "sham",
                               session == 3 & (Stim_Order == "offline,offline_online,sham" | Stim_Order == "offline_online,offline,sham") ~ "sham",
                               session == 3 & (Stim_Order == "sham,offline_online,offline" | Stim_Order == "offline_online,sham,offline") ~ "offline",
                               session == 3 & (Stim_Order == "offline,sham,offline_online" | Stim_Order == "sham,offline,offline_online") ~ "offline_online",
                             TRUE ~ NA))

# calculate mean d-prime from 1-back and 2-back single task main blocks from the sham session as a working memory measure for each participant
df_all_data_raw <- df_all_data_raw %>%
  group_by(participant) %>%
  mutate(mean_dprime_singletasks = mean(c(
        unique(dprime[stim_type == "sham" & block_name == "1back_single_main_click"]),
        unique(dprime[stim_type == "sham" & block_name == "2back_single_main_click"]))))

# reorder df
df_all_data_raw <- df_all_data_raw[,c(1,42,43,2,74,46:50,3:41,44,45,51:73,75)]

# plot some descriptives on number of TMS trains given ----
df_all_data_raw_subset <- subset(df_all_data_raw, stim_type != "offline")

df_all_data_raw_subset$block_name <- factor(df_all_data_raw_subset$block_name, levels = c("Reading_Baseline_main_click", "2back_dual_main_click", "1back_single_main_click", "2back_single_main_click"))

df_subset <- df_all_data_raw %>%
  group_by(participant, stim_type, block_name, target) %>% 
  summarize(max_trains = max(total_triggers_sent_this_condition))

label_map <- c(
  "Reading_Baseline_main_click" = "Reading",
  "2back_dual_main_click" = "Dual task",
  "1back_single_main_click" = "1-back",
  "2back_single_main_click" = "2-back"
)

df_subset$block_name_short <- label_map[df_subset$block_name]

(plot_max_trains <- ggplot(df_subset, aes(x = block_name_short, y = max_trains)) +
    #geom_violinhalf(position = position_nudge(x = 0.05), width = 1.2) +
    geom_boxplot(width = 0.4) +
    stat_summary(fun = mean, geom = "text", aes(label = sprintf("M=%.1f", after_stat(y))), hjust = 1.4, size = 2.5, color = "blue", fontface = "bold") +
    stat_summary(fun = min, geom = "text", aes(label = sprintf("min=%.0f", after_stat(y))), vjust = 1.5, size = 2, color = "grey30") +
    stat_summary(fun = max, geom = "text", aes(label = sprintf("max=%.0f", after_stat(y))), vjust = -0.5, size = 2, color = "grey30") +
    scale_x_discrete(expand = expansion(add = c(0.8, 0.5))) +  
    facet_grid(~stim_type) +
    theme_bw() +
    theme(#legend.position = "none",
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         strip.background = element_blank(),
         plot.title = element_text(size = 10),
         axis.line = element_line(),
         axis.text.y = element_text(size = 8),
         axis.title.x = element_blank(),
         axis.text.x = element_text(angle = 45, hjust = 1),
         axis.text.x.bottom = element_text(size = 8))
)

(plot_max_trains_trigger <- ggplot(df_subset[df_subset$block_name != "Reading_Baseline_main_click",], aes(x = block_name_short, y = max_trains, color = target, fill = target)) +
    #geom_violinhalf(position = position_dodge(width = 0.6), width = 1.2) +
    geom_boxplot(position = position_dodge(width = 0.9), width = 0.4, fill = NA) +
    stat_summary(fun = mean, geom = "text", aes(label = sprintf("M=%.1f", after_stat(y))), vjust = -0.5, size = 2.5, color = "blue", fontface = "bold", position = position_dodge(width = 0.9),) +
    stat_summary(fun = min, geom = "text", aes(label = sprintf("min=%.0f", after_stat(y))), vjust = 1.5, size = 2, color = "grey30", position = position_dodge(width = 0.9),) +
    stat_summary(fun = max, geom = "text", aes(label = sprintf("max=%.0f", after_stat(y))), vjust = -0.5, size = 2, color = "grey30", position = position_dodge(width = 0.9),) +
    facet_grid(~stim_type) +
    theme_bw() +
    theme(legend.position = "bottom",
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         strip.background = element_blank(),
         plot.title = element_text(size = 10),
         axis.line = element_line(),
         axis.text.y = element_text(size = 8),
         axis.title.x = element_blank(),
         axis.text.x = element_text(angle = 45, hjust = 1),
         axis.text.x.bottom = element_text(size = 8))
)

(plot_online_TMS_trains <- plot_max_trains / plot_max_trains_trigger)
ggsave(plot_online_TMS_trains, file = here::here("Plots/plot_online_TMS_trains.png"), width = 155, height = 200, units = "mm")

m_TMS_trains <- lmerTest::lmer(max_trains ~
                                    stim_type +
                                 block_name +
                                    (1|participant),
                                  data = df_subset, 
                                  REML = TRUE)
summary(m_TMS_trains)
```

# Neuropsychological tests
```{r}
# Check for possible sum score for neuropsychological tests and add to large df
NP_df <- df_participants_info %>% 
  select(participant, TMT_A, TMT_B, DSST, RS)

dprime_df <- df_all_data_raw %>% 
  select(participant, mean_dprime_singletasks) %>% 
  distinct()

NP_df <- full_join(NP_df, dprime_df)

# Calculate correlation matrix
cor_mat <- cor(NP_df[,2:6])

# Visualize correlation heatmap
library(reshape2)
melted_cor <- melt(cor_mat)
ggplot(melted_cor, aes(Var1, Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2()

# Calculate Cronbach's alpha
library(psych)
NP_df$TMT_A_inv <- NP_df$TMT_A*(-1)
NP_df$TMT_B_inv <- NP_df$TMT_B*(-1)
psych::alpha(NP_df[,c(4,5,7,8)])

# --> we can summarize TMT and DSST but should keep RS separate
# standardize selected columns
scores_z <- scale(NP_df[, c("DSST", "TMT_A_inv", "TMT_B_inv")])
NP_df$executive_sum <- rowMeans(scores_z, na.rm = TRUE)

NP_df <- NP_df %>% 
  select(participant, executive_sum)

# Merge with large df
df_all_data_raw <- full_join(df_all_data_raw, NP_df)
```

# Questionnaire Side effects
```{r add side effects quest}
df_sideEffects <- read.table(here::here("Quest_Side_Effects_cleaned.csv"), header = TRUE, sep = ";")
df_sideEffects$participant <- str_pad(df_sideEffects$participant, 2, pad = "0")
df_sideEffects <- df_sideEffects %>% 
  select(-c(date, Kommentare.))

df_sideEffects <- df_sideEffects %>% 
  mutate(sideEffects_sum = rowSums(across(c(pain_skin_head, toothache, tingling_head_skin, tingling_body, itching, burning_heat, headache, auditory_perception.tinnitus., skin_sensation, muscle_contraction, tiredness, sleepiness, hearing_changes, mood_change_negative, mood_change_positive, sickness, neck_pain_stiffness, coil_pressure, fear_nervousness, concentration_difficulty))))

df_sideEffects_summary <- df_sideEffects %>% 
  select(c(participant, session, sideEffects_sum))

# join with large df
df_all_data_raw <- full_join(df_all_data_raw, df_sideEffects_summary)
```

# Demographic information
```{r demographic data}
path_data_folder <- here::here("Raw_data/Training/")

# Get list of all .csv files in the data folder
file_list <- list.files(path = path_data_folder, pattern = "^sub-.*\\.csv$")

# Placeholders df for demographics, questions & text data
df_demographics_raw     <- data.frame()

# Loop files in my file list aka directory
for (i in 1:length(file_list)) {

  # Read in current file
  subj_df <- read.csv(paste(path_data_folder, file_list[i],sep = ""), sep = "\t")

  # If the df is separated by a semicolon instead of a comma, we only get
  # one messed-up column. In this case, use semicolon as separator for csv:
  if (ncol(subj_df) == 1) {
    subj_df <- read.csv(paste(path_data_folder, file_list[i],sep = ""), sep = ",")
  }
  
  id <- subj_df$participant[i]
  
  # print message
  message(paste(i, " - Reading in file ", file_list[i], ", participant ID: ", id, sep = ""))

  # rename block_kind column
  subj_df <- subj_df %>% 
    rename(nback_level = block_kind)
  
  subj_df$participant <- gsub("sub-", "", subj_df$participant)
  
  #create new columns for demographics and education answers and fill them with the corresponding answers
  subj_df$gender <- NA 
  subj_df$age <- NA
  subj_df$native_German <- NA
  subj_df$dyslexia <- NA
  subj_df$vision_glasses <- NA
  subj_df$vision_lenses <- NA
  subj_df$handedness <- NA
  subj_df$education <- NA
  subj_df$edu_years <- NA
  subj_df$edu_profession <- NA
  
  subj_df$gender <- subj_df$demographic_form.response[4]
  subj_df$age <- subj_df$demographic_form.response[5]
  subj_df$native_German <- subj_df$demographic_form.response[6]
  subj_df$dyslexia <- subj_df$demographic_form.response[7]
  subj_df$vision_glasses <- subj_df$demographic_form.response[8]
  subj_df$vision_lenses <- subj_df$demographic_form.response[9]
  subj_df$handedness <- subj_df$demographic_form.response[10]
  subj_df$education <- subj_df$education_form.response[13]
  subj_df$edu_profession <- subj_df$education_form.response[21]
  
  #demographics <- subj_df[,c("participant", "gender", "age", "language", "dyslexia", "vision_glasses", "vision_lenses", "handedness", "education", "edu_profession", "edu_years")]
  #subj_demographics[i] <- demographics

  # replace , with . to conform with standard numeric format
  subj_df$education_form.response <- gsub(",", ".", subj_df$education_form.response)

  # extract number including decimal
  subj_df$education_years <- sapply(subj_df$education_form.response, function(x) str_extract(x, "\\d+(\\.\\d+)?"))

  # convert to numeric
  subj_df$education_years <- as.numeric(subj_df$education_years)

  # get the total sum and replace 'edu_years' with that sum
  total_sum <- sum(subj_df$education_years, na.rm = TRUE)
  subj_df$education_years <- total_sum


  # GET RAW TEXT & N-BACK DATA
  subj_df <- subset(subj_df, select=c(participant, gender, native_German, dyslexia, vision_glasses, vision_lenses, handedness, education, edu_profession, education_years))

  subj_df <- subj_df %>% 
    distinct()
  
  # append subj_df chunk to df_text_data where we collect the data of all participants we want to keep
  df_demographics_raw <- as.data.frame(rbind(df_demographics_raw, subj_df))
}

df_demographics_raw$participant <- str_pad(df_demographics_raw$participant, 2, pad = "0")

# join with large df
df_all_data_raw <- full_join(df_all_data_raw, df_demographics_raw)

# Finally, save df ----
saveRDS(df_all_data_raw, here::here("RData/df_all_data_raw.rds"))
```

# Identify outliers in reaction times
```{r}
df_all_data_clean <- df_all_data_raw

### TRANSFORM RT DATA ####

# transf_val = sqrt (  ( x - sample_min ) / ( sample_max - sample_min)  )
# --> after this, z-transform all values and exclude all values exceeding a value of ± 2 (or ± 3, but they used 2 in the paper)

# This is basically a POMS (Little (2013), read in Moeller (2013)) transformation where you get
# the square root of the output afterwards and z-transform everything.

# Careful, normally, if you wanted to use the transformed values for group comparisons later, 
# you'd have to to the transformation across participants & conditions, so everything gets "pulled" into the same range.
# If you do this for each subject & condition separately, you can't compare means
# anymore, because every subset of data would have its own scale.

# Here, we only want to use the transformation for identifying & excluding outliers, so we don't really care about this problem. 
# So we can do this on block level, so we don't exclude more trials from "slower" 2-back blocks than from the BL for example.

# create new column in df_all_data_clean for the transformed RTs:
df_all_data_clean$tmp_transformed_RTs <- NA 

# get min reading time
# sample_min <- min(df_text_data$duration)
sample_min <- 0 # use smallest possible value here (this is described in a book by Little, 2013) - in this case: 0 words / 100 ms

# loop participants:
message("start excluding trials (block-wise)")
for (curr_id in unique(df_all_data_clean$participant)){
  
  message("current participant: ", curr_id)
  
  # get data of current participant:
  curr_df <- subset(df_all_data_clean, participant == curr_id)
  
  # loop sessions:
  for (curr_session in unique(curr_df$session)){
    
    # get df for curr session
    curr_sess <- subset(curr_df, session == curr_session)

    # loop blocks:
    for (curr_block in unique(curr_sess$block_nr_exp)){
    
      # get data of current block:
      curr_block_data <- subset(curr_sess, block_nr_exp == curr_block)
  
      # get max reading time (use sample maximum here)
      sample_max <- max(curr_block_data$RT)
  
      # do sqrt(POMS) transform of raw reading time values
      duration_standardized <- sqrt((curr_block_data$RT - sample_min) / (sample_max - sample_min))
  
      # z-transform reading data
      duration_standardized <- as.vector(scale(duration_standardized, center = T, scale = T))
  
      # put the transformed values into the big df with data of all participants:
      df_all_data_clean[which(df_all_data_clean$participant == curr_id & 
                                df_all_data_clean$session == curr_session &
                                df_all_data_clean$block_nr_exp == curr_block), ]$tmp_transformed_RTs <- duration_standardized
      
      # check how many trials we have that are < -2 or > 2:
      trials_excluded <- length(which(duration_standardized > 3 | duration_standardized < -3))
    }# END LOOP BlOCKS
  } # END SESSION LOOP
} # END LOOP PARTICIPANTS


# get index of all values < - 2 or > 2
excl_row_idx <- which(df_all_data_clean$tmp_transformed_RTs < -3 | df_all_data_clean$tmp_transformed_RTs > 3)

# check how the corresponding untransformed RTs look like so we get a feeling for what's being excluded:
# densityplot(df_all_data_clean[excl_row_idx, "duration"])

# kick out the outliers:
df_all_data_clean[excl_row_idx, "excl_trial"] <- TRUE
# total number of excluded trials
(excl_trials <- length(excl_row_idx)) # 2140 trials

# calculate % of excl trials
(excl_trials/length(df_all_data_clean$participant))*100

df_all_data_clean <- subset(df_all_data_clean, excl_trial == FALSE)

# drop column with the z-sqrt-POMS-transformed data, we don't need it anymore.  
df_all_data_clean$tmp_transformed_RTs <- NULL

#densityPlot(df_all_data_clean$RT)
```

# Some renaming of columns
```{r df_all_data_clean renaming}
# rename some columns
df_all_data_clean <- df_all_data_clean %>% 
  rename(task = block_name,
         cognitive_load = nback_level)

# recode values in cognitive_load column
df_all_data_clean <- df_all_data_clean %>% 
  mutate(cognitive_load = case_when(
    str_detect(cognitive_load, "None") ~ "Reading_only",
    str_detect(cognitive_load, "1") ~ "1-back",
    str_detect(cognitive_load, "2") ~ "2-back",
  ))

# recode values in stimulation condition column
df_all_data_clean <- df_all_data_clean %>% 
  mutate(stim_type = case_when(
    stim_type == "sham" ~ "Sham",
    stim_type == "offline_online" ~ "Offline + Online",
    stim_type == "offline" ~ "Offline"
  ))

# turn the values into factors and set their order
df_all_data_clean$cognitive_load <- factor(df_all_data_clean$cognitive_load,
                                  levels = c("Reading_only", "1-back", "2-back"))

# same for stimulation condition
df_all_data_clean$stim_type <- as.factor(df_all_data_clean$stim_type)
df_all_data_clean$stim_type <- factor(df_all_data_clean$stim_type,
                                  levels = c("Sham", "Offline", "Offline + Online"))

# add column for trial_index in one session
df_all_data_clean <- df_all_data_clean %>%
  arrange(participant, stim_type, block_nr_exp) %>%
  group_by(participant, stim_type) %>%
  mutate(trial_index_session = row_number())

# create a column for time that sets first trial of each session to 0 and calculates time to next trial so we get a measure of time progress in s across one session
df_all_data_clean <- df_all_data_clean %>%
  arrange(participant, stim_type, trial_index_session) %>%
  group_by(participant, stim_type, date) %>%
  mutate(
    time_from_onset_session = as.numeric(global_onset_time - first(global_onset_time), units = "secs")
  ) %>%
  ungroup()


# Check for similar length of sessions
df_subset <- df_all_data_clean %>% 
  group_by(participant, stim_type) %>% 
  mutate(session_length_s = max(time_from_onset_session) - min(time_from_onset_session)) %>% 
  select(participant, stim_type, session_length_s) %>% 
  distinct()

(plot_session_length <- ggplot(df_subset, aes(x = stim_type, y = session_length_s)) +
    #geom_violinhalf(position = position_nudge(x = 0.05), width = 1.2) +
    geom_boxplot(width = 0.4) +
    stat_summary(fun = mean, geom = "text", aes(label = sprintf("M=%.1f", after_stat(y))), vjust = -1.5, size = 2.5, color = "blue", fontface = "bold") +
    stat_summary(fun = min, geom = "text", aes(label = sprintf("min=%.0f", after_stat(y))), vjust = 1.5, size = 2, color = "grey30") +
    stat_summary(fun = max, geom = "text", aes(label = sprintf("max=%.0f", after_stat(y))), vjust = -0.5, size = 2, color = "grey30") +
    scale_x_discrete(expand = expansion(add = c(0.8, 0.5))) +  
    #facet_grid(~stim_type) +
    theme_bw() +
    theme(#legend.position = "none",
         text = element_text(family = "Helvetica"),
         panel.grid.major.x = element_blank(),
         panel.grid.minor = element_blank(),
         strip.background = element_blank(),
         plot.title = element_text(size = 10),
         axis.line = element_line(),
         axis.text.y = element_text(size = 8),
         axis.title.x = element_blank(),
         axis.text.x = element_text(angle = 45, hjust = 1),
         axis.text.x.bottom = element_text(size = 8))
)
ggsave(plot_session_length, file = here::here("Plots/plot_session_length.png"), width = 100, height = 100, units = "mm")

m_sessionLength <- lmerTest::lmer(session_length_s ~
                                    stim_type +
                                    (1|participant),
                                  data = df_subset, 
                                  REML = TRUE)
summary(m_sessionLength)
```

# D-prime cleaning
```{r dprime cleaning}
# Check for blocks that have dprime close to or below 0 since this would indicate that participants didn't perform the task properly
dprime_outliers <- subset(df_all_data_clean, task != "Reading_Baseline_main_click")
dprime_outliers_n <- dprime_outliers %>% group_by(participant, stim_type, block_nr_exp) %>% count(dprime <= 0)
dprime_outliers_n %>% group_by(stim_type) %>% summarise(sum(`dprime <= 0` == TRUE))
blocks2exclude <- dprime_outliers %>% 
  filter(dprime <= 0) %>% 
  dplyr::select(participant, session, block_nr_exp, dprime) %>% 
  distinct()

# Calculate % excluded trials
excl_trials <- df_all_data_clean %>%
  semi_join(blocks2exclude, by = c("participant", "session", "block_nr_exp"))
(length(excl_trials$participant)/length(dprime_outliers$participant))*100

# Let's remove those entries from our original df
df_all_data_no_outliers <- anti_join(df_all_data_clean, blocks2exclude, by = c("participant", "session", "block_nr_exp", "dprime"))

df_all_data_clean <- df_all_data_no_outliers
```

# Add e-field values
```{r e-fields}
df_efields_ext <- readRDS(here::here("RData/df_efields_ext.rds"))

df_all_data_clean <- full_join(df_all_data_clean, df_efields_ext)
```

# Add PCD (pulse-wise coil displacement)
```{r PCD}
# read pre-computed PCD values
df_PCD = read.csv(here::here("PCD/pcd_combined.csv"))

# some participants have more tracked pulses than 1500 (max for AG offline rTMS: 1500 pulses), let's limit this
df_PCD <- df_PCD %>%
  filter(!(target == "AG" & idx > 1500)) %>% 
  rename(stim_type = session,
         participant = sub,
         trigger_idx = idx,
         PCD_target = target)
df_PCD$participant <- gsub("sub-", "", df_PCD$participant)

# exclude unrealistic PCD values (PCD > 20)
df_PCD <- df_PCD %>% 
  filter(abs(PCD) < 20)

# calc mean for AG session
df_PCD <- df_PCD %>% 
  group_by(participant, stim_type) %>% 
  #mutate(PCD_q99 = quantile(PCD, probs = 0.99)) %>% 
  #filter(abs(PCD) <= PCD_q99) %>% 
  mutate(
    PCD = case_when(
      PCD_target == "AG" ~ mean(PCD),
      PCD_target == "DLPFC" ~ PCD
    )
  ) %>% 
  select(-trigger_idx, -interpolated) %>% 
  distinct() %>% 
  group_by(participant, stim_type, PCD_target) %>% 
  mutate(trigger_idx = row_number())

# for now, exclude PCD for AG (offline) in offline_online session
df_PCD <- df_PCD %>% 
  filter(!(stim_type == "offline_online" & PCD_target == "AG"))

# add idx for trigger to large df
test <- df_all_data_raw %>% 
  group_by(participant, stim_type) %>% 
  mutate(trigger_present = ifelse(!is.na(trigger_time), 1, 0),
         trigger_idx = cumsum(trigger_present)) %>% 
  select(-trigger_present)

# combine both dfs
test_all <- full_join(df_PCD, test)

# fix up NA values
test_all <- test_all %>% 
  group_by(participant) %>% 
  mutate(
    PCD_target = case_when(
      stim_type == "sham" ~ "sham",
      stim_type == "offline_online" ~ "DLPFC",
      stim_type == "offline" ~ "AG",
      TRUE ~ PCD_target),
    PCD_AG = first(PCD[PCD_target == "AG" & !is.na(PCD)]),
    PCD = case_when(
      # keep all existing non-NA values
      !is.na(PCD) ~ PCD,
      
      # offline: replace NA with that participant's AG PCD
      stim_type == "offline" ~ PCD_AG,
      
      # offline_online: replace NA with median PCD of offline_online rows
      stim_type == "offline_online" ~ median(PCD[stim_type == "offline_online"], na.rm = TRUE),
      
      stim_type == "sham" ~ 0,
      
      # sham or anything else: leave as is (NA)
      TRUE ~ PCD
    )) %>% 
  select(-PCD_AG)

# sub 17 doesn't have PCD values for offline_online session!
  

# exclude rows based on 99 quantile PCD?



df_PCD <- df_PCD %>% 
  group_by(participant, stim_type) %>% 
  mutate(PCD_q99 = quantile(PCD, probs = 0.99)) %>% 
  filter(abs(PCD) <= PCD_q99) %>% 
  mutate(
    PCD = case_when(
      target == "AG"    ~ mean(PCD),
      target == "DLPFC" ~ PCD
    )
  ) %>% 
  select(-idx, -interpolated, -PCD_q99) %>% 
  distinct() %>% 
  group_by(participant, stim_type, target) %>% 
  mutate(idx = row_number())

# how many pulse indices do we have in the other df?
test2 <- t %>% 
  group_by(participant, stim_type) %>% 
  #filter(!is.na(trigger_time)) %>% 
  select(maximum_triggers_this_block, minimum_triggers_this_condition, total_triggers_sent_this_condition, trigger_time, trigger_present, trigger_idx)

```

# Save cleaned df
```{r save clean df}
# exclude session 2 for participant 07, stim_type offline, since there was an error in this session with the experiment
df_all_data_clean <- df_all_data_clean %>% 
  filter(!(participant == "07" & session == 2))

# Save df
saveRDS(df_all_data_clean, file = here::here("RData/df_all_data_clean.rds"))
```
